```{r, echo=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "", echo = FALSE,
                      warning = FALSE, message = FALSE)
```

```{r}
library(data.table)
library(survey)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
source(paste0(getwd(), "/_RCode/read_census_data.R"))
source(paste0(getwd(), "/_RCode/make_table_data.R"))
source(paste0(getwd(), "/_RCode/make_plot_data.R"))
source(paste0(getwd(), "/_RCode/additional_functions.R"))

gradientColors <- colorRampPalette(c("#EA008B", "#B0AEDC", "#554149"))
discreteColors <- c("#EA008B", "#B0AEDC", "#554149", "#A07200", "#AADA91", 
                    "#FF8189", "#FFCF50", "#6FCFEB", "#76236C", "#FFFF3B")
```

# Camp logistics

## Camp details

### Number of people in camps

```{r}
nbcampGroup <- list("100-199" = c("_100to199",
                                  "100-199",
                                  "100-149", "150-199"), 
                    "10-19" = c("_10to19",
                                "10-19"), 
                    "200+" = c("_200_or_more", 
                               "200 or more"),
                    "20-29" = c("_20to29", 
                                "20-29"), 
                    "30-49" = c("_30to49",
                                "30-49"), 
                    "3-5" = c("_3to5",
                              "3-5"),
                    "50-99" = c("_50to99",
                                "50-99"), 
                    "6-9" = c("_6to9",
                              "6-9"), 
                    "1" = c("1"), 
                    "2" = c("2"))

nbcamp <- makePlotData("How many people were in your camp (total, including you)?",
                       varNameTable = varNameTable,
                       designs = list(design13, design14, design15, design16,
                                      design17, design18, design19, design22,
                                      design23, design24),
                       years = c(2013:2019, 2022:2024),
                       levels = c(rep(list(c("_100to199", "_10to19",
                                             "_200_or_more", "_20to29",
                                             "_30to49", "_3to5", "_50to99",
                                             "_6to9", "1", "2")), times = 7),
                                  rep(list(c("100-199", "10-19", "200 or more",
                                         "20-29", "30-49", "3-5",
                                         "50-99", "6-9", "1", "2")), times = 2),
                                  rep(list(c("100-149", "150-199", "10-19", 
                                             "200 or more", "20-29", "30-49", 
                                             "3-5", "50-99", "6-9", "1", "2")), 
                                      times = 1)),
                       labels = c("100-199", "10-19", "200+",
                                  "20-29", "30-49", "3-5",
                                  "50-99", "6-9", "1", "2"),
                       labelOrder = rev(c(9, 10, 6, 8, 2, 4, 5,
                                          7, 1, 3)),
                       groups = nbcampGroup)

ggplot(nbcamp, aes(x = year, y = est, fill = labels)) +
  # geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B",
  #          alpha = 0.7) +
  geom_area(alpha = 0.6 , linewidth = 1, colour="black") +
  scale_y_continuous(labels = percent) +
  scale_x_continuous(breaks = c(2012:2019, 2022:2024)) +
  scale_fill_manual(values = gradientColors(10)) +
  labs(x = "", y = "Burning Man participants (%)",
       title = "How many people were in your camp (total, including you)?",
       fill = "Number of \npeople in \ncamp") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) #+
  # facet_wrap(~year, nrow = 2)

nbcamp$labels <- factor(nbcamp$labels, levels = rev(levels(nbcamp$labels)))

makeTableData(nbcamp) |>
  kbl(col.names = c(2013:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:11, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

<!-- Question was removed: check this. -->

<!-- ### RV camping and pumping -->

<!-- <!-- Additional (or instead) plot yes/no staying in an RV maybe? -->

--\>

<!-- ```{r} -->

<!-- # Question options were changed in 2015, need to add 2013 and 2014 -->

<!-- # stayedRV <- makePlotData("Did you stay in an RV or camper-trailer in Black Rock City this year, and was it pumped (serviced) on playa?", -->

<!-- #                          varNameTable = varNameTable, -->

<!-- #                          designs = list(design15, design16, design17, -->

<!-- #                                         design18, design19, design22, -->

<!-- #                                         design23), -->

<!-- #                          years = c(2015:2019, 2022:2023), -->

<!-- #                          levels = c(rep(list(c("No", "Not_sure", -->

<!-- #                                                "Yes_and_pumped", -->

<!-- #                                                "Yes_idk_pumped", -->

<!-- #                                                "Yes_not_pumped")), times = 5), -->

<!-- #                                     rep(list(c("No", "Not sure", -->

<!-- #                                            "Yes and pumped", -->

<!-- #                                            "Yes and don\'t know if pumped", -->

<!-- #                                            "Yes and not pumped")), times = 2)), -->

<!-- #                          labels = c("No", "Not sure", -->

<!-- #                                     "Yes and pumped", -->

<!-- #                                     "Yes and don\'t know if pumped", -->

<!-- #                                     "Yes and not pumped"), -->

<!-- #                          labelOrder = c(3, 5, 4, 1, 2)) -->

<!-- #  -->

<!-- # ggplot(stayedRV, aes(x = year, y = est, color = labels)) + -->

<!-- #   geom_line(linewidth = 1.5, alpha = 0.7) + -->

<!-- #   geom_point(size = 2.25) + -->

<!-- #   theme_bw() + -->

<!-- #   theme(panel.grid.minor = element_blank()) + -->

<!-- #   scale_x_continuous(breaks = c(2014:2019, 2022:2023),  -->

<!-- #                      labels = c(2014:2019, 2022:2023)) + -->

<!-- #   scale_y_continuous(labels = percent, limits = c(0, NA)) + -->

<!-- #   scale_color_manual(values = discreteColors[1:5]) + -->

<!-- #   labs(x = "", y = "Burning Man Partcipants (%)", color = "", -->

<!-- #        title = "Did you stay in an RV or camper-trailer in Black Rock City this year, \n and was it pumped (serviced) on playa?") -->

<!-- #  -->

<!-- # makeTableData(stayedRV) |> -->

<!-- #   kbl(col.names = c(2015:2019, 2022:2023), -->

<!-- #       row.names = TRUE) |> -->

<!-- #   kable_paper("striped", full_width = F) |> -->

<!-- #   kable_styling() |> -->

<!-- #   column_spec(column = 1:8, width_min = "10.5em") |> -->

<!-- #   scroll_box(width = "100%") -->

<!-- ``` -->

<!-- Question was removed, check this -->

<!-- ### Number of adults in the RV/camper-trailer -->

<!-- ```{r} -->

<!-- # nbrv <- makePlotData("How many adults (18+years old) stayed in the RV/camper-trailer including you?", -->

<!-- #                      varNameTable = varNameTable, -->

<!-- #                      designs = list(design15, design16, design17, design18, -->

<!-- #                                     design19, design22, design23), -->

<!-- #                      years = c(2015:2019, 2022:2023), -->

<!-- #                      levels = c(list(c("only_me", "2", "3", "4", "5", -->

<!-- #                                        "6", "7", "8", "9", "_10+")), -->

<!-- #                                 rep(list(c("only_me", "2", "3", "4", "5", -->

<!-- #                                            "6", "7", "8", "9", "_10_or_more")), -->

<!-- #                                     times = 4), -->

<!-- #                                 rep(list(c("1", "2", "3", "4", "5", -->

<!-- #                                        "6", "7", "8", "9", "10+")), times = 2)), -->

<!-- #                      labels = c("1", "2", "3", "4", "5", -->

<!-- #                                 "6", "7", "8", "9", "10+")) -->

<!-- #  -->

<!-- # ggplot(nbrv, aes(x = labels, y = est)) + -->

<!-- #   geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B", -->

<!-- #            alpha = 0.7) + -->

<!-- #   scale_y_continuous(labels = percent) + -->

<!-- #   labs(x = "Number of people in camp", y = "Burning Man participants (%)", -->

<!-- #        title = "How many adults stayed in the RV/camper-trailer including you?") + -->

<!-- #   theme_bw() + -->

<!-- #   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + -->

<!-- #   facet_wrap(~year, nrow = 2) -->

<!-- #  -->

<!-- # makeTableData(nbrv) |> -->

<!-- #   kbl(col.names = c(2015:2019, 2022:2023), -->

<!-- #       row.names = TRUE) |> -->

<!-- #   kable_paper("striped", full_width = F) |> -->

<!-- #   kable_styling() |> -->

<!-- #   column_spec(column = 1:8, width_min = "10.5em") |> -->

<!-- #   scroll_box(width = "100%") -->

<!-- ``` -->

### Number of family members in Black Rock City

```{r}
# 2013 has only up to 4+ and 2015 is missing the 6+ option

#TODO update grouping to new list format and use only one 
#     call to makePlotData.

nbfamily1 <- makePlotData("How many of your family members were in Black Rock City this year? (e.g. relatives, partners, spouses, offspring, in-laws)",
                          varNameTable = varNameTable,
                          designs = list(design14, design15, design16, design17,
                                         design18, design19, design22, design23,
                                         design24),
                          years = c(2014:2019, 2022:2024),
                          levels = c(rep(list(c("0", "1", "2", "3",
                                                "4", "5",
                                                "_6_or_more")), times = 6),
                                     rep(list(c("0", "1", "2", "3", "4", "5",
                                            "more than 5")), times = 3)),
                          groups = c(1, 2, 3, 4, 5, 5, 5),
                          labels = c("0", "1", "2", "3", "4+"))

nbfamily2 <- makePlotData("How many of your family members were in Black Rock City this year? (e.g. relatives, partners, spouses, offspring, in-laws)",
                          varNameTable = varNameTable,
                          designs = list(design13),
                          years = c(2013),
                          levels = c(rep(list(c("0", "1", "2", "3",
                                                "_4_or_more")), times = 1)),
                          labels = c("0", "1", "2", "3", "4+"))
nbfamily <- rbind(nbfamily1, nbfamily2)

ggplot(nbfamily, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:5]) +
  labs(x = "", y = "Burning Man Partcipants (%)", color = "",
       title = "How many of your family members were in \n Black Rock City this year?")

makeTableData(nbfamily) |>
  kbl(col.names = c(2013:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:11, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

## Camp placement

<!-- ### Camp location -->

<!-- Camp location heat map? -->

### Camps placed by the Burning Man Placement Team

```{r}
placed <- makePlotData("Was your camp assigned a location by the Burning Man Placement Team before the event?",
                       varNameTable = varNameTable,
                       designs = list(design14, design15, design16, design17,
                                      design18, design19, design22, design23,
                                      design24),
                       years = c(2014:2019, 2022:2024),
                       levels = c(rep(list(c("Yes", "IDK", "No")), times = 6),
                                  rep(list(c("Yes","Don\'t know", "No")), times = 3)),
                       labels = c("Yes", "I don\'t know", "No"),
                       labelOrder = c(3, 2, 1))

ggplot(placed, aes(x = year, y = est, fill = labels)) +
  geom_area(alpha = 0.60, color = "black") +
  scale_y_continuous(labels = percent) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024), labels = c(2013:2019, 2022:2024)) +
  scale_fill_manual(values = discreteColors[3:1]) +
  labs(x = "", y = "Burning Man participants (%)",
       fill = "Was your camp assigned \n a location by the \n Placement Team?",
       title = "Was your camp assigned a location by the Burning Man Placement Team \n before the event?") +
  theme_bw()

makeTableData(placed) |>
  kbl(col.names = c(2014:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:10, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### Reason for camp location in Black Rock City

<!-- There was something wrong with this question.  The code here doesn't work -->

```{r}

# location <- makePlotData("What most determined where you chose to camp in Black Rock City this year?",
#                          varNameTable = varNameTable,
#                          designs = list(design14, design15, design16, design17,
#                                         design18, design19, design22, design23),
#                          years = c(2014:2019, 2022:2023),
#                          levels = c(rep(list(c("yes")), times = 6),
#                                     rep(list(c(TRUE)), times = 2)),
#                          labels = c("Nearby attractions",
#                                     "Favorable playa surface conditions",
#                                     "Friends\' choice",
#                                     "Space available",
#                                     "Nice neighbors",
#                                     "Same as last year",
#                                     "Different than last year",
#                                     "Quiet",
#                                     "Access to all-night parties",
#                                     "I don\'t know"),
#                          labelOrder = c(4,3,8,5,6,1,2,7,9,10))
# 
# ggplot(location[location$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B",
#            alpha = 0.7) +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Number of people in camp",
#        y = "Burning Man participants in 2023 (%)",
#        title = "What most determined where you chose to camp in Black Rock City this year?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# makeTableData(location) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")

location <- makePlotData("What most determined where you chose to camp in Black Rock City this year?",
                         varNameTable = varNameTable,
                         designs = list(design14, design15, design16, design17,
                                        design18, design19, design22, design23,
                                        design24),
                         years = c(2014:2019, 2022:2024),
                         levels = c(rep(list(c("yes")), times = 6),
                                    rep(list(c(TRUE)), times = 3)),
                         labels = c("Nearby attractions",
                                    "Favorable playa surface conditions",
                                    "Friends\' choice",
                                    "Space available",
                                    "Nice neighbors",
                                    "Same as last year",
                                    "Different than last year",
                                    "Quiet",
                                    "Access to all-night parties",
                                    "I don\'t know"),
                         labelOrder = c(4,3,8,5,6,1,2,7,9,10))

ggplot(location[location$year == 2024,], aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B",
           alpha = 0.7) +
  scale_y_continuous(labels = percent) +
  labs(x = "Number of people in camp",
       y = "Burning Man participants in 2024 (%)",
       title = "What most determined where you chose to camp in Black Rock City this year?") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

makeTableData(location) |>
  kbl(col.names = c(2014:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:10, width_min = "10.5em") |>
  scroll_box(width = "100%")

```

## Tickets

### Source of Burning Man ticket

```{r}
# ticketSource <- makePlotData("Where did you get your ticket for the event this year?",
#                              varNameTable = varNameTable,
#                              designs = list(design22, design23),
#                              years = c(2022:2023),
#                              levels = rep(list(c("2021 Invitation to the Future Ticket",
#                                              "Burner Express Bus Plus",
#                                              "FOMO sale",
#                                              "Gifted ticket",
#                                              "Main sale or OMG sale",
#                                              "No ticket",
#                                              "Other",
#                                              "Someone I know",
#                                              "Staff or volunteer credential",
#                                              "STEP",
#                                              "Stewards sales",
#                                              "Stranger",
#                                              "Third party reseller",
#                                              "Ticket Aid/Low Income Ticket Program")), times = 2),
#                              labels = c("2021 Invitation to the \n Future Ticket",
#                                              "Burner Express Bus Plus",
#                                              "FOMO sale",
#                                              "Gifted ticket",
#                                              "Main sale or OMG sale",
#                                              "No ticket",
#                                              "Other",
#                                              "Someone I know",
#                                              "Staff or volunteer \n credential",
#                                              "STEP",
#                                              "Stewards sales",
#                                              "Stranger",
#                                              "Third party reseller",
#                                              "Ticket Aid/Low Income \n Ticket Program"),
#                              labelOrder = c(7,9,1,2,6,4,3,13,8,11,12,14,10,5))
# 
# ggplot(ticketSource, aes(x = labels, y = est, fill = as.factor(year))) +
#   geom_bar(stat = "identity", position = "dodge") +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = discreteColors[2:1]) +
#   labs(x = "Ticket source", y = "Burning Man participants in 2023 (%)",
#        title = "Where did you get your ticket for the event?",
#        fill = "") +
#   theme_bw() +
#   coord_flip() +
#   guides(fill = guide_legend(reverse = TRUE))
# 
# makeTableData(ticketSource)[14:1,] |>
#   kbl(col.names = c(2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:2, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")

ticketSource <- makePlotData("Where did you get your ticket for the event this year?",
                             varNameTable = varNameTable,
                             designs = list(design24),
                             years = c(2024),
                             levels = rep(list(c("Burner Express Bus Plus", 
                                                 "FOMO Sale", 
                                                 "Gifted ticket", 
                                                 "Kid's Ticket", 
                                                 "Main sale or OMG sale", 
                                                 "No ticket", 
                                                 "Other", 
                                                 "Someone I know", 
                                                 "Stewards sales", 
                                                 "Stranger", 
                                                 "Third party reseller", 
                                                 "Ticket Aid/Low Income Ticket Program")), times = 2),
                             labels = c("Burner Express Bus Plus", 
                                                 "FOMO Sale", 
                                                 "Gifted ticket", 
                                                 "Kid's Ticket", 
                                                 "Main sale or OMG sale", 
                                                 "No ticket", 
                                                 "Other", 
                                                 "Someone I know", 
                                                 "Stewards sales", 
                                                 "Stranger", 
                                                 "Third party reseller", 
                                                 "Ticket Aid/Low Income Ticket Program"),
                             labelOrder = rev(c("Main sale or OMG sale", 
                                                "Stewards sales",
                                                "Someone I know",
                                                "Gifted ticket",
                                                "Ticket Aid/Low Income Ticket Program", 
                                                "FOMO Sale", 
                                                "Burner Express Bus Plus", 
                                                "Third party reseller", 
                                                "No ticket",
                                                "Stranger", 
                                                "Kid's Ticket", 
                                                "Other")))

ggplot(ticketSource, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", position = "dodge", fill = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "Ticket source", y = "Burning Man participants in 2024 (%)",
       title = "Where did you get your ticket for the event?",
       fill = "") +
  theme_bw() +
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE))

makeTableData(ticketSource)[12:1,] |>
  kbl(col.names = c(2024), row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  column_spec(column = 1:1, width_min = "10.5em") |>
  kable_styling() |>
  scroll_box(width = "100%")
```

### Amount paid for Burning Man ticket

```{r}
# ticketCost <- makePlotData("Did you pay face value for your ticket?",
#                            varNameTable = varNameTable,
#                            designs = list(design14, design15, design16,
#                                           design17, design18, design19,
#                                           design22, design23),
#                            years = c(2014:2019, 2022:2023),
#                            levels = c(rep(list(c("Facevalue", "Gift",
#                                                  "IDK", "Less_than_facevalue",
#                                                  "More_than_facevalue",
#                                                  "Other")), times = 6),
#                                       rep(list(c("Face value", "Gift/did not pay",
#                                              "Don\'t know",
#                                              "Less than face value",
#                                              "More than face value",
#                                              "Other")), times = 2)),
#                            labels = c("Face value", "Gift or did not pay",
#                                              "I don\'t know",
#                                              "Less than face value",
#                                              "More than face value",
#                                              "Other"),
#                            labelOrder = c(5, 1, 4, 2, 3, 6))
# 
# ggplot(ticketCost, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2014:2019, 2022:2023), 
#                      labels = c(2014:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors[1:6]) +
#   labs(x = "", y = "Burning Man Partcipants (%)", color = "Amount paid",
#        title = "Did you pay face value for your ticket?")
# 
# ticketCostChange <- data.table(level = ticketCost$labels[1:6],
#                                est2022 = ticketCost$est[ticketCost$year == 2022],
#                                est2023 = ticketCost$est[ticketCost$year == 2023])
# ticketCostChange$estDif <- ticketCostChange$est2023 - ticketCostChange$est2022
# ticketCostChange$positive <- ifelse(ticketCostChange$estDif > 0, ticketCostChange$estDif, 0)
# ticketCostChange$negative <- ifelse(ticketCostChange$estDif < 0, ticketCostChange$estDif, 0)
# 
# ticketCostChange2 <- data.table(level = ticketCostChange$level,
#                                 change = c(ticketCostChange$positive,
#                                            ticketCostChange$negative),
#                                 direction = rep(c("Positive", "Negative"),
#                                                 each = nrow(ticketCostChange)))
# 
# ggplot(ticketCostChange2, aes(x = level, y = change, fill = direction)) + 
#   geom_bar(stat="identity", position="identity", show.legend = FALSE) +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1),
#         panel.grid.minor = element_blank()) +
#   scale_y_continuous(labels = percent, limits = c(-0.025, 0.025)) +
#   scale_fill_manual(values = discreteColors[2:1]) +
#   labs(x = "Ticket cost", y = "Change in response",
#        title = "Changes in amount paid for tickets from 2022 to 2023")
# 
# makeTableData(ticketCost) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")

ticketCost <- makePlotData("Did you pay face value for your ticket?",
                           varNameTable = varNameTable,
                           designs = list(design14, design15, design16,
                                          design17, design18, design19,
                                          design22, design23, design24),
                           years = c(2014:2019, 2022:2024),
                           levels = c(rep(list(c("Facevalue", "Gift",
                                                 "IDK", "Less_than_facevalue",
                                                 "More_than_facevalue",
                                                 "Other")), times = 6),
                                      rep(list(c("Face value", "Gift/did not pay",
                                             "Don\'t know",
                                             "Less than face value",
                                             "More than face value",
                                             "Other")), times = 3)),
                           labels = c("Face value", "Gift or did not pay",
                                             "I don\'t know",
                                             "Less than face value",
                                             "More than face value",
                                             "Other"),
                           labelOrder = c(5, 1, 4, 2, 3, 6))

ggplot(ticketCost, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2014:2019, 2022:2024),
                     labels = c(2014:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:6]) +
  labs(x = "", y = "Burning Man Partcipants (%)", color = "Amount paid",
       title = "Did you pay face value for your ticket?")

ticketCostChange <- data.table(level = ticketCost$labels[1:6],
                               est2023 = ticketCost$est[ticketCost$year == 2023],
                               est2024 = ticketCost$est[ticketCost$year == 2024])
ticketCostChange$estDif <- ticketCostChange$est2024 - ticketCostChange$est2023
ticketCostChange$positive <- ifelse(ticketCostChange$estDif > 0, ticketCostChange$estDif, 0)
ticketCostChange$negative <- ifelse(ticketCostChange$estDif < 0, ticketCostChange$estDif, 0)

ticketCostChange2 <- data.table(level = ticketCostChange$level,
                                change = c(ticketCostChange$positive,
                                           ticketCostChange$negative),
                                direction = rep(c("Positive", "Negative"),
                                                each = nrow(ticketCostChange)))

ggplot(ticketCostChange2, aes(x = level, y = change, fill = direction)) +
  geom_bar(stat="identity", position="identity", show.legend = FALSE) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(labels = percent, limits = c(-0.025, 0.025)) +
  scale_fill_manual(values = discreteColors[2:1]) +
  labs(x = "Ticket cost", y = "Change in response",
       title = "Changes in amount paid for tickets from 2023 to 2024")

makeTableData(ticketCost) |>
  kbl(col.names = c(2014:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:10, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

## Generators

### Electricity generation in camps

```{r}


generate <- makePlotData("Did you generate electricity in your camp?",
                         varNameTable = varNameTable,
                         designs = list(design13, design14, design15,
                                        design16, design17, design18,
                                        design19, design22, design23,
                                        design24),
                         years = c(2013:2019, 2022:2024),
                         levels = c(rep(list(c("yes")), times = 7),
                                    rep(list(c(TRUE)), times = 3)),
                         labels = c("I didn\'t use any power",
                                    "I used batteries",
                                    "I used solar power",
                                    "I used wind power",
                                    "I used my vehicle\'s generator",
                                    "I used my camp\'s generator",
                                    "I used another camp\'s power",
                                    "I used the BRC grid",
                                    "Other"),
                         labelOrder = c(9,4,7,1,8,5,3,2,6)[9:1])


ggplot(generate, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:9]) +
  labs(x = "", y = "Burning Man Partcipants (%)", color = "",
       title = "How did you generate electricity in your camp?") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

makeTableData(generate)[9:1,] |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  column_spec(column = 1:11, width_min = "10.5em") |>
  kable_styling() |>
  scroll_box(width = "100%")
```

### Primary fuel used to run vehicle generators

```{r}
vehicleGenfuel <- makePlotData("What was the primary type of fuel you used to run your vehicle\'s generator during your time in Black Rock City?",
                              varNameTable = varNameTable,
                              designs = list(design16, design17, design18,
                                             design19, design22, design23,
                                             design24),
                              years = c(2016:2019, 2022:2024),
                            levels = c(rep(list(c("Biodiesel",
                                                  "Diesel",
                                                  "Gasoline",
                                                  "IDK",
                                                  "Propane",
                                                  "Other")), times = 4),
                                       rep(list(c("Biodiesel",
                                              "Diesel",
                                              "Gasoline",
                                              "Don\'t know",
                                              "Propane",
                                              "Other")), times = 3)),
                              labels = c("Biodiesel",
                                         "Diesel",
                                         "Gasoline",
                                         "I don\'t know",
                                         "Propane",
                                         "Other"),
                            labelOrder = c(3, 2, 1, 5, 4, 6))

ggplot(vehicleGenfuel, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2016:2019, 2022:2024),
                     labels = c(2016:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:6]) +
  labs(x = "", y = "Burning Man Partcipants (%)", color = "",
       title = "What was the primary type of fuel you used to run \n your vehicle\'s generator during your time in Black Rock City?")

makeTableData(vehicleGenfuel) |>
  kbl(col.names = c(2016:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:8, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### Approximately how many hours per day did you run your vehicle's generator?

```{r}
vehicleHours <- data.frame(hours = c(census16$hoursvehicgen,
                                     census17$hoursvehicgen,
                                     census18$hoursvehicgen,
                                     census19$hoursvehicgen,
                                     census22$generatorHoursVehicle,
                                     census23$generatorHoursVehicle,
                                     census24$generatorHoursVehicle),
                           year = c(rep(2016, times = nrow(census16)),
                                    rep(2017, times = nrow(census17)),
                                    rep(2018, times = nrow(census18)),
                                    rep(2019, times = nrow(census19)),
                                    rep(2022, times = nrow(census22)),
                                    rep(2023, times = nrow(census23)),
                                    rep(2024, times = nrow(census24))),
                           weights = c(census16$weightbmorg1,
                                       census17$weightbfarrival,
                                       census18$weightbfarrival,
                                       census19$weightbfarrival,
                                       census22$weights,
                                       census23$weights,
                                       census24$weights))

vehicleHoursMean <- as.data.frame(rbind(weighted.mean2(census16$hoursvehicgen,
                                                       census16$weightbmorg1),
                                        weighted.mean2(census17$hoursvehicgen,
                                                       census17$weightbfarrival),
                                        weighted.mean2(census18$hoursvehicgen,
                                                       census18$weightbfarrival),
                                        weighted.mean2(census19$hoursvehicgen,
                                                       census19$weightbfarrival),
                                        weighted.mean2(census22$generatorHoursVehicle,
                                                       census22$weights),
                                        weighted.mean2(census23$generatorHoursVehicle,
                                                       census23$weights),
                                        weighted.mean2(census24$generatorHoursVehicle,
                                                       census24$weights)))
vehicleHoursMean$year <- c(2016:2019, 2022:2024)


ggplot(vehicleHours, aes(y = hours, x = as.factor(year),
                         weight = weights)) +
  geom_boxplot(width=0.6,  fill = "#EA008B", color = "black",
               alpha = 0.7) +
  geom_point(data = vehicleHoursMean, aes(x = as.factor(year), y = wmean),
             shape = 23, size = 3, fill = "grey", inherit.aes = FALSE) +
  theme_bw() +
  labs(x = "", y = "Generator hours per day",
       caption = "Diamond indicates weighted mean",
       title = "Approximately how many hours per day did you run your vehicle's generator?") +
  scale_y_continuous(limits = c(0, 24),
                     breaks = c(0, 4, 8, 12, 16, 20, 24),
                     labels = c(0, 4, 8, 12, 16, 20, 24))

fdf <- paste0("%.", 1, "f")
vehicleHoursTable <- apply(vehicleHoursMean, 1, function(x){
  paste0(sprintf(fdf, round(x[1],1)), " (",
         sprintf(fdf, round(x[3], 1)), ", ",
         sprintf(fdf, round(x[4], 1)), ")")
})

vehicleHoursTable <- matrix(vehicleHoursTable, nrow = 1)
rownames(vehicleHoursTable) <- "Average hours"

vehicleHoursTable |>
  kbl(col.names = c(2016:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:8, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### Primary fuel used to run camp generator

```{r}
#Selections changed in 2022.  2016-2019 is available also
campGenFuel <- makePlotData("What was the primary type of fuel you used to run your camp\'s generator during your time in Black Rock City?",
                              varNameTable = varNameTable,
                              designs = list(design16, design17, design18,
                                             design19, design22, design23,
                                             design24),
                              years = c(2016:2019, 2022:2024),
                            levels = c(rep(list(c("Biodiesel",
                                                  "Diesel",
                                                  "Gasoline",
                                                  "IDK",
                                                  "Multiple_types",
                                                  "Propane",
                                                  "Other")), times = 4),
                                       rep(list(c("Biodiesel",
                                              "Diesel",
                                              "Gasoline",
                                              "Don\'t know",
                                              "Multiple types",
                                              "Propane",
                                              "Other")), times = 3)),
                              labels = c("Biodiesel",
                                         "Diesel",
                                         "Gasoline",
                                         "I don\'t know",
                                         "Multiple types",
                                         "Propane",
                                         "Other"),
                            labelOrder = c(3, 2, 1, 7, 5, 4, 6))

ggplot(campGenFuel, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2016:2019, 2022:2024),
                     labels = c(2016:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:7]) +
  labs(x = "", y = "Burning Man Partcipants (%)", color = "",
       title = "What was the primary type of fuel you used to run \n your camp's generator while in Black Rock City?")

makeTableData(campGenFuel) |>
  kbl(col.names = c(2016:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:8, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### Approximately how many hours per day did you run your camp's generators?

```{r}
campHours <- data.frame(hours = c(census16$hourscampgen,
                                     census17$hourscampgen,
                                     census18$hourscampgen,
                                     census19$hourscampgen,
                                     census22$generatorHoursCamp,
                                     census23$generatorHoursCamp,
                                     census24$generatorHoursCamp),
                           year = c(rep(2016, times = nrow(census16)),
                                    rep(2017, times = nrow(census17)),
                                    rep(2018, times = nrow(census18)),
                                    rep(2019, times = nrow(census19)),
                                    rep(2022, times = nrow(census22)),
                                    rep(2023, times = nrow(census23)),
                                    rep(2024, times = nrow(census24))),
                           weights = c(census16$weightbmorg1,
                                       census17$weightbfarrival,
                                       census18$weightbfarrival,
                                       census19$weightbfarrival,
                                       census22$weights,
                                       census23$weights,
                                       census24$weights))

campHoursMean <- as.data.frame(rbind(weighted.mean2(census16$hourscampgen,
                                                       census16$weightbmorg1),
                                        weighted.mean2(census17$hourscampgen,
                                                       census17$weightbfarrival),
                                        weighted.mean2(census18$hourscampgen,
                                                       census18$weightbfarrival),
                                        weighted.mean2(census19$hourscampgen,
                                                       census19$weightbfarrival),
                                        weighted.mean2(census22$generatorHoursCamp,
                                                       census22$weights),
                                     weighted.mean2(census23$generatorHoursCamp,
                                                       census23$weights),
                                     weighted.mean2(census24$generatorHoursCamp,
                                                       census24$weights)))
campHoursMean$year <- c(2016:2019, 2022:2024)


ggplot(campHours, aes(y = hours, x = as.factor(year),
                         weight = weights)) +
  geom_boxplot(width=0.6,  fill = "#EA008B", color = "black",
               alpha = 0.7) +
  geom_point(data = campHoursMean, aes(x = as.factor(year), y = wmean),
             shape = 23, size = 3, fill = "grey", inherit.aes = FALSE) +
  theme_bw() +
  labs(x = "", y = "Generator running hours per day", caption = "Diamond indicates weighted mean") +
  scale_y_continuous(limits = c(0, 24),
                     breaks = c(0, 4, 8, 12, 16, 20, 24),
                     labels = c(0, 4, 8, 12, 16, 20, 24))

fdf <- paste0("%.", 1, "f")
campHoursTable <- apply(campHoursMean, 1, function(x){
  paste0(sprintf(fdf, round(x[1],1)), " (",
         sprintf(fdf, round(x[3], 1)), ", ",
         sprintf(fdf, round(x[4], 1)), ")")
})

campHoursTable <- matrix(campHoursTable, nrow = 1)
rownames(campHoursTable) <- "Average hours"

campHoursTable |>
  kbl(col.names = c(2016:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:8, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### What was the total output of your camp's generator?

```{r}

genOutput <- makePlotData("What was the total output of your camp's generator(s)?",
                          varNameTable = varNameTable,
                          designs = list(design16, design17, design18,
                                         design19, design22, design23,
                                         design24),
                          years = c(2016:2019, 2022:2024),
                          levels = c(rep(list(c("_1kW", "_10kWto19kW",
                                                "_20kWto39kW", "_2kWto3kW",
                                                "_40kW_or_more", "_4kWto9kW",
                                                "IDK", "lessthan1kW")), times = 4),
                                     rep(list(c("1kW-<2kW", "10kW-<20kW",
                                            "20kW-<40kW", "2kW-<4kW",
                                            "40kW+", "4kW-<10kW",
                                            "Don't know", "<1kW")), times = 3)),
                          labels = c("1kW-<2kW", "10kW-<20kW",
                                     "20kW-<40kW", "2kW-<4kW",
                                     "40kW+", "4kW-<10kW",
                                     "Don't know", "<1kW"),
                          labelOrder = c(8, 1, 4, 6, 2, 3, 5, 7))

ggplot(genOutput[genOutput$year == 2024,], aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B",
           alpha = 0.7) +
  scale_y_continuous(labels = percent) +
  labs(x = "Generator output", y = "Burning Man participants (%)",
       title = "What was the total output of your camp's generator?") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

makeTableData(genOutput) |>
  kbl(col.names = c(2016:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:8, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

## Bikes

### Bike use in Black Rock City

```{r}
# Need to check 2023 data

# bikeUse <- makePlotData("Did you ride a bike in Black Rock City?",
#                           varNameTable = varNameTable,
#                           designs = list(design23, design24),
#                           years = c(2023:2024),
#                           levels = c(list(c("3", "2", "1")),
#                                      list(c("I don\'t know", "No", "Yes"))),
#                           labels = c(c("I don\'t know", "No", "Yes")),
#                           labelOrder = c(3, 1, 2))

bikeUse <- makePlotData("Did you ride a bike in Black Rock City?",
                          varNameTable = varNameTable,
                          designs = list(design24),
                          years = c(2024),
                          levels = c(list(c("I don\'t know", "No", "Yes"))),
                          labels = c(c("I don\'t know", "No", "Yes")),
                          labelOrder = c(3, 2, 1))

ggplot(bikeUse, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "", y = "Burning Man participants in 2024 (%)",
       title = "Did you ride a bike in Black Rock City?") +
  theme_bw()

makeTableData(bikeUse) |>
  kbl(col.names = c(2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:2, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### Bike ownership

```{r}
bikeWhose <- makePlotData("Whose bike did you ride in Black Rock City?",
                          varNameTable = varNameTable,
                          designs = list(design24),
                          years = c(2024),
                          levels = c(list(c("A yellow bike", 
                                            "My own I brought to Black Rock City", 
                                            "Other",
                                            "Someone else's I borrowed with their consent",
                                            "Someone else's I borrowed without their consent"))),
                          labels = c("A yellow bike", 
                                     "My own I brought to Black Rock City", 
                                     "Other",
                                     "Someone else's I borrowed with their consent",
                                     "Someone else's I borrowed without their consent"),
                          labelOrder = rev(c(2, 4, 1, 5, 3)))

ggplot(bikeWhose, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "", y = "Burning Man participants in 2024 (%)",
       title = "Whose bike did you ride in Black Rock City?") +
  coord_flip() +
  theme_bw()

makeTableData(bikeWhose) |>
  kbl(col.names = c(2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:2, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### Needed bike repair

```{r}
bikeRepairNeed <- makePlotData("Did your bike need repair while in Black Rock City?",
                          varNameTable = varNameTable,
                          designs = list(design24),
                          years = c(2024),
                          levels = c(list(c("No", 
                                            "Other",
                                            "Yes, I was able to get it fixed",
                                            "Yes, I was unable to get it fixed"))),
                          labels = c("No", 
                                     "Other",
                                     "Yes, I was able to get it fixed",
                                     "Yes, I was unable to get it fixed"),
                          labelOrder = rev(c(3, 4, 1, 2)))

ggplot(bikeRepairNeed, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "", y = "Burning Man participants in 2024 (%)",
       title = "Did your bike need repair while in Black Rock City?") +
  theme_bw() +
  coord_flip()

makeTableData(bikeRepairNeed) |>
  kbl(col.names = c(2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:2, width_min = "10.5em") |>
  scroll_box(width = "100%")
```

### How bikes were repaired

```{r}
bikeRepairHow <- makePlotData("How did you get your bike repaired?",
                          varNameTable = varNameTable,
                          designs = list(design24),
                          years = c(2024),
                          levels = c(list(c("By a stranger (not affiliated with an identified bike repair camp)", 
                                            "By an identified bike repair camp",
                                            "By someone I know",
                                            "I did it myself",
                                            "Other"))),
                          labels = c("By a stranger",
                                     "By an identified bike repair camp",
                                     "By someone I know",
                                     "I did it myself",
                                     "Other"),
                          labelOrder = rev(c(4, 3, 2, 1, 5)))

ggplot(bikeRepairHow, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B", color = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "", y = "Burning Man participants in 2024 (%)",
       title = "How did you get your bike repaired?") +
  theme_bw() +
  coord_flip()

makeTableData(bikeRepairHow) |>
  kbl(col.names = c(2024),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:2, width_min = "10.5em") |>
  scroll_box(width = "100%")
```
