```{r, echo=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "", echo = FALSE,
                      warning = FALSE, message = FALSE)
```

# Demographics and social characteristics {#sociodemo}

```{r}
# Preparation

# Read in all years of data
library(data.table)
library(survey)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
library(weights)
library(cartogram)
library(sf)
library(tmap)
library(tigris)
library(zipcodeR)

source(paste0(getwd(), "/_RCode/read_census_data.R"))
source(paste0(getwd(), "/_RCode/make_table_data.R"))
source(paste0(getwd(), "/_RCode/make_plot_data.R"))
source(paste0(getwd(), "/_RCode/additional_functions.R"))

gradientColors <- colorRampPalette(c("#EA008B", "#B0AEDC", "#554149"))
discreteColors <- c("#EA008B", "#B0AEDC", "#554149", "#A07200", "#AADA91", 
                    "#FF8189", "#FFCF50", "#6FCFEB", "#76236C", "#FFFF3B")

```

## Burning Man attendence

### Proportion of virgins

```{r}

yearrange <- c(2013:2019, 2022:2024)

virgin <- makePlotData(varName = "Was this your first time visiting Black Rock City?", 
                       varNameTable,
                       designs = list(design13, design14, design15, 
                                      design16, design17, design18, 
                                      design19, design22, design23,
                                      design24),
                       years = yearrange,
                       levels = list(c("no", "yes"), c("no", "yes"),
                                     c("no", "yes"), c("no", "yes"),
                                     c("no", "yes"), c("no", "yes"),
                                     c("no", "yes"), c(FALSE, TRUE),
                                     c(FALSE, TRUE), c(FALSE, TRUE)),
                       labels = c("Not virgin", "Virgin"),
                       labelOrder = c("Virgin", "Not virgin"))


ggplot(virgin[virgin$labels == "Virgin",], aes(x = year, y = est)) +
  geom_line(linewidth = 1.5, color = "#EA008B", alpha = 0.7) +
  geom_point(size = 2.25, color = "#EA008B") +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = yearrange, 
                     labels = yearrange) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  labs(x = "", y = "Burning Man Participants (%)")

virginTable <- makeTableData(virgin)
virginTable <- virginTable[1,] |>
  matrix(nrow = 1) |>
  as.table()
rownames(virginTable) = "Virgin"
colnames(virginTable) = yearrange
kbl(virginTable, col.names = yearrange,
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:10, width_min = "10.5em") |>
  scroll_box(width = "100%")

```

### Number of burns attended

```{r}
ggplot(census24, 
       aes(x = numberBurns, y = after_stat(density), weight = weights)) +
  geom_histogram(fill = "#EA008B", color = "black", binwidth = 1) +
  theme_bw() +
  labs(x = "Number of burns attended (including 2024)", y = "Proportion") +
  coord_cartesian(xlim = c(0, 30))


empCDFs <- list(svycdf(~numberBurns, design24)[[1]],
                 svycdf(~nburns, design23)[[1]],
                 svycdf(~numberBurns, design22)[[1]],
                 svycdf(~nbburns, design19)[[1]],
                 svycdf(~nbburns, design18)[[1]],
                 svycdf(~nbburns, design17)[[1]],
                 svycdf(~nbburns, design16)[[1]],
                 svycdf(~nbburns, design15)[[1]],
                 svycdf(~nbburns, design14)[[1]])
names(empCDFs) <- c(2024:2022, 2019:2014)
## todo: use nbburns2-6 to add 2013 data

myQuantiles <- c(0, 1, 2, 4, 10, Inf) # account for time looping burners!
rangeNames <- c("1","2","3-4","5-10",">10")

## number burns >=2022 are inclusive, but <= 2019 are not inclusive
cumulProportions1 <- sapply(
  empCDFs[c("2024", "2023", "2022")], 
  mapply, 
  myQuantiles)
cumulProportions2 <- sapply(
  empCDFs[c("2019", "2018", "2017", "2016", "2015", "2014")], 
  mapply, 
  myQuantiles-1) # -1 to make these inclusive
cumulProportions <- cbind(cumulProportions1, cumulProportions2)

myProportions <- diff(cumulProportions)
rownames(myProportions) <- rangeNames
 
myDat <- data.frame(
  rows=factor(rownames(myProportions)[row(myProportions)],
              levels=rev(rangeNames)), 
  Year=factor(colnames(myProportions)[col(myProportions)],
              levels=2014:2024),
  Percentage=c(myProportions))

ggplot(myDat, aes(x = Year, y = Percentage, fill = rows)) + 
  geom_bar(position = "fill",stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_x_discrete(drop = FALSE) + 
  labs(fill="Number\n of burns\n attended\n (inclusive)",
       x = "") +
  scale_fill_manual(values = gradientColors(5)) +
  # scale_fill_manual(values=c("#EA008B", "#d460c7", "#bc8ce0", "#b0aedc",
  #                               "#c3c4c6")[1:5]) +
  theme_bw()
```

### Plans to Return to Black Rock City

### Reason for Returning to Black Rock City

<!-- Other ideas?  Average number of burns attended without a break? -->

## Demographics

### Age

```{r}
# ggplot(census23, aes(x = age, y = after_stat(density), weight = weights)) +
#   geom_histogram(binwidth = 1, fill = "#EA008B", color = "black") +
#   scale_x_continuous(breaks=seq(20,90,5)) + 
#   theme_bw() +
#   labs(x = "Age at arrival on playa in 2023", y = "Density")
# 
# props <- c(10, 25, 50, 75, 90)/100
# 
# ageQuantiles <- data.frame(svyquantile(~age, design23, props)[[1]][,1],
#                       svyquantile(~age, design22, props)[[1]][,1],
#                       rep("",length(props)),
#                       svyquantile(~age, design19, props)[[1]][,1],
#                       svyquantile(~age, design18, props)[[1]][,1],
#                       svyquantile(~age, design17, props)[[1]][,1],
#                       svyquantile(~age, design16, props)[[1]][,1],
#                       svyquantile(~age, design15, props)[[1]][,1],
#                       svyquantile(~age, design14, props)[[1]][,1]
#                       ) |>
# rev()
# row.names(ageQuantiles) <- paste0(props*100, "th percentile")
# ageQuantiles |>
#   kbl(col.names = c(2014:2019,"", 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   #column_spec(column = 1:9, width_min = "10.5em") |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Current gender

```{r}
#### 2022
# gender22.male <- svyciprop(~grepl("(?<!([Ff]e))[Mm]ale", currentGender, perl = TRUE),
#                            design22)
# gender22.male <- data.table(est = as.numeric(gender22.male),
#                             lower = attr(gender22.male, "ci")[1],
#                             upper = attr(gender22.male, "ci")[2],
#                             level = "male",
#                             year = 2022,
#                             labels = factor("Male",
#                                             levels = c("Male", "Female",
#                                                        "Other identity")))
# gender22.female <- svyciprop(~grepl("[Ff]emale", currentGender, perl = TRUE),
#                            design22)
# gender22.female <- data.table(est = as.numeric(gender22.female),
#                             lower = attr(gender22.female, "ci")[1],
#                             upper = attr(gender22.female, "ci")[2],
#                             level = "female",
#                             year = 2022,
#                             labels = factor("Female",
#                                             levels = c("Male", "Female",
#                                                        "Other identity")))
# gender22.other <- svyciprop(~I(!grepl("[Mm]ale", currentGender, perl = TRUE)),
#                            design22)
# gender22.other <- data.table(est = as.numeric(gender22.other),
#                             lower = attr(gender22.other, "ci")[1],
#                             upper = attr(gender22.other, "ci")[2],
#                             level = "male",
#                             year = 2022,
#                             labels = factor("Other identity",
#                                             levels = c("Male", "Female",
#                                                        "Other identity")))
# gender22 <- rbind(gender22.male, gender22.female, gender22.other)
# #### 2023
# gender23.male <- svyciprop(~grepl("(?<!([Ff]e))[Mm]ale", currentGender, perl = TRUE),
#                            design23)
# gender23.male <- data.table(est = as.numeric(gender23.male),
#                             lower = attr(gender23.male, "ci")[1],
#                             upper = attr(gender23.male, "ci")[2],
#                             level = "male",
#                             year = 2023,
#                             labels = factor("Male",
#                                             levels = c("Male", "Female",
#                                                        "Other identity")))
# gender23.female <- svyciprop(~grepl("[Ff]emale", currentGender, perl = TRUE),
#                            design23)
# gender23.female <- data.table(est = as.numeric(gender23.female),
#                             lower = attr(gender23.female, "ci")[1],
#                             upper = attr(gender23.female, "ci")[2],
#                             level = "female",
#                             year = 2023,
#                             labels = factor("Female",
#                                             levels = c("Male", "Female",
#                                                        "Other identity")))
# gender23.other <- svyciprop(~I(!grepl("[Mm]ale", currentGender, perl = TRUE)),
#                            design23)
# gender23.other <- data.table(est = as.numeric(gender23.other),
#                             lower = attr(gender23.other, "ci")[1],
#                             upper = attr(gender23.other, "ci")[2],
#                             level = "male",
#                             year = 2023,
#                             labels = factor("Other identity",
#                                             levels = c("Male", "Female",
#                                                        "Other identity")))
# gender23 <- rbind(gender23.male, gender23.female, gender23.other)
# 
# gender <- makePlotData(varName = "What is your current gender?", varNameTable,
#                           designs = list(design13, design14, design15,
#                                          design16, design17, design18,
#                                          design19),
#                           years = c(2013:2019),
#                           levels = rep(list(c("female", "fluid", "male")), times = 7),
#                           labels = c("Female", "Other identity", "Male"),
#                           labelOrder = c("Male", "Female", "Other identity"))
# gender <- gender[!is.na(gender$est),]
# gender <- rbind(gender, gender22, gender23)
# 
# ggplot(gender, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   # geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2,
#   #               linewidth = 1) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022, 2023), labels = c(2013:2019, 2022, 2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = c("#EA008B", "#554149", "#BDA5AD")) +
#   labs(x = "", y = "Burning Man participants (%)",
#        color = "Current gender")
# 
# makeTableData(gender) |>
#   kbl(col.names = c(2013:2019, 2022, 2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### Sex assigned at birth

```{r}
# sexAtBirth <- makePlotData(varName = "What sex was assigned to you at birth?",
#                            varNameTable,
#                            designs = list(design23),
#                            years = c(2023),
#                            levels = list(c("Female", "Intersex", "Male")),
#                            labels = c("Female", "Intersex", "Male"),
#                            labelOrder = rev(c("Male", "Female", "Intersex")))
# 
# ggplot(sexAtBirth, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Sex at birth", y = "Burning Man participants (%)") +
#   theme_bw()
#   # theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# makeTableData(sexAtBirth)[3:1,] |>
#   kbl(col.names = c(2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:1, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Ethnoracial background

```{r}
# ethnoracial22to23 <- makePlotData("Which category best describes your race?",
#                               varNameTable = varNameTable,
#                               designs = list(design22, design23),
#                               years = 2022:2023,
#                               levels = rep(list(TRUE), times = 2),
#                               labels = c("Asian", "Native American",
#                                          "Hispanic/Latino",
#                                          "White (non-hispanic)",
#                                          "Middle Eastern or North African",
#                                          "Black (non-Hispanic)", "Other"),
#                               labelOrder = c("White (non-hispanic)",
#                                              "Hispanic/Latino",
#                                              "Asian",
#                                              "Middle Eastern or North African",
#                                              "Black (non-Hispanic)",
#                                              "Native American", "Other"))
# ethnoracial17to19 <- makePlotData("ethnoracial 2013 through 2019",
#                               varNameTable = varNameTable,
#                               designs = list(design17, design18, design19),
#                               years = 2017:2019,
#                               levels = rep(list(c("asian", "black", "hispanic",
#                                                   "middleeastern", "native",
#                                                   "other_or_mix", "white")),
#                                            times = 3),
#                               labels = c("Asian", "Black (non-Hispanic)",
#                                          "Hispanic/Latino",
#                                          "Middle Eastern or North African",
#                                          "Native American",
#                                          "Other", "White (non-hispanic)"),
#                               labelOrder = c("White (non-hispanic)",
#                                              "Hispanic/Latino",
#                                              "Asian",
#                                              "Middle Eastern or North African",
#                                              "Black (non-Hispanic)",
#                                              "Native American", "Other"))
# 
# ethnoracial13to16 <- makePlotData("ethnoracial 2013 through 2019",
#                               varNameTable = varNameTable,
#                               designs = list(design13, design14, design15,
#                                              design16),
#                               years = 2013:2016,
#                               levels = rep(list(c("asian", "black", "hispanic",
#                                                   "native", "other_or_mix",
#                                                   "white")), times = 4),
#                               labels = c("Asian", "Black (non-Hispanic)",
#                                          "Hispanic/Latino",
#                                          "Native American",
#                                          "Other", "White (non-hispanic)"),
#                               labelOrder = c("White (non-hispanic)",
#                                              "Hispanic/Latino",
#                                              "Asian",
#                                              "Black (non-Hispanic)",
#                                              "Native American", "Other"))
# ethnoracial13to16 <- rbind(ethnoracial13to16,
#                            data.frame(est = NA, lower = NA, upper = NA,
#                                       level = "middleeastern",
#                                       year = 2013:2016,
#                                       labels = factor("Middle Eastern or North African",
#                                                       levels = c("White (non-hispanic)",
#                                                                  "Hispanic/Latino",
#                                                                  "Asian",
#                                                                  "Middle Eastern or North African",
#                                                                  "Black (non-Hispanic)",
#                                                                  "Native American", "Other"))))
# 
# ggplot(ethnoracial22to23[ethnoracial22to23$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", position = "dodge", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Ethnoracial background", y = "Burning Man participants in 2023 (%)",
#        title = "Which category best describes your race?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# tableDat <- makeTableData(rbind(ethnoracial22to23, ethnoracial17to19, ethnoracial13to16))
# tdrn <- rownames(tableDat)
# tdrn[4] <- "Middle Eastern or North African^a^"
# tdrn[7] <- "Other^b^"
# rownames(tableDat) <- tdrn
#
# tdcn <- colnames(tableDat)
#
# tdcn[8] <- "2022^c^"
#
# colnames(tableDat) <- tdcn
# 
# tableDat |>
#   kbl(col.names = c(as.character(2013:2019), "2022^c^", as.character(2023)), 
#       row.names = TRUE) |>
#   kable_paper("striped") |>
#   kable_styling(full_width = F, wraptable_width = "100%") |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   footnote(alphabet = c("Middle eastern was not an option in 2013-2016.",
#                         "The \"other or mixed\" option in 2013-2019 changed to \"other\" in 2022.",
#                         "In 2022 the format changed to allow users to select multiple options. While this improves our data collection, it unfortunately makes it impossible to make direct comparisons to previous years.")) |>
#   scroll_box(width = "100%")}
```

### Self-identification as a person of color

```{r}
# personOfColor <- makePlotData("Do you consider yourself to be a person of color?",
#                               varNameTable = varNameTable,
#                               designs = list(design13, design14, design15,
#                                              design16, design17, design18,
#                                              design19, design22, design23),
#                               years = c(2013:2019, 2022:2023),
#                               levels = c("No", "Sometimes", "Yes"),
#                               labels = c("No", "Sometimes", "Yes"),
#                               labelOrder = 1:3)
# 
# ggplot(personOfColor, aes(x = year, y = est, fill = labels)) +
#   geom_area(alpha = 0.65) +
#   scale_y_continuous(labels = percent) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_fill_manual(values = gradientColors(3)[3:1]) +
#   labs(x = "", y = "Burning Man participants (%)",
#        fill = "Person of color",
#        title = "Do you consider yourself a person of color?") +
#   theme_bw()
# 
# makeTableData(personOfColor) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")}
```

### First language learned

```{r}
# language <- makePlotData("What was the first language you learned and still use (i.e., native language)?",
#                          varNameTable = varNameTable,
#                          designs = list(design13, design14, design15,
#                                         design16, design17, design18,
#                                         design19, design22, design23),
#                          years = c(2013:2019, 2022:2023),
#                          levels = rep(list(c("Arabic", "Chinese", "Danish",
#                                              "Dutch", "English", "Farsi",
#                                              "French", "German","Hebrew",
#                                              "Hindi", "Italian", "Japanese",
#                                              "Norwegian", "Other", "Polish",
#                                              "Portuguese", "Punjabi",
#                                              "Romanian", "Russian", "Spanish",
#                                              "Swedish", "Tagalog", "Urdu")),
#                                       times = 9),
#                          labels = NULL,
#                          labelOrder = c(5, 20, 7, 8, 19, 2, 16, 4, 9, 11,
#                                         21, 6, 1, 15, 10, 3, 18, 22, 17, 12,
#                                         13, 23, 14))
# 
# language2 <- makePlotData("What was the first language you learned and still use (i.e., native language)?",
#                          varNameTable = varNameTable,
#                          designs = list(design13, design14, design15,
#                                              design16, design17, design18,
#                                              design19, design22, design23),
#                          years = c(2013:2019, 2022:2023),
#                          levels = rep(list(c("Arabic", "Chinese", "Danish",
#                                              "Dutch", "English", "Farsi",
#                                              "French", "German","Hebrew",
#                                              "Hindi", "Italian", "Japanese",
#                                              "Norwegian", "Other", "Polish",
#                                              "Portuguese", "Punjabi",
#                                              "Romanian", "Russian", "Spanish",
#                                              "Swedish", "Tagalog", "Urdu")),
#                                       times = 9),
#                          labels = c("English", "Other language"),
#                          labelOrder = 2:1,
#                          groups = c(2, 2, 2,
#                                     2, 1, 2,
#                                     2, 2, 2,
#                                     2, 2, 2,
#                                     2, 2, 2,
#                                     2, 2,
#                                     2, 2, 2,
#                                     2, 2, 2))
# 
# 
# 
# ggplot(language2, aes(x = year, y = est, fill = labels)) +
#   geom_area(alpha = 0.65) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = gradientColors(2)[2:1]) +
#   labs(x = "", y = "Burning Man participants (%)", fill = "Language",
#        title = "What was the first language you learned and still use?")
# 
# 
# makeTableData(language) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")}
```

## 

### Personal income in 2023

```{r}
# pi.lt25.23 <- customPlotDat(c("No income", "Less than $7500",
#                                  "$7,500-$14,999", "$15,000-$24,999"),
#                                design = design23, "personalIncome",
#                                2023, "Less than $25,000")
# pi.25to50.23 <- customPlotDat(c("$25,000-$34,999", "$35,000-$49,999"),
#                               design = design23, "personalIncome", 2023,
#                               "$25,000-$49,999")
# pi.50to100.23 <- customPlotDat(c("$50,000-$74,999", "$75,000-$99,999"),
#                                design = design23, "personalIncome",
#                                2023, "$50,000-$99,999")
# pi.100to300.23 <- customPlotDat(c("$100,000-$149,999", "$150,000-$299,000"),
#                                 design = design23, "personalIncome", 2023,
#                                 "$100,000-$299,999")
# pi.gt300.23 <- customPlotDat("$300,000 or more", design = design23,
#                              "personalIncome", 2023, "$300,000 or more")
# pi.23 <- rbind(pi.lt25.23, pi.25to50.23, pi.50to100.23, pi.100to300.23,
#                pi.gt300.23)
# 
# pi.lt25.22 <- customPlotDat(c("No income", "Less than $7500",
#                                  "$7,500-$14,999", "$15,000-$24,999"),
#                                design = design22, "personalIncome",
#                                2022, "Less than $25,000")
# pi.25to50.22 <- customPlotDat(c("$25,000-$34,999", "$35,000-$49,999"),
#                               design = design22, "personalIncome", 2022,
#                               "$25,000-$49,999")
# pi.50to100.22 <- customPlotDat(c("$50,000-$74,999", "$75,000-$99,999"),
#                                design = design22, "personalIncome",
#                                2022, "$50,000-$99,999")
# pi.100to300.22 <- customPlotDat(c("$100,000-$149,999", "$150,000-$299,000"),
#                                 design = design22, "personalIncome", 2022,
#                                 "$100,000-$299,999")
# pi.gt300.22 <- customPlotDat("$300,000 or more", design = design22,
#                              "personalIncome", 2022, "$300,000 or more")
# pi.22 <- rbind(pi.lt25.22, pi.25to50.22, pi.50to100.22, pi.100to300.22,
#                pi.gt300.22)
# 
# pi.lt25.19 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design19, "incomep",
#                                2019, "Less than $25,000")
# pi.25to50.19 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design19, "incomep", 2019,
#                               "$25,000-$49,999")
# pi.50to100.19 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design19, "incomep",
#                                2019, "$50,000-$99,999")
# pi.100to300.19 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design19, "incomep", 2019,
#                                 "$100,000-$299,999")
# pi.gt300.19 <- customPlotDat("_300kUS_or_more", design = design19,
#                              "incomep", 2019, "$300,000 or more")
# pi.19 <- rbind(pi.lt25.19, pi.25to50.19, pi.50to100.19, pi.100to300.19,
#                pi.gt300.19)
# 
# pi.lt25.18 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design18, "incomep",
#                                2018, "Less than $25,000")
# pi.25to50.18 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design18, "incomep", 2018,
#                               "$25,000-$49,999")
# pi.50to100.18 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design18, "incomep",
#                                2018, "$50,000-$99,999")
# pi.100to300.18 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design18, "incomep", 2018,
#                                 "$100,000-$299,999")
# pi.gt300.18 <- customPlotDat("_300kUS_or_more", design = design18,
#                              "incomep", 2018, "$300,000 or more")
# pi.18 <- rbind(pi.lt25.18, pi.25to50.18, pi.50to100.18, pi.100to300.18,
#                pi.gt300.18)
# 
# pi.lt25.17 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design17, "incomep",
#                                2017, "Less than $25,000")
# pi.25to50.17 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design17, "incomep", 2017,
#                               "$25,000-$49,999")
# pi.50to100.17 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design17, "incomep",
#                                2017, "$50,000-$99,999")
# pi.100to300.17 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design17, "incomep", 2017,
#                                 "$100,000-$299,999")
# pi.gt300.17 <- customPlotDat("_300kUS_or_more", design = design17,
#                              "incomep", 2017, "$300,000 or more")
# pi.17 <- rbind(pi.lt25.17, pi.25to50.17, pi.50to100.17, pi.100to300.17,
#                pi.gt300.17)
# 
# pi.lt25.16 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design16, "incomep",
#                                2016, "Less than $25,000")
# pi.25to50.16 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design16, "incomep", 2016,
#                               "$25,000-$49,999")
# pi.50to100.16 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design16, "incomep",
#                                2016, "$50,000-$99,999")
# pi.100to300.16 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design16, "incomep", 2016,
#                                 "$100,000-$299,999")
# pi.gt300.16 <- customPlotDat("_300kUS_or_more", design = design16,
#                              "incomep", 2016, "$300,000 or more")
# pi.16 <- rbind(pi.lt25.16, pi.25to50.16, pi.50to100.16, pi.100to300.16,
#                pi.gt300.16)
# 
# pi.lt25.15 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design15, "incomep",
#                                2015, "Less than $25,000")
# pi.25to50.15 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design15, "incomep", 2015,
#                               "$25,000-$49,999")
# pi.50to100.15 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design15, "incomep",
#                                2015, "$50,000-$99,999")
# pi.100to300.15 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design15, "incomep", 2015,
#                                 "$100,000-$299,999")
# pi.gt300.15 <- customPlotDat("_300kUS_or_more", design = design15,
#                              "incomep", 2015, "$300,000 or more")
# pi.15 <- rbind(pi.lt25.15, pi.25to50.15, pi.50to100.15, pi.100to300.15,
#                pi.gt300.15)
# 
# pi.allYears <- rbind(pi.23, pi.22, pi.19, pi.18, pi.17, pi.16, pi.15)
# pi.allYears$labels <- factor(pi.allYears$labels,
#                              levels = c("Less than $25,000",
#                                         "$25,000-$49,999",
#                                         "$50,000-$99,999",
#                                         "$100,000-$299,999",
#                                         "$300,000 or more"))
# 
# ggplot(pi.allYears, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   # geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2,
#   #               linewidth = 1) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = gradientColors(5)) +
#   labs(x = "", y = "Burning Man participants (%)", color = "Personal income (USD)")
# 
# ## note: varName below should refer to previous burn year
# personalIncome <- makePlotData(varName = "What was your personal income in 2022 before taxes? Give your best estimate. Please do not include your spouse's income as your own.",
#                          varNameTable,
#                          designs = list(design15, design16, design17, design18,
#                                         design19, design22, design23),
#                          years = c(2015:2019, 2022:2023),
#                          levels = c(rep(list(c("_100k_149999US",
#                                                "_15000_24999US",
#                                                "_150k_299999US",
#                                                "_25000_34999US",
#                                                "_300kUS_or_more",
#                                                "_35000_49999US",
#                                                "_50000_74999US",
#                                                "_7500_14999US",
#                                                "_75000_99999US",
#                                                "Less_than_7500US",
#                                                "None")), times  = 5),
#                                     rep(list(c("$100,000-$149,999", "$15,000-$24,999",
#                                     "$150,000-$299,000", "$25,000-$34,999",
#                                     "$300,000 or more", "$35,000-$49,999",
#                                     "$50,000-$74,999", "$7,500-$14,999",
#                                     "$75,000-$99,999", "Less than $7500",
#                                     "No income")), times = 2)),
#                          labels = c("$100,000-$149,999", "$15,000-$24,999",
#                                     "$150,000-$299,000", "$25,000-$34,999",
#                                     "$300,000 or more", "$35,000-$49,999",
#                                     "$50,000-$74,999", "$7,500-$14,999",
#                                     "$75,000-$99,999", "Less than $7,500",
#                                     "No income"),
#                          labelOrder = c("No income", "Less than $7,500",
#                                         "$7,500-$14,999", "$15,000-$24,999",
#                                         "$25,000-$34,999", "$35,000-$49,999",
#                                         "$50,000-$74,999", "$75,000-$99,999",
#                                         "$100,000-$149,999", "$150,000-$299,000",
#                                         "$300,000 or more"))
# 
# 
# makeTableData(personalIncome) |>
#   kbl(col.names = c(2015:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Household income in 2023

```{r}
# hi.lt25.23 <- customPlotDat(c("No income", "Less than $7500",
#                                  "$7,500-$14,999", "$15,000-$24,999"),
#                                design = design23, "householdIncome",
#                                2023, "Less than $25,000")
# hi.25to50.23 <- customPlotDat(c("$25,000-$34,999", "$35,000-$49,999"),
#                               design = design23, "householdIncome", 2023,
#                               "$25,000-$49,999")
# hi.50to100.23 <- customPlotDat(c("$50,000-$74,999", "$75,000-$99,999"),
#                                design = design23, "householdIncome",
#                                2023, "$50,000-$99,999")
# hi.100to300.23 <- customPlotDat(c("$100,000-$149,999", "$150,000-$299,000"),
#                                 design = design23, "householdIncome", 2023,
#                                 "$100,000-$299,999")
# hi.gt300.23 <- customPlotDat("$300,000 or more", design = design23,
#                              "householdIncome", 2023, "$300,000 or more")
# hi.23 <- rbind(hi.lt25.23, hi.25to50.23, hi.50to100.23, hi.100to300.23,
#                hi.gt300.23)
# 
# hi.lt25.22 <- customPlotDat(c("No income", "Less than $7500",
#                                  "$7,500-$14,999", "$15,000-$24,999"),
#                                design = design22, "householdIncome",
#                                2022, "Less than $25,000")
# hi.25to50.22 <- customPlotDat(c("$25,000-$34,999", "$35,000-$49,999"),
#                               design = design22, "householdIncome", 2022,
#                               "$25,000-$49,999")
# hi.50to100.22 <- customPlotDat(c("$50,000-$74,999", "$75,000-$99,999"),
#                                design = design22, "householdIncome",
#                                2022, "$50,000-$99,999")
# hi.100to300.22 <- customPlotDat(c("$100,000-$149,999", "$150,000-$299,000"),
#                                 design = design22, "householdIncome", 2022,
#                                 "$100,000-$299,999")
# hi.gt300.22 <- customPlotDat("$300,000 or more", design = design22,
#                              "householdIncome", 2022, "$300,000 or more")
# hi.22 <- rbind(hi.lt25.22, hi.25to50.22, hi.50to100.22, hi.100to300.22,
#                hi.gt300.22)
# 
# hi.lt25.19 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design19, "incomeh",
#                                2019, "Less than $25,000")
# hi.25to50.19 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design19, "incomeh", 2019,
#                               "$25,000-$49,999")
# hi.50to100.19 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design19, "incomeh",
#                                2019, "$50,000-$99,999")
# hi.100to300.19 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design19, "incomeh", 2019,
#                                 "$100,000-$299,999")
# hi.gt300.19 <- customPlotDat("_300kUS_or_more", design = design19,
#                              "incomeh", 2019, "$300,000 or more")
# hi.19 <- rbind(hi.lt25.19, hi.25to50.19, hi.50to100.19, hi.100to300.19,
#                hi.gt300.19)
# 
# hi.lt25.18 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design18, "incomeh",
#                                2018, "Less than $25,000")
# hi.25to50.18 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design18, "incomeh", 2018,
#                               "$25,000-$49,999")
# hi.50to100.18 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design18, "incomeh",
#                                2018, "$50,000-$99,999")
# hi.100to300.18 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design18, "incomeh", 2018,
#                                 "$100,000-$299,999")
# hi.gt300.18 <- customPlotDat("_300kUS_or_more", design = design18,
#                              "incomeh", 2018, "$300,000 or more")
# hi.18 <- rbind(hi.lt25.18, hi.25to50.18, hi.50to100.18, hi.100to300.18,
#                hi.gt300.18)
# 
# hi.lt25.17 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design17, "incomeh",
#                                2017, "Less than $25,000")
# hi.25to50.17 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design17, "incomeh", 2017,
#                               "$25,000-$49,999")
# hi.50to100.17 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design17, "incomeh",
#                                2017, "$50,000-$99,999")
# hi.100to300.17 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design17, "incomeh", 2017,
#                                 "$100,000-$299,999")
# hi.gt300.17 <- customPlotDat("_300kUS_or_more", design = design17,
#                              "incomeh", 2017, "$300,000 or more")
# hi.17 <- rbind(hi.lt25.17, hi.25to50.17, hi.50to100.17, hi.100to300.17,
#                hi.gt300.17)
# 
# hi.lt25.16 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design16, "incomeh",
#                                2016, "Less than $25,000")
# hi.25to50.16 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design16, "incomeh", 2016,
#                               "$25,000-$49,999")
# hi.50to100.16 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design16, "incomeh",
#                                2016, "$50,000-$99,999")
# hi.100to300.16 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design16, "incomeh", 2016,
#                                 "$100,000-$299,999")
# hi.gt300.16 <- customPlotDat("_300kUS_or_more", design = design16,
#                              "incomeh", 2016, "$300,000 or more")
# hi.16 <- rbind(hi.lt25.16, hi.25to50.16, hi.50to100.16, hi.100to300.16,
#                hi.gt300.16)
# 
# hi.lt25.15 <- customPlotDat(c("None", "Less_than_7500US",
#                                  "_7500_14999US", "_15000_24999US"),
#                                design = design15, "incomeh",
#                                2015, "Less than $25,000")
# hi.25to50.15 <- customPlotDat(c("_25000_34999US", "_35000_49999US"),
#                               design = design15, "incomeh", 2015,
#                               "$25,000-$49,999")
# hi.50to100.15 <- customPlotDat(c("_50000_74999US", "_75000_99999US"),
#                                design = design15, "incomeh",
#                                2015, "$50,000-$99,999")
# hi.100to300.15 <- customPlotDat(c("_100k_149999US", "_150k_299999US"),
#                                 design = design15, "incomeh", 2015,
#                                 "$100,000-$299,999")
# hi.gt300.15 <- customPlotDat("_300kUS_or_more", design = design15,
#                              "incomeh", 2015, "$300,000 or more")
# hi.15 <- rbind(hi.lt25.15, hi.25to50.15, hi.50to100.15, hi.100to300.15,
#                hi.gt300.15)
# 
# hi.allYears <- rbind(hi.23, hi.22, hi.19, hi.18, hi.17, hi.16, hi.15)
# hi.allYears$labels <- factor(hi.allYears$labels,
#                              levels = c("Less than $25,000",
#                                         "$25,000-$49,999",
#                                         "$50,000-$99,999",
#                                         "$100,000-$299,999",
#                                         "$300,000 or more"))
# 
# ggplot(hi.allYears, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   # geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2,
#   #               linewidth = 1) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = gradientColors(5)) +
#   labs(x = "", y = "Burning Man participants (%)", color = "Household income (USD)")
# 
# householdIncome <- makePlotData(varName = "What was the total income before taxes of all members of your household (including you) in 2022?",
#                          varNameTable,
#                          designs = list(design15, design16, design17, design18,
#                                         design19, design22, design23),
#                          years = c(2015:2019, 2022:2023),
#                          levels = c(rep(list(c("_100k_149999US",
#                                                "_15000_24999US",
#                                                "_150k_299999US",
#                                                "_25000_34999US",
#                                                "_300kUS_or_more",
#                                                "_35000_49999US",
#                                                "_50000_74999US",
#                                                "_7500_14999US",
#                                                "_75000_99999US",
#                                                "Less_than_7500US",
#                                                "None")), times  = 5),
#                                     rep(list(c("$100,000-$149,999", "$15,000-$24,999",
#                                     "$150,000-$299,000", "$25,000-$34,999",
#                                     "$300,000 or more", "$35,000-$49,999",
#                                     "$50,000-$74,999", "$7,500-$14,999",
#                                     "$75,000-$99,999", "Less than $7500",
#                                     "No income")), times=2)),
#                          labels = c("$100,000-$149,999", "$15,000-$24,999",
#                                     "$150,000-$299,000", "$25,000-$34,999",
#                                     "$300,000 or more", "$35,000-$49,999",
#                                     "$50,000-$74,999", "$7,500-$14,999",
#                                     "$75,000-$99,999", "Less than $7,500",
#                                     "No income"),
#                          labelOrder = c("No income", "Less than $7,500",
#                                         "$7,500-$14,999", "$15,000-$24,999",
#                                         "$25,000-$34,999", "$35,000-$49,999",
#                                         "$50,000-$74,999", "$75,000-$99,999",
#                                         "$100,000-$149,999", "$150,000-$299,000",
#                                         "$300,000 or more"))
# 
# makeTableData(householdIncome) |>
#   kbl(col.names = c(2015:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Highest level of education completed

<!-- need to create 2022 variable for highest level completed to compare to prior years -->

```{r}
# education <- makePlotData(varName = "Which level of education have you completed?",
#                           varNameTable,
#                           designs = list(design23),
#                           years = c(2023),
#                           levels = c(TRUE),
#                           labels = c("High school diploma \n or equivalent",
#                                      "Some college",
#                                      "Associate's degree",
#                                      "Bachelor's degree",
#                                      "Graduate degree (Master's, \n Doctorate, or equivalent)",
#                                      "Technical/vocational \n certification",
#                                      "Other",
#                                      "None of these"),
#                           labelOrder = c("High school diploma \n or equivalent",
#                                          "Some college",
#                                          "Associate's degree",
#                                          "Bachelor's degree",
#                                          "Graduate degree (Master's, \n Doctorate, or equivalent)",
#                                          "Technical/vocational \n certification",
#                                          "Other",
#                                          "None of these"))
# 
# ggplot(education, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Level of education competed", 
#        y = "Burning Man participants in 2023 (%)",
#        title = "Which level of education have you completed?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
# 
# makeTableData(education) |>
#   kbl(col.names = c(2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:1, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

## Residence

<!-- ### Residence inside of Black Rock City -->

<!-- I didn't get to this last year.  Some sort of mapping would be great -->

```{r}

# library(ggmap)
# library(RColorBrewer)
# 
# BRCMap <- get_map(location = "Black Rock City, NV",
#                   source = "stamen", maptype = "toner-lite",
#                   crop = TRUE, zoom = 2)
```

### Residence outside of Black Rock City

```{r}

# theZipz <- census23$reside.ZIP
# 
# theZipz[nchar(theZipz) >5 & !is.na(theZipz)] <- gsub(
#   "-.{4}$",
#   "",
#   theZipz[nchar(theZipz) >5 & !is.na(theZipz)]
# ) # remove last 4 of zip codes
# 
# Zs <- lapply(theZipz, function(u){
#   if (is.na(u)) {
#     NA
#   } else {
#     reverse_zipcode(u)
#   }
# }
# )
# 
# burnerState <- sapply(Zs, function(v){
#   if (length(v)>1) {
#     v$state
#   } else {
#     NA
#   }
# }
# )
# 
# statesWeights <- tapply(census23$weights, burnerState, sum)
# statesWeights <- statesWeights/sum(statesWeights)*100
# 
# statesPercents <- sort(round(statesWeights,2), decreasing=TRUE) # weighted
# 
# burnersByState <- data.frame(STATE = names(statesPercents), Percent = statesPercents)
# 
# # adding mississippi
# burnersByState <- rbind(burnersByState, data.frame(STATE="MS",Percent=0))
# 
# ## plotting
# usa <- states(cb = TRUE, progress_bar = FALSE) %>%
#   shift_geometry()
# 
# usa$STATE <- c(state.abb, "DC", "PR")[
#   match(usa$NAME, c(state.name, "District of Columbia", "Puerto Rico"),)
#   ]
# 
# usa2 <- merge(usa, burnersByState, by="STATE")
# 
# usa2 <- st_transform(usa2, 3395)
# 
# # construct cartogram
# usa2_cont <- cartogram_cont(usa2, "Percent", 
#                             itermax = 15,
#                             threshold = 0.01,
#                             verbose=FALSE) %>%
#   st_cast()
# 
# # plot it
# tm_shape(usa2_cont) + 
#   tm_polygons("Percent", style = "jenks", 
#               palette=gradientColors(3)) +
#   tm_layout("Frequency of US residence",title.position=c(0.5, 0.9),
#             frame = FALSE, legend.position = c(0.8,0.1),
#             legend.outside=FALSE) + 
#   tm_text("STATE", size = 1/2, remove.overlap = FALSE)
# 
# ## table of 
# 
# # names(statesPercents) <- c(state.name, "District of Columbia", "Puerto Rico")[
# #   match(names(statesPercents), c(state.abb, "DC", "PR"),)
# # ]
# # 
# # head(data.frame(statesPercents),12) |>
# #   kbl(col.names = c("Percentage"), row.names = TRUE) |>
# #   kable_paper("striped", full_width = F) |>
# #   kable_styling() |>
# #   column_spec(column = 1:1, width_min = "10.5em") |>
# #   scroll_box(width = "100%")
# 
# 
# 
# reside <- makePlotData("Where do you usually reside/live (when not in Black Rock City)?",
#                        varNameTable = varNameTable,
#                        designs = list(design13, design14, design15,
#                                       design16, design17, design18,
#                                       design19, design22, design23),
#                        years = c(2013:2019, 2022:2023),
#                        levels = c(rep(list(c("California",
#                                              "Canada",
#                                              "Nevada",
#                                              "Other",
#                                              "USA_other")), times = 7),
#                                   rep(list(c("Within California", "In Canada",
#                                          "Within Nevada", "Other",
#                                          "Other location within U.S.")), times = 2)),
#                        labels = c("Within California", "Within Canada",
#                                   "Within Nevada", "Other",
#                                   "Other location within U.S."),
#                        labelOrder = c(1, 3, 5, 2, 4))
# 
# ggplot(reside, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors[1:5]) +
#   labs(x = "", y = "Burning Man participants (%)", 
#        color = "Residence (not in BRC)",
#        title = "Where do you usually reside (when not in Black Rock City)")
# 
# makeTableData(reside) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

<!-- ### California and Nevada County Residence -->

<!-- ZIP Code converted to county and maybe smoothed -->

<!-- ### State residence -->

<!-- ZIP code converted to state -->

<!-- ### Canadian province residence -->

<!-- Postal code converted to province -->

<!-- ## Voting and politics -->

### Number of times voted in last four Federal US elections

<!-- Combine with voting eligiblity -->

<!-- Need to revisit this one when I have more time.  Probably separate -->

<!-- voter eligibility breakdowns and a lasagna plot for number of votes -->

<!-- would be better. -->

```{r}
# voteEligible <- makePlotData(varName = "Are you eligible to vote in the United States?",
#                              varNameTable,
#                              designs = list(design13, design14, design15,
#                                             design16, design17, design18,
#                                             design19, design22, design23),
#                              years = c(2013:2019, 2022:2023),
#                              levels = rep(list(c("no", "yes")), times = 9),
#                              labels = c("Not eligible to vote", "Eligible"),
#                              labelOrder = 1:2)
# numberVotes <- makePlotData(varName = "Number of the last four Federal US elections voted among eligible voters?",
#                             varNameTable = varNameTable,
#                             designs = list(design13, design14, design15,
#                                             design16, design17, design18,
#                                             design19, design22, design23),
#                             years = c(2013:2019, 2022:2023),
#                             levels = rep(list(as.character(0:4)), times = 9),
#                             labels = c("Did not vote", "1 election",
#                                        "2 elections", "3 elections",
#                                        "4 elections"),
#                             labelOrder = c(2:4,1,5))
# numberVotes$est <- numberVotes$est * rep(voteEligible$est[voteEligible$labels == "Eligible"], each = 5)
# numberVotes$lower <- numberVotes$lower * rep(voteEligible$est[voteEligible$labels == "Eligible"], each = 5)
# numberVotes$upper <- numberVotes$upper * rep(voteEligible$est[voteEligible$labels == "Eligible"], each = 5)
# numberVotes$labels <- as.character(numberVotes$labels)
# voteEligible$labels <- as.character(voteEligible$labels)
# numberVotes <- rbind(numberVotes, voteEligible[voteEligible$labels == "Not eligible to vote",])
# numberVotes$labels <- factor(numberVotes$labels, levels = c("Did not vote",
#                                                             "1 election",
#                                                             "2 elections",
#                                                             "3 elections",
#                                                             "4 elections",
#                                                             "Not eligible to vote"))
# 
# ggplot(numberVotes, aes(x = year, y = est, fill = labels)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   # geom_line(linewidth = 1.5, alpha = 0.7) +
#   # geom_point(size = 2.25) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_fill_manual(values = gradientColors(6)[c(5:1,6)]) +
#   labs(x = "", y = "Burning Man participants (%)", 
#        labels = "Number of elections voted",
#        title = "How many of the last four US elections did you vote in?")
# 
# makeTableData(numberVotes) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Political party affiliation

```{r}
# politicalParty <- makePlotData("With which political party are you currently affiliated in the United States, if any?",
#                                varNameTable = varNameTable,
#                                designs = list(design17, design18, design19,
#                                               design22, design23),
#                                years = c(2017:2019, 2022:2023),
#                                levels = c(rep(list(c("Democratic", "Green",
#                                                      "Libertarian", "None",
#                                                      "Other", "Republican")),
#                                               times = 3),
#                                           rep(list(c("Democratic Party", "Green Party",
#                                             "Libertarian Party", "None or unaffiliated",
#                                             "Other US Party", "Republican Party")), times = 2)),
#                                labels = c("Democratic Party", "Green Party",
#                                           "Libertarian Party", "None or unaffiliated",
#                                           "Other US Party", "Republican Party"),
#                                labelOrder = c("Democratic Party", "Republican Party",
#                                               "Libertarian Party", "Green Party",
#                                               "Other US Party", "None or unaffiliated"))
# 
# 
# party.dem.16 <- customPlotDat(c("Democratic"),
#                               design = design16, "usparty",
#                               2016, "Democratic Party")
# party.rep.16 <- customPlotDat(c("Republican"),
#                               design = design16, "usparty",
#                               2016, "Republican Party")
# party.lib.16 <- customPlotDat(c("Libertarian"),
#                               design = design16, "usparty",
#                               2016, "Libertarian Party")
# party.grn.16 <- customPlotDat(c("Green"),
#                               design = design16, "usparty",
#                               2016, "Green Party")
# party.oth.16 <- customPlotDat(c("Other", "Am_Indep_Party"),
#                               design = design16, "usparty",
#                               2016, "Other US Party")
# party.nne.16 <- customPlotDat(c("None"),
#                               design = design16, "usparty",
#                               2016, "None or unaffiliated")
# party.dem.15 <- customPlotDat(c("Democratic"),
#                               design = design15, "usparty",
#                               2015, "Democratic Party")
# party.rep.15 <- customPlotDat(c("Republican"),
#                               design = design15, "usparty",
#                               2015, "Republican Party")
# party.lib.15 <- customPlotDat(c("Libertarian"),
#                               design = design15, "usparty",
#                               2015, "Libertarian Party")
# party.grn.15 <- customPlotDat(c("Green"),
#                               design = design15, "usparty",
#                               2015, "Green Party")
# party.oth.15 <- customPlotDat(c("Other", "Am_Indep_Party"),
#                               design = design15, "usparty",
#                               2015, "Other US Party")
# party.nne.15 <- customPlotDat(c("None"),
#                               design = design15, "usparty",
#                               2015, "None or unaffiliated")
# party.dem.14 <- customPlotDat(c("Democratic"),
#                               design = design14, "usparty",
#                               2014, "Democratic Party")
# party.rep.14 <- customPlotDat(c("Republican"),
#                               design = design14, "usparty",
#                               2014, "Republican Party")
# party.lib.14 <- customPlotDat(c("Libertarian"),
#                               design = design14, "usparty",
#                               2014, "Libertarian Party")
# party.grn.14 <- customPlotDat(c("Green"),
#                               design = design14, "usparty",
#                               2014, "Green Party")
# party.oth.14 <- customPlotDat(c("Other", "Am_Indep_Party"),
#                               design = design14, "usparty",
#                               2014, "Other US Party")
# party.nne.14 <- customPlotDat(c("None"),
#                               design = design14, "usparty",
#                               2014, "None or unaffiliated")
# party.dem.13 <- customPlotDat(c("Democratic"),
#                               design = design13, "usparty",
#                               2013, "Democratic Party")
# party.rep.13 <- customPlotDat(c("Republican"),
#                               design = design13, "usparty",
#                               2013, "Republican Party")
# party.lib.13 <- customPlotDat(c("Libertarian"),
#                               design = design13, "usparty",
#                               2013, "Libertarian Party")
# party.grn.13 <- customPlotDat(c("Green"),
#                               design = design13, "usparty",
#                               2013, "Green Party")
# party.oth.13 <- customPlotDat(c("Other", "Am_Indep_Party"),
#                               design = design13, "usparty",
#                               2013, "Other US Party")
# party.nne.13 <- customPlotDat(c("None"),
#                               design = design13, "usparty",
#                               2013, "None or unaffiliated")
# pp16 <- rbind(party.dem.16, party.rep.16, party.lib.16,
#               party.grn.16, party.oth.16, party.nne.16)
# pp16$est <- pp16$est / sum(pp16$est)
# pp16$lower <- pp16$lower / sum(pp16$est)
# pp16$upper <- pp16$upper / sum(pp16$est)
# 
# pp15 <- rbind(party.dem.15, party.rep.15, party.lib.15,
#               party.grn.15, party.oth.15, party.nne.15)
# pp15$est <- pp15$est / sum(pp15$est)
# pp15$lower <- pp15$lower / sum(pp15$est)
# pp15$upper <- pp15$upper / sum(pp15$est)
# 
# 
# pp14 <- rbind(party.dem.14, party.rep.14, party.lib.14,
#               party.grn.14, party.oth.14, party.nne.14)
# pp14$est <- pp14$est / sum(pp14$est)
# pp14$lower <- pp14$lower / sum(pp14$est)
# pp14$upper <- pp14$upper / sum(pp14$est)
# 
# pp13 <- rbind(party.dem.13, party.rep.13, party.lib.13,
#               party.grn.13, party.oth.13, party.nne.13)
# pp13$est <- pp13$est / sum(pp13$est)
# pp13$lower <- pp13$lower / sum(pp13$est)
# pp13$upper <- pp13$upper / sum(pp13$est)
# 
# 
# 
# politicalParty <- rbind(politicalParty, pp16, pp15, pp14, pp13)
# 
# ggplot(politicalParty, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5) +
#   geom_point(size = 2.25, color = "black") +
#   # geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2,
#   #               linewidth = 1) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors[c(1:3,5,4,6)]) +
#   labs(x = "", y = "Burning Man participants eligible to vote (%)", 
#        color = "US politcal party \n affiliation",
#        title = "With which political party are you currently affiliated \n in the United States, if any?")
# 
# makeTableData(politicalParty) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Political views

```{r}
# politicalViews <- makePlotData("Generally, in terms of political views, rather than political parties, I consider myself to be primarily",
#                                varNameTable = varNameTable,
#                                designs = list(design19, design22, design23),
#                                years = c(2019, 2022, 2023),
#                                levels = c(list(c("Anarchist",
#                                                  "Centrist_or_moderate",
#                                                  "Conservative", "Green",
#                                                  "Liberal", "Libertarian",
#                                                  "Non_political", "Other",
#                                                  "Progressive", "Socialist")),
#                                           rep(list(c("Anarchist",
#                                                  "Centrist or moderate",
#                                                  "Conservative", "Green",
#                                                  "Liberal", "Libertarian",
#                                                  "None or non-political",
#                                                  "Other", "Progressive",
#                                                  "Socialist")), times = 2)),
#                                labels = c("Anarchist",
#                                           "Centrist or moderate",
#                                           "Conservative", "Green",
#                                           "Liberal", "Libertarian",
#                                           "None or non-political",
#                                           "Other", "Progressive",
#                                           "Socialist"),
#                                labelOrder = c("Liberal", "Progressive",
#                                               "Socialist", "Green",
#                                               "Centrist or moderate",
#                                               "Conservative", "Libertarian",
#                                               "Anarchist",
#                                               "None or non-political",
#                                               "Other"))
# 
# ggplot(politicalViews, aes(x = labels, y = est, fill = as.factor(year))) +
#   geom_bar(stat = "identity", position = "dodge") +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = discreteColors[1:3]) +
#   labs(x = "Political view", y = "Burning Man participants (%)", fill = "Year",
#        title = "Generally, in terms of political views, rather than political parties, \n I consider  myself to be primarily...") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# makeTableData(politicalViews) |>
#   kbl(col.names = c(2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:4, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

## Spirituality

### How do you describe your spirituality?

```{r}
# spirituality <- makePlotData("How do you describe your spirituality?",
#                              varNameTable = varNameTable,
#                              designs = list(design13, design14, design15,
#                                                  design16, design17, design18,
#                                                  design19, design22, design23),
#                              years = c(2013:2019, 2022:2023),
#                              levels = c(rep(list(c("Agnostic", "Atheist", "Deist",
#                                                    "IDK", "Religious",
#                                                    "Spiritual_not_relig")),
#                                           times = 7),
#                                         rep(list(c("Agnostic", "Atheist", "Deist",
#                                                "Don\'t know", "Religious",
#                                                "Spiritual, but not religious")), times = 2)),
#                              labels = c("Agnostic", "Atheist", "Deist",
#                                         "I don\'t know", "Religious",
#                                         "Spiritual, but \n not religious"),
#                              labelOrder = c(6, 2, 1, 5, 3, 4))
# 
# ggplot(spirituality, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors[1:6]) +
#   labs(x = "", y = "Burning Man participants (%)", color = "Language",
#        "How do you describe your spirituality?")
# 
# makeTableData(spirituality) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

## Sexuality and Relationships

### Sexual orientation

```{r}
# sexualOrientation <- makePlotData("Which of these expressions best describes your sexual orientation?",
#              varNameTable = varNameTable,
#              designs = list(design22, design23),
#              years = 2022:2023,
#              levels = c("Asexual", "Bicurious or heteroflexible",
#                         "Bisexual or pansexual", "Demi-sexual",
#                         "Gay, lesbian, or homosexual",
#                         "Heterosexual or straight",
#                         "Other", "Refuse labels"),
#              labels = c("Asexual", "Bicurious or \n heteroflexible",
#                         "Bisexual or \n pansexual", "Demi-sexual",
#                         "Gay, lesbian, or \n homosexual",
#                         "Heterosexual or \n straight",
#                         "Other", "Refuse labels"),
#              labelOrder = rev(c(6, 3, 2, 5, 1, 4, 8, 7)))
# 
# sexualOrientation2 <- makePlotData("Which of these expressions best describes your sexual orientation?",
#              varNameTable = varNameTable,
#              designs = list(design13, design14, design15, design16, design17,
#                             design18, design19),
#              years = 2013:2019,
#              levels = rep(list(c("Asexual", "Bicurious",
#                         "Bisexual", "demisexual", "Gay_Lesbian",
#                         "Heterosexual", "other", "Refuse_labels")), times = 7),
#              labels = c("Asexual", "Bicurious or \n heteroflexible",
#                         "Bisexual or \n pansexual", "Demi-sexual",
#                         "Gay, lesbian, or \n homosexual",
#                         "Heterosexual or \n straight",
#                         "Other", "Refuse labels"),
#              labelOrder = c(6, 3, 2, 5, 1, 4, 8, 7))
# 
# ggplot(sexualOrientation[sexualOrientation$year == 2023,], 
#        aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Sexual orientation", y = "Burning Man participants in 2023 (%)",
#        title = "Which of these expressions best describes your sexual orientation?") +
#   theme_bw() +
#   coord_flip()
# 
# allSexualOrientation <- rbind(sexualOrientation2, sexualOrientation)
# 
# makeTableData(allSexualOrientation) |>
#   kbl(col.names = c(2013:2019, "2022^c^", 2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   footnote(alphabet = c("\'Demi-sexual\' and \'Other\' choices were added in 2022.")) |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Sexuality labels

```{r}
# design19$variables$graysex[design19$variables$graysex == 11] <- "yes"
# sexuality <- makePlotData("Some people use specific labels to describe their sexuality. Do you consider that one or more of these labels describe your sexuality?",
#                            varNameTable = varNameTable,
#                            designs = list(design15, design16, design17, 
#                                           design18, design19, design22, 
#                                           design23),
#                            years = c(2015:2019, 2022:2023),
#                            levels = c(as.list(rep("yes", times = 5)),
#                                       as.list(rep(TRUE, times = 2))),
#                            labels = c("Kinkster or BDSM participant",
#                                       "Swinger",
#                                       "Sex worker",
#                                       "Gray-sexual or demisexual",
#                                       "Queer",
#                                       "Sex/love addict",
#                                       "Open/curious",
#                                       "Other"),
#                           labelOrder = c(8, 3, 4, 2, 6, 5, 1, 7))
# 
# 
# 
# # sexuality <- sexuality[!(sexuality$labels %in% c("Monogamous",
# #                                                  "Mostly monogamous",
# #                                                  "Polyamorous",
# #                                                  "Relationship anarchist")),]
# # sexuality$labels <- factor(sexuality$labels, levels = c("Other",
# #                                                         "Sex worker",
# #                                                         "Gray-sexual or demisexual",
# #                                                         "Swinger",
# #                                                         "Sex/love addict",
# #                                                         "Queer",
# #                                                         "Kinkster or BDSM participant",
# #                                                         "Open/curious"))
# 
# ggplot(sexuality[sexuality$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Sexuality label", y = "Burning Man participants in 2023 (%)") +
#   theme_bw() +
#   coord_flip()
# 
# makeTableData(sexuality)[8:1,] |>
#   kbl(col.names = c(2015:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Partner in the default world

```{r}
# partner <- makePlotData("In the default world, do you have a partner or partners?",
#                         varNameTable = varNameTable,
#                         designs = list(design15, design16, design17,
#                                        design18, design19, design22,
#                                        design23),
#                         years = c(2015:2019, 2022:2023),
#                         levels = c(rep(list(c("Its_complicated", "No",
#                                               "Married", "In_relationship")),
#                                        times = 5),
#                                    rep(list(c("It\'s complicated", "No",
#                                           "Yes and we are married",
#                                           "Yes and we are not married")), times = 2)),
#                         labels = c("It\'s complicated",
#                                    "No, I am not in a relationship",
#                                    "Yes, and we are married",
#                                    "Yes, and we are not married"),
#                         labelOrder = c(3, 4, 2, 1))
# 
# ggplot(partner, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors[1:7]) +
#   labs(x = "", y = "Burning Man participants (%)", 
#        color = "Do you have a partner?",
#        title = "In the default world, do you have a partner or partners?")
# 
# makeTableData(partner) |>
#   kbl(col.names = c(2015:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```
