```{r echo=FALSE}
#| label: set-options
knitr::opts_chunk$set(fig.pos = "H", out.extra = "", echo = FALSE,
                      warning = FALSE, message = FALSE)
```

# Demographics and social characteristics {#sociodemo}

```{r}
#| label: prep
# Preparation

# Read in all years of data
library(data.table)
library(survey)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
library(weights)
library(cartogram)
library(sf)
library(tmap)
library(zipcodeR) # for reverse_zipcode function
options(tigris_use_cache = TRUE) # saves time when running this a bunch
library(tigris)   # to shift and rescale AK, HI, PR via shift_geometry
library(tidytext)
library(wordcloud2)
library(purrr)
library(dplyr)

source(paste0(getwd(), "/_RCode/read_census_data.R"))
source(paste0(getwd(), "/_RCode/make_table_data.R"))
source(paste0(getwd(), "/_RCode/make_plot_data.R"))
source(paste0(getwd(), "/_RCode/additional_functions.R"))
source(paste0(getwd(), "/_RCode/geo_tabulate_zip.R"))

gradientColors <- colorRampPalette(c("#EA008B", "#B0AEDC", "#554149"))
discreteColors <- c("#EA008B", "#B0AEDC", "#554149", "#A07200", "#AADA91", 
                    "#FF8189", "#FFCF50", "#6FCFEB", "#76236C", "#FFFF3B")

```

## Burning Man attendance

### Proportion of virgins

```{r}
#| label: attendance-virgins

yearrange <- c(2013:2019, 2022:2024)

# virgin <- makePlotData(varName = "Was this your first time visiting Black Rock City?", 
#                        varNameTable,
#                        designs = list(design13, design14, design15, 
#                                       design16, design17, design18, 
#                                       design19, design22, design23,
#                                       design24),
#                        years = yearrange,
#                        levels = list(c("no", "yes"), c("no", "yes"),
#                                      c("no", "yes"), c("no", "yes"),
#                                      c("no", "yes"), c("no", "yes"),
#                                      c("no", "yes"), c(FALSE, TRUE),
#                                      c(FALSE, TRUE), c(FALSE, TRUE)),
#                        labels = c("Not virgin", "Virgin"),
#                        labelOrder = c("Virgin", "Not virgin"))
# 
# 
# ggplot(virgin[virgin$labels == "Virgin",], aes(x = year, y = est)) +
#   geom_line(linewidth = 1.5, color = "#EA008B", alpha = 0.7) +
#   geom_point(size = 2.25, color = "#EA008B") +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = yearrange, 
#                      labels = yearrange) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   labs(x = "", y = "Burning Man Participants (%)")
# 
# virginTable <- makeTableData(virgin)
# virginTable <- virginTable[1,] |>
#   matrix(nrow = 1) |>
#   as.table()
# rownames(virginTable) = "Virgin"
# colnames(virginTable) = yearrange
# kbl(virginTable, col.names = yearrange,
#       row.names = TRUE) |>
#   kable_paper("striped")  |>
#   kable_styling() |>
#   column_spec(column = 1:11, width_min = "10.5em") 

virgin <- makePlotData(varName = "Was this your first time visiting Black Rock City?",
                       varNameTable,
                       designs = list(design13, design14, design15,
                                      design16, design17, design18,
                                      design19, design22, design23,
                                      design24),
                       years = c(2013:2019, 2022:2024),
                       levels = list(c("no", "yes"), c("no", "yes"),
                                     c("no", "yes"), c("no", "yes"),
                                     c("no", "yes"), c("no", "yes"),
                                     c("no", "yes"), c(FALSE, TRUE),
                                     c(FALSE, TRUE), c(FALSE, TRUE)),
                       labels = c("Not virgin", "Virgin"),
                       labelOrder = c("Virgin", "Not virgin"))


ggplot(virgin[virgin$labels == "Virgin",], aes(x = year, y = est)) +
  geom_line(linewidth = 1.5, color = "#EA008B", alpha = 0.7) +
  geom_point(size = 2.25, color = "#EA008B") +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  labs(x = "", y = "Burning Man Participants (%)")

virginTable <- makeTableData(virgin)
virginTable <- virginTable[1,] |>
  matrix(nrow = 1) |>
  as.table()
rownames(virginTable) = "Virgin"
colnames(virginTable) = c(2013:2019, 2022:2024)
kbl(virginTable, col.names = c(2013:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:11, width_min = "10.5em") 

```

### Number of burns attended

```{r}
#| label: attendance-num-burns
ggplot(census24, 
       aes(x = numberBurns, y = after_stat(density), weight = weights)) +
  geom_histogram(fill = "#EA008B", color = "black", binwidth = 1) +
  theme_bw() +
  labs(x = "Number of burns attended (including 2024)", y = "Proportion") +
  coord_cartesian(xlim = c(0, 30))


empCDFs <- list(svycdf(~numberBurns, design24)[[1]],
                 svycdf(~nburns, design23)[[1]],
                 svycdf(~numberBurns, design22)[[1]],
                 svycdf(~nbburns, design19)[[1]],
                 svycdf(~nbburns, design18)[[1]],
                 svycdf(~nbburns, design17)[[1]],
                 svycdf(~nbburns, design16)[[1]],
                 svycdf(~nbburns, design15)[[1]],
                 svycdf(~nbburns, design14)[[1]])
names(empCDFs) <- c(2024:2022, 2019:2014)
## todo: use nbburns2-6 to add 2013 data

myQuantiles <- c(0, 1, 2, 4, 10, Inf) # account for time looping burners!
rangeNames <- c("1","2","3-4","5-10",">10")

## number burns >=2022 are inclusive, but <= 2019 are not inclusive
cumulProportions1 <- sapply(
  empCDFs[c("2024", "2023", "2022")], 
  mapply, 
  myQuantiles)
cumulProportions2 <- sapply(
  empCDFs[c("2019", "2018", "2017", "2016", "2015", "2014")], 
  mapply, 
  myQuantiles-1) # -1 to make these inclusive
cumulProportions <- cbind(cumulProportions1, cumulProportions2)

myProportions <- diff(cumulProportions)
rownames(myProportions) <- rangeNames
 
myDat <- data.frame(
  rows=factor(rownames(myProportions)[row(myProportions)],
              levels=rev(rangeNames)), 
  Year=factor(colnames(myProportions)[col(myProportions)],
              levels=2014:2024),
  Percentage=c(myProportions))

ggplot(myDat, aes(x = Year, y = Percentage, fill = rows)) + 
  geom_bar(position = "fill",stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_x_discrete(drop = FALSE) + 
  labs(fill="Number\n of burns\n attended\n (inclusive)",
       x = "") +
  scale_fill_manual(values = gradientColors(5)) +
  # scale_fill_manual(values=c("#EA008B", "#d460c7", "#bc8ce0", "#b0aedc",
  #                               "#c3c4c6")[1:5]) +
  theme_bw()
```

### Plans to Return to Black Rock City

```{r}
#| label: attendance-plans-return
returnBRC <- makePlotData(varName = "Do you plan to return to Black Rock City for Burning Man?",
                       varNameTable,
                       designs = list(design24),
                       years = c(2024),
                       levels = list(c("Maybe in the future if possible",
                                       "No, definitely not",
                                       "Not likely",
                                       "Yes, definitely in 2025",
                                       "Yes, not in 2025 but definitely in the next 5 years")),
                       labels = c("Maybe in the future if possible",
                                       "No, definitely no",
                                       "Not likely",
                                       "Yes, definitely in 2025",
                                       "Yes, not in 2025 but definitely in the next 5 years"),
                       labelOrder = rev(c(4, 5, 1, 3, 2)))

ggplot(returnBRC, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "Plan to return to BRC", y = "Burning Man participants in 2024 (%)",
       title = "Do you plan to return to Black Rock City?") +
  theme_bw() +
  coord_flip()

makeTableData(returnBRC) |>
  kbl(col.names = c(2024),
      row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:2, width_min = "11.5em") 
  
```

### Reason for Returning or not Returning to Black Rock City

```{r}
#| label: attendance-reasons-return
reasons <- data.frame(text = c(census24$planToReturn.writeIn.1,
                               census24$planToReturn.writeIn.2,
                               census24$planToReturn.writeIn.3))
reasonTokens <- tidytext::unnest_tokens(reasons, output = tkn, input = text, 
                                        token = "sentences")
reasonsTable <- table(reasonTokens$tkn)[order(table(reasonTokens$tkn), 
                                              decreasing = TRUE)]
reasonFreq <- data.frame(text = attr(reasonsTable, "dimnames")[[1]], 
                         freq = as.numeric(reasonsTable))
wordcloud2(reasonFreq[1:200,], color = discreteColors)
```

<!-- Other ideas?  Average number of burns attended without a break? -->

## Demographics

### Age

```{r}
#| label: demographics-age

ggplot(subset(census24[,c("age","weights")], !is.na(age)), aes(x = age, y = after_stat(density), weight = weights)) +
  geom_histogram(binwidth = 1, fill = "#EA008B", color = "black") +
  scale_x_continuous(breaks=seq(20,95,5)) +

  theme_bw() +
  labs(x = "Age at arrival on playa in 2024", y = "Density")



#### removed age quantiles over time in favor of binning the ages and reporting percentages
# props <- c(10, 25, 50, 75, 90)/100
# 
# 
# ageQuantiles <- data.frame(svyquantile(~age, design24, props)[[1]][,1],
# 
#                       svyquantile(~age, design23, props)[[1]][,1],
#                       svyquantile(~age, design22, props)[[1]][,1],
#                       rep("",length(props)),
#                       svyquantile(~age, design19, props)[[1]][,1],
#                       svyquantile(~age, design18, props)[[1]][,1],
#                       svyquantile(~age, design17, props)[[1]][,1],
#                       svyquantile(~age, design16, props)[[1]][,1],
#                       svyquantile(~age, design15, props)[[1]][,1],
#                       svyquantile(~age, design14, props)[[1]][,1]
#                       ) |>
# rev()
# row.names(ageQuantiles) <- paste0(props*100, "th percentile")
# 
# ageQuantiles |>
#   kbl(col.names = c(2014:2019,"", 2022:2024),
#       row.names = TRUE) |>
#   kable_paper("striped")  |>
#   kable_styling() |>
#   #column_spec(column = 1:9, width_min = "10.5em") |>
# 
#   column_spec(column = 1:11, width_min = "10.5em") 
# 

#### age groups over time


empCDFs <- list(svycdf(~age, design24)[[1]],
                 svycdf(~age, design23)[[1]],
                 svycdf(~age, design22)[[1]],
                 svycdf(~age, design19)[[1]],
                 svycdf(~age, design18)[[1]],
                 svycdf(~age, design17)[[1]],
                 svycdf(~age, design16)[[1]],
                 svycdf(~age, design15)[[1]],
                 svycdf(~age, design14)[[1]])
names(empCDFs) <- c(2024:2022, 2019:2014)

myQuantiles <- c(0, 19, 29, 39, 49, 59,69, Inf)
rangeNames <- c(" 0-19"," 20-29"," 30-39"," 40-49"," 50-59"," 59-69",">69")


## construct updated designs with binned ages 
yrs <- c(2014:2019, 2022:2024)
designs <- list(design14, design15, design16, design17, design18, design19, design22, design23, design24)

upDesigns <- lapply(designs, function(l){
  ageRngs <- cut(l$variables$age, myQuantiles)
  levels(ageRngs) <- rangeNames
  update(l, ageRange = ageRngs)
})



estPrcs <- sapply(upDesigns, function(l){
  svymean(~ageRange, l, na.rm = TRUE)*100
})

rownames(estPrcs) <- rangeNames
colnames(estPrcs) <- yrs


digts <- 1 # digits to round to 
## estimated percentages
estPrcsTable <- sapply(upDesigns, function(l){
  paste(
    c(formatC( round( svymean(~ageRange, l, na.rm = TRUE)*100,
                    digts ), format='f', digits=digts )), # keep trailing 0's
    "%",sep="")
})
## estimated left conf bounds
estLConfTable <- sapply(upDesigns, function(l){
  paste(
    c(formatC( 
      round( 
        pmax(cbind( # nonzero values
          confint(svymean(~ageRange, l, na.rm = TRUE))[,1]*100
          ),0),
                    digts ), 
      format='f', digits=digts )), # keep trailing 0's
    "%",sep="")
})
## estimated right conf bounds
estRConfTable <- sapply(upDesigns, function(l){
  paste(
    c(formatC( 
      round( 
          confint(svymean(~ageRange, l, na.rm = TRUE))[,2]*100,
                    digts ), 
      format='f', digits=digts )), # keep trailing 0's
    "%",sep="")
})


estPrcsTable[] <- paste(
  estPrcsTable, " (", estLConfTable, ", ", estRConfTable,")",
  sep=""
)

rownames(estPrcsTable) <- rangeNames
colnames(estPrcsTable) <- yrs

estPrcsTable <- cbind(
  estPrcsTable[,as.character(2014:2019)],
  "",
  estPrcsTable[,as.character(2022:2024)]
) # adding empty column for early covid years

estPrcs <- as.data.frame(estPrcs)
names(estPrcs) <- paste("Year",names(estPrcs),sep="_")
estPrcsLong <- reshape(estPrcs, 
                       direction = "long", 
                       varying = names(estPrcs),
                       ids = rownames(estPrcs),
                       sep = "_")

names(estPrcsLong) <- c("Year","Percentage","row" )
estPrcsLong$row[estPrcsLong$row == ">69"] <- "70+"
estPrcsLong$row[estPrcsLong$row == " 59-69"] <- "60-69"
estPrcsLong$row <- trimws(estPrcsLong$row)
estPrcsLong$row <- factor(estPrcsLong$row,
                          levels = rev(c("0-19", "20-29",
                                     "30-39", "40-49",
                                     "50-59", "60-69", 
                                     "70+")))


ggplot(estPrcsLong, aes(x = Year, y = Percentage, fill = row)) + 
  geom_bar(position = "fill",stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
    scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) + 
  labs(fill="Age (Earth years)",
       x = "What was your age when you arrived at Black Rock City this year?", y = "Burning Man participants (%)") +
  scale_fill_manual(values = gradientColors(9)[c(1,3:9)]) +
  # scale_fill_manual(values=c("#EA008B", "#d460c7", "#bc8ce0", "#b0aedc",
  #                               "#c3c4c6")[1:5]) +
  theme_bw()

rownames(estPrcsTable)[6] <- "60-69"
rownames(estPrcsTable)[7] <- "70+"
estPrcsTable[,-7] |> 
  kbl(col.names = c(2014:2019,2022:2024),
      row.names = TRUE,digits=4) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:10, width_min = "11.5em") 


```

### Current gender

```{r}
#| label: demographics-gender-current
#### 2022
gender22.male <- svyciprop(~grepl("(?<!([Ff]e))[Mm]ale", currentGender, perl = TRUE),
                           design22)
gender22.male <- data.table(est = as.numeric(gender22.male),
                            lower = attr(gender22.male, "ci")[1],
                            upper = attr(gender22.male, "ci")[2],
                            level = "male",
                            year = 2022,
                            labels = factor("Male",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender22.female <- svyciprop(~grepl("[Ff]emale", currentGender, perl = TRUE),
                           design22)
gender22.female <- data.table(est = as.numeric(gender22.female),
                            lower = attr(gender22.female, "ci")[1],
                            upper = attr(gender22.female, "ci")[2],
                            level = "female",
                            year = 2022,
                            labels = factor("Female",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender22.other <- svyciprop(~I(!grepl("[Mm]ale", currentGender, perl = TRUE)),
                           design22)
gender22.other <- data.table(est = as.numeric(gender22.other),
                            lower = attr(gender22.other, "ci")[1],
                            upper = attr(gender22.other, "ci")[2],
                            level = "male",
                            year = 2022,
                            labels = factor("Other identity",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender22 <- rbind(gender22.male, gender22.female, gender22.other)



#### 2023
gender23.male <- svyciprop(~grepl("(?<!([Ff]e))[Mm]ale", currentGender, perl = TRUE),
                           design23)
gender23.male <- data.table(est = as.numeric(gender23.male),
                            lower = attr(gender23.male, "ci")[1],
                            upper = attr(gender23.male, "ci")[2],
                            level = "male",
                            year = 2023,
                            labels = factor("Male",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender23.female <- svyciprop(~grepl("[Ff]emale", currentGender, perl = TRUE),
                           design23)
gender23.female <- data.table(est = as.numeric(gender23.female),
                            lower = attr(gender23.female, "ci")[1],
                            upper = attr(gender23.female, "ci")[2],
                            level = "female",
                            year = 2023,
                            labels = factor("Female",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender23.other <- svyciprop(~I(!grepl("[Mm]ale", currentGender, perl = TRUE)),
                           design23)
gender23.other <- data.table(est = as.numeric(gender23.other),
                            lower = attr(gender23.other, "ci")[1],
                            upper = attr(gender23.other, "ci")[2],
                            level = "male",
                            year = 2023,
                            labels = factor("Other identity",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender23 <- rbind(gender23.male, gender23.female, gender23.other)


#### 2024

gender24.male <- svyciprop(~grepl("(?<!([Ff]e))[Mm]ale", currentGender, perl = TRUE),
                           design24)
gender24.male <- data.table(est = as.numeric(gender24.male),
                            lower = attr(gender24.male, "ci")[1],
                            upper = attr(gender24.male, "ci")[2],
                            level = "male",
                            year = 2024,
                            labels = factor("Male",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender24.female <- svyciprop(~grepl("[Ff]emale", currentGender, perl = TRUE),
                           design24)
gender24.female <- data.table(est = as.numeric(gender24.female),
                            lower = attr(gender24.female, "ci")[1],
                            upper = attr(gender24.female, "ci")[2],
                            level = "female",
                            year = 2024,
                            labels = factor("Female",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender24.other <- svyciprop(~I(!grepl("[Mm]ale", currentGender, perl = TRUE)),
                           design24)
gender24.other <- data.table(est = as.numeric(gender24.other),
                            lower = attr(gender24.other, "ci")[1],
                            upper = attr(gender24.other, "ci")[2],
                            level = "male",
                            year = 2024,
                            labels = factor("Other identity",
                                            levels = c("Male", "Female",
                                                       "Other identity")))
gender24 <- rbind(gender24.male, gender24.female, gender24.other)

gender <- makePlotData(varName = "What is your current gender?", varNameTable,
                          designs = list(design13, design14, design15,
                                         design16, design17, design18,
                                         design19),
                          years = c(2013:2019),
                          levels = rep(list(c("female", "fluid", "male")), times = 7),
                          labels = c("Female", "Other identity", "Male"),
                          labelOrder = c("Male", "Female", "Other identity"))
gender <- gender[!is.na(gender$est),]
gender <- rbind(gender, gender22, gender23, gender24)

ggplot(gender, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  # geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2,
  #               linewidth = 1) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024), labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = c("#EA008B", "#554149", "#BDA5AD")) +
  labs(x = "", y = "Burning Man participants (%)",
       color = "Current gender")

makeTableData(gender) |>
  kbl(col.names = c(2013:2019, 2022:2024),
      row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>

  column_spec(column = 1:11, width_min = "11.5em")

```

<!-- ### Gender identity -->

<!-- ```{r} -->

<!-- genderID <- makePlotData(varName = "Do you consider yourself to be any of the following?",  -->

<!--                          varNameTable, -->

<!--                          designs = list(design24), -->

<!--                          years = c(2024), -->

<!--                          levels = TRUE, -->

<!--                          labels = c("Transperson  (e.g., transgender, transsexual)", -->

<!--                                     "Gender queer", -->

<!--                                     "Gender non-conforming", -->

<!--                                     "Gender questioning", -->

<!--                                     "Two-spirit", -->

<!--                                     "My gender does not match my sex assigned at birth"), -->

<!--                           labelOrder = c(1:6)) -->

<!-- ggplot(genderID, aes(x = labels, y = est)) + -->

<!--   geom_bar(stat = "identity", fill = "#EA008B") + -->

<!--   scale_y_continuous(labels = percent) + -->

<!--   labs(x = "Gender identity", y = "Burning Man participants (%)") + -->

<!--   theme_bw() + -->

<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) -->

<!-- makeTableData(genderID) |> -->

<!--   kbl(col.names = c(2022:2024), -->

<!--       row.names = TRUE) |> -->

<!--   kable_paper("striped")  |> -->

<!--   kable_styling() |> -->

<!--   column_spec(column = 1:1, width_min = "10.5em") |> -->

<!-- ``` -->

<!-- ### Sex assigned at birth -->

```{r}
#| label: demographics-birth-gender
# sexAtBirth <- makePlotData(varName = "What sex was assigned to you at birth?",
#                            varNameTable,
#                            designs = list(design23),
#                            years = c(2023),
#                            levels = list(c("Female", "Intersex", "Male")),
#                            labels = c("Female", "Intersex", "Male"),
#                            labelOrder = rev(c("Male", "Female", "Intersex")))
# 
# ggplot(sexAtBirth, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Sex at birth", y = "Burning Man participants (%)") +
#   theme_bw()
#   # theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# makeTableData(sexAtBirth)[3:1,] |>
#   kbl(col.names = c(2023),
#       row.names = TRUE) |>
#   kable_paper("striped")  |>
#   kable_styling() |>
#   column_spec(column = 1:1, width_min = "10.5em") 
```

### Ethnoracial background

```{r}
#| label: demographics-ethnoracial-background

ethnoracial24 <- makePlotData("Which category best describes your race?",
                              varNameTable = varNameTable,
                              designs = list(design24),
                              years = 2024,
                              levels = rep(list(TRUE), times = 1),
                              labels = c("Asian", "Native American",
                                         "Native Hawaiian or Pacific Islander",
                                         "Hispanic/Latino",
                                         "White (non-Hispanic)",
                                         "Middle Eastern or North African",
                                         "Black (non-Hispanic)", "Other"),
                              labelOrder = c("White (non-Hispanic)",
                                             "Hispanic/Latino",
                                             "Asian",
                                             "Middle Eastern or North African",
                                             "Black (non-Hispanic)",
                                             "Native American", 
                                             "Native Hawaiian or Pacific Islander",
                                             "Other"))
ethnoracial22to23 <- makePlotData("Which category best describes your race?",
                              varNameTable = varNameTable,
                              designs = list(design22, design23),
                              years = 2022:2023,
                              levels = rep(list(TRUE), times = 2),
                              labels = c("Asian", "Native American",
                                         "Native Hawaiian or Pacific Islander",
                                         "Hispanic/Latino",
                                         "White (non-Hispanic)",
                                         "Middle Eastern or North African",
                                         "Black (non-Hispanic)", "Other"),
                              labelOrder = c("White (non-Hispanic)",
                                             "Hispanic/Latino",
                                             "Asian",
                                             "Middle Eastern or North African",
                                             "Black (non-Hispanic)",
                                             "Native American","Native Hawaiian or Pacific Islander", "Other"))
ethnoracial22to23 <- ethnoracial22to23[!ethnoracial22to23$labels == "",] # remove spaces due to addition of Pacific Islander in 2024

ethnoracial17to19 <- makePlotData("ethnoracial 2013 through 2019",
                              varNameTable = varNameTable,
                              designs = list(design17, design18, design19),
                              years = 2017:2019,
                              levels = rep(list(c("asian", "black", "hispanic",
                                                  "middleeastern", "native",
                                                  "other_or_mix", "white")),
                                           times = 3),
                              labels = c("Asian", "Black (non-Hispanic)",
                                         "Hispanic/Latino",
                                         "Middle Eastern or North African",
                                         "Native American",
                                         "Other", "White (non-Hispanic)"),
                              labelOrder = c("White (non-Hispanic)",
                                             "Hispanic/Latino",
                                             "Asian",
                                             "Middle Eastern or North African",
                                             "Black (non-Hispanic)",
                                             "Native American", "Other"))

ethnoracial13to16 <- makePlotData("ethnoracial 2013 through 2019",
                              varNameTable = varNameTable,
                              designs = list(design13, design14, design15,
                                             design16),
                              years = 2013:2016,
                              levels = rep(list(c("asian", "black", "hispanic",
                                                  "native", "other_or_mix",
                                                  "white")), times = 4),
                              labels = c("Asian", "Black (non-Hispanic)",
                                         "Hispanic/Latino",
                                         "Native American",
                                         "Other", "White (non-Hispanic)"),
                              labelOrder = c("White (non-Hispanic)",
                                             "Hispanic/Latino",
                                             "Asian",
                                             "Black (non-Hispanic)",
                                             "Native American", "Other"))



ethnoracial13to16 <- rbind(ethnoracial13to16,
                           data.frame(est = NA, lower = NA, upper = NA,
                                      level = "middleeastern",
                                      year = 2013:2016,
                                      labels = factor("Middle Eastern or North African",
                                                      levels = c("White (non-Hispanic)",
                                                                 "Hispanic/Latino",
                                                                 "Asian",
                                                                 "Middle Eastern or North African",
                                                                 "Black (non-Hispanic)",
                                                                 "Native American", "Other"))))


ggplot(ethnoracial24, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", position = "dodge", fill = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "Ethnoracial background", y = "Burning Man participants in 2024 (%)",
       title = "Which category best describes your race?") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))


## adding pacific islander for 2024
pacislander13to19 <- data.frame(est=NA, lower=NA, upper=NA, level=NA, 
                                year=2013:2019, 
                                labels="Native Hawaiian or Pacific Islander")

tableDat <- makeTableData(rbind(ethnoracial24,ethnoracial22to23,ethnoracial17to19, ethnoracial13to16, pacislander13to19))

tdrn <- rownames(tableDat)
tdrn[4] <- paste0("Middle Eastern or North African",footnote_marker_alphabet(1))
tdrn[7] <- paste0("Native Hawaiian or Pacific Islander",footnote_marker_alphabet(2))
tdrn[8] <- paste0("Other",footnote_marker_alphabet(3))
rownames(tableDat) <- tdrn

tdcn <- colnames(tableDat)

tdcn[colnames(tableDat)=="2022"] <- paste0("2022",footnote_marker_alphabet(4))

colnames(tableDat) <- tdcn

tableDat |>
  kbl(col.names = tdcn,
      row.names = TRUE, escape = FALSE) |>
  kable_paper("striped") |>
  kable_styling(full_width = TRUE) |>
  column_spec(column = 1:11, width_min = "11.5em") |>
  footnote(alphabet = c("Middle eastern was not an option from 2013-2016.",
                        "Pacific Islander was not an option from 2013-2022.",
                        "The \"other or mixed\" option in 2013-2019 changed to \"other\" in 2022.",
                        "In 2022 the format changed to allow users to select multiple options. While this improves our data collection, it unfortunately makes it impossible to make direct comparisons to previous years."))
```

### Self-identification as a person of color

```{r}
#| label: ethnoracial-person-of-color
personOfColor <- makePlotData("Do you consider yourself to be a person of color?",
                              varNameTable = varNameTable,
                              designs = list(design13, design14, design15,
                                             design16, design17, design18,
                                             design19, design22, design23,
                                             design24),
                              years = c(2013:2019, 2022:2024),
                              levels = c("No", "Sometimes", "Yes"),
                              labels = c("No", "Sometimes", "Yes"),
                              labelOrder = 1:3)

ggplot(personOfColor, aes(x = year, y = est, fill = labels)) +
  geom_area(alpha = 0.65) +
  scale_y_continuous(labels = percent) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_fill_manual(values = gradientColors(3)[3:1]) +
  labs(x = "", y = "Burning Man participants (%)",
       fill = "Person of color",
       title = "Do you consider yourself a person of color?") +
  theme_bw()

makeTableData(personOfColor) |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:11, width_min = "11.5em") |>
  kable_styling() 
```

### First language learned

```{r}
#| label: demographics-first-language
language15 <- makePlotData("What was the first language you learned and still use (i.e., native language)?",
                         varNameTable = varNameTable,
                         designs = list(design15),
                         years = c(2015),
                         levels = rep(list(c("Arabic", "Chinese", "Danish",
                                             "Dutch", "English", "Farsi",
                                             "French", "German","Hebrew",
                                             "Hindi", "Italian", "Japanese",
                                             "Norwegian", "Other", "Polish",
                                             "Portuguese",
                                             "Romanian", "Russian", "Spanish",
                                             "Swedish", "Tagalog", "Urdu")),
                                      times = 1),
                         labels = NULL,
                         labelOrder = c("English","Spanish","French",
                                        "German","Russian","Chinese",
                                        "Portuguese","Dutch","Hebrew",
                                        "Italian","Swedish","Farsi",
                                        "Arabic","Polish","Hindi",
                                        "Danish","Romanian","Tagalog",
                                        "Japanese",
                                        "Urdu","Other"))

## 2015 is missing Punjabi for some reason, seems to cause numerical instability?
language15 <- language15[!is.na(language15$est),]

language15$labels <- language15$level

language15 <- rbind(language15, c(0, 0, 0, "Punjabi", 2015, "Punjabi"))

language13to23less15 <- makePlotData("What was the first language you learned and still use (i.e., native language)?",
                         varNameTable = varNameTable,
                         designs = list(design13, design14,
                                        design16, design17, design18,
                                        design19, design22, design23),
                         years = c(2013:2014,2016:2019, 2022:2023),
                         levels = rep(list(c("Arabic", "Chinese", "Danish",
                                             "Dutch", "English", "Farsi",
                                             "French", "German","Hebrew",
                                             "Hindi", "Italian", "Japanese",
                                             "Norwegian", "Other", "Polish",
                                             "Portuguese", "Punjabi",
                                             "Romanian", "Russian", "Spanish",
                                             "Swedish", "Tagalog", "Urdu")),
                                      times = 8),
                         labels = NULL,
                         labelOrder = c("English","Spanish","French",
                                        "German","Russian","Chinese",
                                        "Portuguese","Dutch","Hebrew",
                                        "Italian","Swedish","Farsi",
                                        "Arabic","Polish","Hindi",
                                        "Danish","Romanian","Tagalog",
                                        "Punjabi","Japanese","Norwegian",
                                        "Urdu","Other"))


language24 <- makePlotData("What was the first language you learned and still use (i.e., native language)?",
                         varNameTable = varNameTable,
                         designs = list(design24),
                         years = c(2024),
                         levels = rep(list(c("Arabic", "Chinese", "Danish",
                                             "Dutch", "English", "Farsi",
                                             "French", "German","Hebrew",
                                             "Hindi", "Italian", "Japanese",
                                              "Other", "Polish",
                                             "Portuguese", "Punjabi",
                                             "Romanian", "Russian", "Spanish",
                                             "Swedish", "Tagalog", "Urdu")),
                                      times = 1),
                         labels = NULL,
                         labelOrder = c("English","Spanish","French",
                                        "German","Russian","Chinese",
                                        "Portuguese","Dutch","Hebrew",
                                        "Italian","Swedish","Farsi",
                                        "Arabic","Polish","Hindi",
                                        "Danish","Romanian","Tagalog",
                                        "Punjabi","Japanese",
                                        "Urdu","Other"))

language24$labels <- language24$level
language24 <- rbind(language24, c(0, 0, 0, "Norwegian", 2024, "Norwegian"))


language <- rbind(language15,language13to23less15, language24)


english <- language[language$level=="English",]
notEnglish <- english
notEnglish[,c(1,3,2)] <- sapply(english[,1:3],function(x){1-as.numeric(x)})
notEnglish$level <- "notEnglish"
notEnglish$labels <- "Other Language"

language2 <- rbind(notEnglish,english)

language2[,c(1:3,5)] <- sapply(language2[,c(1:3,5)], as.numeric)
language2$labels <- factor(language2$labels, 
                           levels = c("Other Language","English")) #reorder factor

ggplot(language2, aes(x = year, y = est, fill = labels)) +
  geom_area(alpha = 0.65) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_y_continuous(labels = percent) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_fill_manual(values = gradientColors(2)[2:1]) +
  labs(x = "", y = "Burning Man participants (%)", fill = "Language",
       title = "What was the first language you learned and still use?")

tableData <- makeTableData(language)
tableOrder <- order(tableData[,"2024"], decreasing = TRUE)
tableData <- tableData[tableOrder,]

tableData |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:11, width_min = "11.5em") |>
  kable_styling() 
```

### Personal income in 2024

```{r}
#| label: demographics-income-personal
#TODO Make barplot and table for just 2024 data

piGraphGroups <- list("Less than $25,000" = c("None", 
                                              "Less_than_7500US",
                                              "_7500_14999US", 
                                              "_15000_24999US",
                                              "I had no personal income",
                                              "Less than $7,500 USD",
                                              "$7,500-$14,999 USD",
                                              "$15,000-$24,999 USD",
                                              "No income", 
                                              "Less than $7500",
                                              "$7,500-$14,999", 
                                              "$15,000-$24,999"),
                        "$25,000-$49,999" = c("_25000_34999US",
                                              "_35000_49999US",
                                              "$25,000-$34,999", 
                                              "$35,000-$49,999",
                                              "$25,000-$34,999 USD",
                                              "$35,000-$49,999 USD"),
                        "$50,000-$99,999" = c("_50000_74999US", 
                                              "_75000_99999US",
                                              "$50,000-$74,999", 
                                              "$75,000-$99,999",
                                              "$50,000-$74,999 USD",
                                              "$75,000-$99,999 USD"),
                        "$100,000-$299,999" = c("_100k_149999US", 
                                                "_150k_299999US",
                                                "$100,000-$149,999", 
                                                "$150,000-$299,000",
                                                "$100,000-$149,999 USD",
                                                "$150,000-$299,999 USD"),
                        "$300,000 or more" = c("_300kUS_or_more",
                                               "$300,000 or more",
                                               "$300,000-$399,999 USD",
                                               "$400,000-$499,999 USD",
                                               "$500,000-$749,999 USD",
                                               "$750,000-$999,999 USD",
                                               "$1,000,000-$4,999,999 USD",
                                               "$5,000,000-$9,999,999 USD",
                                               "$10,000,000 USD or more"))

pi.allYears <- makePlotData(varName = "What was your personal income in 2023 before taxes? Give your best estimate. Please do not include your spouse's income as your own.",
                         varNameTable,
                         designs = list(design15, design16, design17, design18,
                                        design19, design22, design23, design24),
                         years = c(2015:2019, 2022:2024),
                         levels = c(rep(list(c("_100k_149999US",
                                               "_15000_24999US",
                                               "_150k_299999US",
                                               "_25000_34999US",
                                               "_300kUS_or_more",
                                               "_35000_49999US",
                                               "_50000_74999US",
                                               "_7500_14999US",
                                               "_75000_99999US",
                                               "Less_than_7500US",
                                               "None")), times  = 5),
                                    rep(list(c("$100,000-$149,999", 
                                               "$15,000-$24,999",
                                               "$150,000-$299,000", 
                                               "$25,000-$34,999",
                                               "$300,000 or more", 
                                               "$35,000-$49,999",
                                               "$50,000-$74,999", 
                                               "$7,500-$14,999",
                                               "$75,000-$99,999", 
                                               "Less than $7500",
                                               "No income")), times = 2),
                                    list(c("$1,000,000-$4,999,999 USD", 
                                         "$10,000,000 USD or more",
                                         "$100,000-$149,999 USD", 
                                         "$15,000-$24,999 USD",
                                         "$150,000-$299,999 USD", 
                                         "$25,000-$34,999 USD",
                                         "$300,000-$399,999 USD",
                                         "$35,000-$49,999 USD",
                                         "$400,000-$499,999 USD",
                                         "$5,000,000-$9,999,999 USD",
                                         "$50,000-$74,999 USD",
                                         "$500,000-$749,999 USD",
                                         "$7,500-$14,999 USD",
                                         "$75,000-$99,999 USD",
                                         "$750,000-$999,999 USD",
                                         "I had no personal income",
                                         "Less than $7,500 USD"))),
                         labels = c("Less than $25,000", "$25,000-$49,999",
                                    "$50,000-$99,999", "$100,000-$299,999",
                                    "$300,000 or more"),
                         labelOrder = c("Less than $25,000", "$25,000-$49,999",
                                        "$50,000-$99,999", "$100,000-$299,999",
                                        "$300,000 or more"),
                         groups = piGraphGroups) 



ggplot(pi.allYears, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024), labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = gradientColors(5)) +
  labs(x = "", y = "Burning Man participants (%)", color = "Personal income (USD)",
       title = "Personal income of Burning Man participants in 2024")




personalIncome <- makePlotData(varName = "What was your personal income in 2023 before taxes? Give your best estimate. Please do not include your spouse's income as your own.",
                         varNameTable,
                         designs = list(design15, design16, design17, design18,
                                        design19, design22, design23),
                         years = c(2015:2019, 2022:2023),
                         levels = c(rep(list(c("_100k_149999US",
                                               "_15000_24999US",
                                               "_150k_299999US",
                                               "_25000_34999US",
                                               "_300kUS_or_more",
                                               "_35000_49999US",
                                               "_50000_74999US",
                                               "_7500_14999US",
                                               "_75000_99999US",
                                               "Less_than_7500US",
                                               "None")), times  = 5),
                                    rep(list(c("$100,000-$149,999", 
                                               "$15,000-$24,999",
                                               "$150,000-$299,000", 
                                               "$25,000-$34,999",
                                               "$300,000 or more", 
                                               "$35,000-$49,999",
                                               "$50,000-$74,999", 
                                               "$7,500-$14,999",
                                               "$75,000-$99,999", 
                                               "Less than $7500",
                                               "No income")), times = 2)),
                         labels = c("$100,000-$149,999", "$15,000-$24,999",
                                    "$150,000-$299,000", "$25,000-$34,999",
                                    "$300,000 or more", "$35,000-$49,999",
                                    "$50,000-$74,999", "$7,500-$14,999",
                                    "$75,000-$99,999", "Less than $7,500",
                                    "No income"),
                         labelOrder = c("No income", "Less than $7,500",
                                        "$7,500-$14,999", "$15,000-$24,999",
                                        "$25,000-$34,999", "$35,000-$49,999",
                                        "$50,000-$74,999", "$75,000-$99,999",
                                        "$100,000-$149,999", "$150,000-$299,000",
                                        "$300,000 or more")) 
  
piGroups24 = list("No income" = c("I had no personal income"),
                  "Less than $7,500" = c("Less than $7,500 USD"),
                  "$7,500-$14,999" = c("$7,500-$14,999 USD"), 
                  "$15,000-$24,999" = c("$15,000-$24,999 USD"),
                  "$25,000-$34,999" = c("$25,000-$34,999 USD"), 
                  "$35,000-$49,999" = c("$35,000-$49,999 USD"),
                  "$50,000-$74,999" = c("$50,000-$74,999 USD"), 
                  "$75,000-$99,999" = c("$75,000-$99,999 USD"),
                  "$100,000-$149,999" = c("$100,000-$149,999 USD"), 
                  "$150,000-$299,000" = c("$150,000-$299,999 USD"),
                  "$300,000 or more" = c("$300,000-$399,999 USD",
                                         "$400,000-$499,999 USD",
                                         "$500,000-$749,999 USD",
                                         "$750,000-$999,999 USD",
                                         "$1,000,000-$4,999,999 USD",
                                         "$5,000,000-$9,999,999 USD",
                                         "$10,000,000 USD or more"))

personalIncome24 <- makePlotData(varName = "What was your personal income in 2023 before taxes? Give your best estimate. Please do not include your spouse's income as your own.",
                         varNameTable,
                         designs = list(design24),
                         years = c(2024),
                         levels = list(c("$1,000,000-$4,999,999 USD", 
                                         "$10,000,000 USD or more",
                                         "$100,000-$149,999 USD", 
                                         "$15,000-$24,999 USD",
                                         "$150,000-$299,999 USD", 
                                         "$25,000-$34,999 USD",
                                         "$300,000-$399,999 USD",
                                         "$35,000-$49,999 USD",
                                         "$400,000-$499,999 USD",
                                         "$5,000,000-$9,999,999 USD",
                                         "$50,000-$74,999 USD",
                                         "$500,000-$749,999 USD",
                                         "$7,500-$14,999 USD",
                                         "$75,000-$99,999 USD",
                                         "$750,000-$999,999 USD",
                                         "I had no personal income",
                                         "Less than $7,500 USD")),
                         labels = c("$100,000-$149,999", "$15,000-$24,999",
                                    "$150,000-$299,000", "$25,000-$34,999",
                                    "$300,000 or more", "$35,000-$49,999",
                                    "$50,000-$74,999", "$7,500-$14,999",
                                    "$75,000-$99,999", "Less than $7,500",
                                    "No income"),
                         labelOrder = c("No income", "Less than $7,500",
                                        "$7,500-$14,999", "$15,000-$24,999",
                                        "$25,000-$34,999", "$35,000-$49,999",
                                        "$50,000-$74,999", "$75,000-$99,999",
                                        "$100,000-$149,999", "$150,000-$299,000",
                                        "$300,000 or more"),
                         groups = piGroups24) 

makeTableData(rbind(personalIncome, personalIncome24)) |>
  kbl(col.names = c(2015:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:9, width_min = "10.5em") 
```

### Household income in 2024

```{r}
#| label: demographics-income-household
#TODO Make barplot and table for just 2024 data

hiGraphGroups <- list("Less than $25,000" = c("None", 
                                              "Less_than_7500US",
                                              "_7500_14999US", 
                                              "_15000_24999US",
                                              "I had no household income",
                                              "Less than $7,500 USD",
                                              "$7,500-$14,999 USD",
                                              "$15,000-$24,999 USD",
                                              "No income", 
                                              "Less than $7500",
                                              "$7,500-$14,999", 
                                              "$15,000-$24,999"),
                        "$25,000-$49,999" = c("_25000_34999US",
                                              "_35000_49999US",
                                              "$25,000-$34,999", 
                                              "$35,000-$49,999",
                                              "$25,000-$34,999 USD",
                                              "$35,000-$49,999 USD"),
                        "$50,000-$99,999" = c("_50000_74999US", 
                                              "_75000_99999US",
                                              "$50,000-$74,999", 
                                              "$75,000-$99,999",
                                              "$50,000-$74,999 USD",
                                              "$75,000-$99,999 USD"),
                        "$100,000-$299,999" = c("_100k_149999US", 
                                                "_150k_299999US",
                                                "$100,000-$149,999", 
                                                "$150,000-$299,000",
                                                "$100,000-$149,999 USD",
                                                "$150,000-$299,999 USD"),
                        "$300,000 or more" = c("_300kUS_or_more",
                                               "$300,000 or more",
                                               "$300,000-$399,999 USD",
                                               "$400,000-$499,999 USD",
                                               "$500,000-$749,999 USD",
                                               "$750,000-$999,999 USD",
                                               "$1,000,000-$4,999,999 USD",
                                               "$5,000,000-$9,999,999 USD",
                                               "$10,000,000 USD or more"))

hi.allYears <- makePlotData(varName = "What was the total income before taxes of all members of your household (including you) in 2023?",
                         varNameTable,
                         designs = list(design15, design16, design17, design18,
                                        design19, design22, design23, design24),
                         years = c(2015:2019, 2022:2024),
                         levels = c(rep(list(c("_100k_149999US",
                                               "_15000_24999US",
                                               "_150k_299999US",
                                               "_25000_34999US",
                                               "_300kUS_or_more",
                                               "_35000_49999US",
                                               "_50000_74999US",
                                               "_7500_14999US",
                                               "_75000_99999US",
                                               "Less_than_7500US",
                                               "None")), times  = 5),
                                    rep(list(c("$100,000-$149,999", 
                                               "$15,000-$24,999",
                                               "$150,000-$299,000", 
                                               "$25,000-$34,999",
                                               "$300,000 or more", 
                                               "$35,000-$49,999",
                                               "$50,000-$74,999", 
                                               "$7,500-$14,999",
                                               "$75,000-$99,999", 
                                               "Less than $7500",
                                               "No income")), times = 2),
                                    list(c("$1,000,000-$4,999,999 USD", 
                                         "$10,000,000 USD or more",
                                         "$100,000-$149,999 USD", 
                                         "$15,000-$24,999 USD",
                                         "$150,000-$299,999 USD", 
                                         "$25,000-$34,999 USD",
                                         "$300,000-$399,999 USD",
                                         "$35,000-$49,999 USD",
                                         "$400,000-$499,999 USD",
                                         "$5,000,000-$9,999,999 USD",
                                         "$50,000-$74,999 USD",
                                         "$500,000-$749,999 USD",
                                         "$7,500-$14,999 USD",
                                         "$75,000-$99,999 USD",
                                         "$750,000-$999,999 USD",
                                         "I had no household income",
                                         "Less than $7,500 USD"))),
                         labels = c("Less than $25,000", "$25,000-$49,999",
                                    "$50,000-$99,999", "$100,000-$299,999",
                                    "$300,000 or more"),
                         labelOrder = c("Less than $25,000", "$25,000-$49,999",
                                        "$50,000-$99,999", "$100,000-$299,999",
                                        "$300,000 or more"),
                         groups = hiGraphGroups) 



ggplot(hi.allYears, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024), labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = gradientColors(5)) +
  labs(x = "", y = "Burning Man participants (%)", color = "Personal income (USD)",
       title = "Household income (for 2023) of Burning Man participants in 2024")




householdIncome <- makePlotData(varName = "What was the total income before taxes of all members of your household (including you) in 2023?",
                         varNameTable,
                         designs = list(design15, design16, design17, design18,
                                        design19, design22, design23),
                         years = c(2015:2019, 2022:2023),
                         levels = c(rep(list(c("_100k_149999US",
                                               "_15000_24999US",
                                               "_150k_299999US",
                                               "_25000_34999US",
                                               "_300kUS_or_more",
                                               "_35000_49999US",
                                               "_50000_74999US",
                                               "_7500_14999US",
                                               "_75000_99999US",
                                               "Less_than_7500US",
                                               "None")), times  = 5),
                                    rep(list(c("$100,000-$149,999", 
                                               "$15,000-$24,999",
                                               "$150,000-$299,000", 
                                               "$25,000-$34,999",
                                               "$300,000 or more", 
                                               "$35,000-$49,999",
                                               "$50,000-$74,999", 
                                               "$7,500-$14,999",
                                               "$75,000-$99,999", 
                                               "Less than $7500",
                                               "No income")), times = 2)),
                         labels = c("$100,000-$149,999", "$15,000-$24,999",
                                    "$150,000-$299,000", "$25,000-$34,999",
                                    "$300,000 or more", "$35,000-$49,999",
                                    "$50,000-$74,999", "$7,500-$14,999",
                                    "$75,000-$99,999", "Less than $7,500",
                                    "No income"),
                         labelOrder = c("No income", "Less than $7,500",
                                        "$7,500-$14,999", "$15,000-$24,999",
                                        "$25,000-$34,999", "$35,000-$49,999",
                                        "$50,000-$74,999", "$75,000-$99,999",
                                        "$100,000-$149,999", "$150,000-$299,000",
                                        "$300,000 or more")) 
  
hiGroups24 = list("No income" = c("I had no household income"),
                  "Less than $7,500" = c("Less than $7,500 USD"),
                  "$7,500-$14,999" = c("$7,500-$14,999 USD"), 
                  "$15,000-$24,999" = c("$15,000-$24,999 USD"),
                  "$25,000-$34,999" = c("$25,000-$34,999 USD"), 
                  "$35,000-$49,999" = c("$35,000-$49,999 USD"),
                  "$50,000-$74,999" = c("$50,000-$74,999 USD"), 
                  "$75,000-$99,999" = c("$75,000-$99,999 USD"),
                  "$100,000-$149,999" = c("$100,000-$149,999 USD"), 
                  "$150,000-$299,000" = c("$150,000-$299,999 USD"),
                  "$300,000 or more" = c("$300,000-$399,999 USD",
                                         "$400,000-$499,999 USD",
                                         "$500,000-$749,999 USD",
                                         "$750,000-$999,999 USD",
                                         "$1,000,000-$4,999,999 USD",
                                         "$5,000,000-$9,999,999 USD",
                                         "$10,000,000 USD or more"))

householdIncome24 <- makePlotData(varName = "What was the total income before taxes of all members of your household (including you) in 2023?",
                         varNameTable,
                         designs = list(design24),
                         years = c(2024),
                         levels = list(c("$1,000,000-$4,999,999 USD", 
                                         "$10,000,000 USD or more",
                                         "$100,000-$149,999 USD", 
                                         "$15,000-$24,999 USD",
                                         "$150,000-$299,999 USD", 
                                         "$25,000-$34,999 USD",
                                         "$300,000-$399,999 USD",
                                         "$35,000-$49,999 USD",
                                         "$400,000-$499,999 USD",
                                         "$5,000,000-$9,999,999 USD",
                                         "$50,000-$74,999 USD",
                                         "$500,000-$749,999 USD",
                                         "$7,500-$14,999 USD",
                                         "$75,000-$99,999 USD",
                                         "$750,000-$999,999 USD",
                                         "I had no household income",
                                         "Less than $7,500 USD")),
                         labels = c("$100,000-$149,999", "$15,000-$24,999",
                                    "$150,000-$299,000", "$25,000-$34,999",
                                    "$300,000 or more", "$35,000-$49,999",
                                    "$50,000-$74,999", "$7,500-$14,999",
                                    "$75,000-$99,999", "Less than $7,500",
                                    "No income"),
                         labelOrder = c("No income", "Less than $7,500",
                                        "$7,500-$14,999", "$15,000-$24,999",
                                        "$25,000-$34,999", "$35,000-$49,999",
                                        "$50,000-$74,999", "$75,000-$99,999",
                                        "$100,000-$149,999", "$150,000-$299,000",
                                        "$300,000 or more"),
                         groups = hiGroups24) 

makeTableData(rbind(householdIncome, householdIncome24)) |>
  kbl(col.names = c(2015:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:9, width_min = "10.5em") 
```

### Highest level of education completed

<!-- need to create 2022 variable for highest level completed to compare to prior years -->

```{r}
#| label: demographics-education
education <- makePlotData(varName = "What is the highest level of education have you completed?",
                          varNameTable,
                          designs = list(design24),
                          years = c(2024),
                          levels = c("Associate's degree or equivalent", 
                                     "Bachelor's degree or equivalent", 
                                     "Elementary school or equivalent", 
                                     "Graduate degree (Master's, Doctorate, or equivalent) or equivalent", 
                                     "High school diploma or equivalent", 
                                     "None of the above", 
                                     "Other", 
                                     "Technical/vocational certification or equivalent"),
                          labels = c("Associate's degree\n or equivalent", 
                                     "Bachelor's degree\n or equivalent", 
                                     "Elementary school\n or equivalent", 
                                     "Graduate degree (Master's,\n Doctorate, or equivalent)", 
                                     "High school diploma\n or equivalent", 
                                     "None of the above", 
                                     "Other", 
                                     "Technical/vocational certification\n or equivalent"),
                          labelOrder = c("Graduate degree (Master's,\n Doctorate, or equivalent)",
                                         "Technical/vocational certification\n or equivalent",
                                         "Bachelor's degree\n or equivalent", 
                                         "Associate's degree\n or equivalent", 
                                         "High school diploma\n or equivalent", 
                                         "Elementary school\n or equivalent", 
                                         "Other","None of the above"))

ggplot(education, aes(x = labels, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B") +
  scale_y_continuous(labels = percent) +
  labs(x = "Level of education competed",
       y = "Burning Man participants in 2024 (%)",
       title = "Which level of education have you completed?") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

makeTableData(education) |>
  kbl(col.names = c(2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:1, width_min = "10.5em") 
```

## Residence

### Residence inside of Black Rock City

```{r}
#| label: residence-brc

# Pull in official street centerlines and intersections generated from /_RCode/geo_make_intersections.R
brc_centerlines <- read_sf("geo_data/brc_centerlines.geojson")
brc_intersections <- read_sf("geo_data/brc_intersections.geojson")

# All possible survey responses for location campStreet and campRadial
validcampStreet <- c(LETTERS[1:12], "Esplanade", 
                     "Rod's Road", "Center Camp Plaza", "DPW Depot", "ESD", "Airport", 
                     "Walk-in camping")
validcampRadial <- paste0(rep(2:10, each = 2), ":", rep(c("00", "30"), times = 9))[1:17]

# Filter down to just the intersections a survey response could map to
brc_intersections_valid <- brc_intersections %>% 
  filter(
    street2 %in% validcampStreet,
    street1 %in% validcampRadial
  ) %>%
  select(all_of(c("street1", "street2", "address", "geometry")))

# Tally responses per intersection
intersection_summary <-brc_intersections_valid %>%
  left_join(census24, by = c("street1" = "campRadial", "street2" = "campStreet"), 
            relationship = "many-to-many") %>%
  group_by(address, geometry) %>%
  summarize(num_matches = n(), .groups = "drop")

# Map the result
brc_map <- ggplot() + geom_sf(data = brc_centerlines) + theme_void()
brc_map + 
  geom_sf(data = intersection_summary, aes(size = num_matches), color = '#EA008B') + 
  scale_size_continuous(range = c(1, 6), name = "Number of Responses") +
  geom_sf_text(data = intersection_summary, aes(label = num_matches), 
               color = "white", size = 2, check_overlap = TRUE) +
  theme_void() +
  theme(
    legend.position = c(0.95, 0.95),
    legend.justification = c("right", "top"),
    panel.background = element_rect(fill = "#f5f1e9", color = NA),  # Tan background
    plot.background = element_rect(fill = "#f5f1e9", color = NA),
    legend.background = element_rect(fill = "#f5f1e9", color = NA),
    legend.key = element_rect(fill = "#f5f1e9", color = NA)
  )

```

### Residence outside of Black Rock City

```{r}
#| label: residence-outside
### residence by continent

# begin by categorizing the write-in responses
myContinents <- list()
myContinents$Asia <- c("Asia",
                     "Israel",
                     "Hong Kong",
                     "United Arab Emirates",
                     "China",
                     "Japan",
                     "Thailand",
                     "UAE",
                     "Bali",
                     "Cambodia",
                     "india",
                     "Israel, Georgia",
                     "Isreal",
                     "Kazakhstan/ Russia",
                     "Kuwait",
                     "Lebanon",
                     "Philippines",
                     "Russia",
                     "Saudi Arabia",
                     "Singapore",
                     "Taiwan",
                     ""
                     )
myContinents$Africa <- c("Africa",
                       "South Africa",
                       "Morocco",
                       "Namibia",
                       "Nigeria",
                       "Nomad from South Africa",
                       "Runion Island"
                       )
myContinents$Oceania <- c("Australia",
                          "New Zealand",
                          "Sydney, Australia",
                          "Western Australia",
                          "Australia atm",
                          "Australia, Mexico",
                          "French polynesia",
                          "Gold Coast, Australia",
                          "Melbourne, Australia",
                          "UK but I moved to Australia following this year's burn"
                          )
myContinents$Europe <- c("Europe",
                       "Germany",
                       "France",
                       "Switzerland",
                       "United Kingdom",
                       "Netherlands",
                       "UK",
                       "Spain",
                       "Finland",
                       "Ireland",
                       "The Netherlands",
                       "England",
                       "Denmark",
                       "Italy",
                       "Uk",
                       "Austria",
                       "Belgium",
                       "Sweden",
                       "Estonia",
                       "London",
                       "London, UK",
                       "Norway",
                       "Poland",
                       "Ukraine",
                       "Amsterdam",
                       "Around Europe",
                       "Barcelona, Espaa",
                       "Belarus",
                       "Brittany",
                       "Czech Rep.",
                       "Czech Republic",
                       "Dominican Republic",
                       "Espaa",
                       "France / Netherland",
                       "Ger.",
                       "I'm German but currently living in Switzerland",
                       "Ibiza, Spain",
                       "Iceland",
                       "Italia",
                       "Lithuania",
                       "Lived in California before, now moved back to Germany",
                       "London England",
                       "Madrid spain",
                       "Munich, Germany",
                       "Nantes, France",
                       "monaco",
                       "Northern Ireland",
                       "Portugal",
                       "Scotland",
                       "Scotland and United Arab Emirates",
                       "Tbilisi, Georgia",
                       "Vienna / Austria / Europe",
                       "Wales, United Kingdom",
                       "Zurich, Switzerland"
                       )
myContinents$`North America` <- c("North America",
                             "Mexico",
                             "Mxico",
                             "Puerto Rico",
                             "Mexico City",
                             "Oregon",
                             "Panama",
                             "Montana",
                             "Texas",
                             "Alaska",
                             "atlanta georgia",
                             "Cincinnati, OH",
                             "Colorado",
                             "Costa rica",
                             "Costa Rica (mostly) and US (partly)",
                             "Eugene, Oregon",
                             "FL",
                             "Honduras",
                             "I'm an American nomad, travel worldwide",
                             "McKinney, TX",
                             "Mexico / Berlin",
                             "Mexico & part time California",
                             "Mxico and Boulder, CO",
                             "Mexico and Israel",
                             "Miami, Florida",
                             "Cancn,. Mxico",
                             "N/a, i'm nomadic, i live in my camping trailer and travel around (mostly in US and Mx)",
                             "New Jersey",
                             "New York",
                             "New York City, NY",
                             "Nicaragua",
                             "Nicaragua/ Colorado",
                             "Nomadic, US",
                             "Holbox, Mexico",
                             "Live a bit nomadically sometimes in USA in New Jersey, was in PR for a bit, traveled to Mexico and Guatemala",
                             "nyc",
                             "Part of the year in Coahuila Mexico the other part in California US",
                             "philadelphia",
                             "Portland oregon",
                             "Portland, Oregon",
                             "Salt Lake City, UT",
                             "San Miguel de Allende, Mexico",
                             "Seattle, WA, USA",
                             "tennessee",
                             "texas",
                             "Turks & Caicos Islands",
                             "U.S. nomadic",
                             "United States",
                             "US and Israel",
                             "USA",
                             "Utah, Alaska",
                             "Was living in China but just moved back to the US",
                             "Washington",
                             "Washington State",
                             "Wyoming",
                             "N/a, i'm nomadic, i live in my camping trailer and travel around (mostly in US and Mx)"
                             )
myContinents$`South America` <- c("South America",
                             "Brazil",
                             "Argentina",
                             "Chile",
                             "Brasil",
                             "Colombia",
                             "Colombia and other countries abroad",
                             "Ecuador"
                             )



ContinentResides <- census24$reside.writeIn
ContinentResides <- sapply(ContinentResides, function(s){
  contResults <- sapply(names(myContinents), function(nm){match(tolower(s),tolower(myContinents[[nm]]))})
  if(all(is.na(contResults))){NA}else{names(contResults[!is.na(contResults)])[1]}
})

ContinentResides[census24$reside%in%c("In Canada",
                            "Other location within U.S.",
                            "Within California",
                            "Within Nevada")] <- "North America" 


## check whether entries are missing
#sort(table(ContinentResides),decreasing=TRUE)
#remaining.writeIn <- census24$reside.writeIn[!grepl(paste(tolower(unlist(myContinents)),collapse="|"),tolower(census24$reside.writeIn))]
#sort(table(remaining.writeIn),dec=TRUE)



prptbl <- svymean(~ContinentResides, design = design24,na.rm=TRUE)*100


names(prptbl) <- gsub("ContinentResides","",names(prptbl))

continentFrequencies <- data.frame(
  continent = names(prptbl),
  Percent = c(prptbl)
)

World2 <- World
World2[World2$iso_a3 == "RUS","continent"] <- "Asia"
# we assign Russia to Asia, so that Siberia doesn't distort the cartogram

earth <- World2 %>% dplyr::group_by(continent) %>% dplyr::summarise() %>% dplyr::slice(-which(continent %in% c("Antarctica","Seven seas (open ocean)"))) 



earth2 <- merge(earth, continentFrequencies, by="continent")

earth2 <- st_transform(earth2, 3395)

# construct cartogram
earth2_cont <- cartogram_cont(earth2, "Percent",
                            itermax = 30,
                            threshold = 0.000001,
                            verbose=FALSE) %>%
  st_cast()

# plot it
tm_shape(earth2_cont) +
  tm_polygons("Percent", 
              fill.scale = tm_scale_continuous_log(values = rev(gradientColors(3)))) + 
  tm_title("Burner residence by continent", position=c(0.45, 1.05)) + 
  tm_layout(frame = FALSE, 
            legend.outside=FALSE) +
  tm_text("continent", size = 1, remove.overlap = TRUE)


#### residence by US state

theZipz <- census24$reside.zip

theZipz[nchar(theZipz) >5 & !is.na(theZipz)] <- gsub(
  "-.{4}$",
  "",
  theZipz[nchar(theZipz) >5 & !is.na(theZipz)]
) # remove last 4 of zip codes

Zs <- lapply(theZipz, function(u){
  if (is.na(u)) {
    NA
  } else {
    reverse_zipcode(u)
  }
}
)

burnerState <- sapply(Zs, function(v){
  if (length(v)>1) {
    v$state
  } else {
    NA
  }
}
)

statesWeights <- tapply(census24$weights, burnerState, sum)
statesWeights <- statesWeights/sum(statesWeights)*100

statesPercents <- sort(round(statesWeights,2), decreasing=TRUE) # weighted

burnersByState <- data.frame(STATE = names(statesPercents), Percent = statesPercents)

# adding mississippi
burnersByState <- rbind(burnersByState, data.frame(STATE="MS",Percent=0))
burnersByState$Percent <- burnersByState$Percent + 0.002 # adjust for numerical convenience in plotting

## plotting
usa <- states(cb = TRUE, progress_bar = FALSE) %>%
  shift_geometry()

usa$STATE <- c(state.abb, "DC", "PR")[
  match(usa$NAME, c(state.name, "District of Columbia", "Puerto Rico"),)
  ]

usa2 <- merge(usa, burnersByState, by="STATE")

usa2 <- st_transform(usa2, 3395)

# construct cartogram
usa2_cont <- cartogram_cont(usa2, "Percent",
                            itermax = 15,
                            threshold = 0.01,
                            verbose=FALSE) %>%
  st_cast()

# plot it
tm_shape(usa2_cont) +
  tm_polygons("Percent", 
              fill.scale = tm_scale_continuous_log(values = rev(gradientColors(3)))) +
  tm_title("Burner residence by US state", position=c(0.35, 1.09)) + 
  tm_layout(frame = FALSE, 
            legend.outside=FALSE) +
  tm_text("STATE", size = 1/2, remove.overlap = FALSE)


#### binning with the more reasonable CA/NV/other bins suitable for longitudinal trends


reside <- makePlotData("Where do you usually reside/live (when not in Black Rock City)?",
                       varNameTable = varNameTable,
                       designs = list(design13, design14, design15,
                                      design16, design17, design18,
                                      design19, design22, design23,
                                      design24),
                       years = c(2013:2019, 2022:2024),
                       levels = c(rep(list(c("California",
                                             "Canada",
                                             "Nevada",
                                             "Other",
                                             "USA_other")), times = 7),
                                  rep(list(c("Within California", "In Canada",
                                         "Within Nevada", "Other",
                                         "Other location within U.S.")), times = 3)),
                       labels = c("Within California", "Within Canada",
                                  "Within Nevada", "Other",
                                  "Other location in U.S."),
                       labelOrder = c(1, 3, 5, 2, 4))



ggplot(reside, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:5]) +
  labs(x = "", y = "Burning Man participants (%)",
       color = "Residence (not in BRC)",
       title = "Where do you usually reside (when not in Black Rock City)")

makeTableData(reside) |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:11, width_min = "11.5em") |>
  kable_styling() 
```

<!-- ### California and Nevada Residents -->

<!-- ZIP Code converted to county and maybe smoothed -->

<!-- ### State residence -->

<!-- ZIP code converted to state -->

```{r}
# Be sure to run the first chunk to load the required libraries

#NOTES
# can extend to ROW for next year, danger of not finishing if I do that now
# not an easy palette for maps
# reduced from 1:1 because there are too many dots to render otherwise and
# the density within some zips stretches credulity.
# as an added benefit, looks less like PII

# Load and shift all states/territories to fit in a reasonable bounding box
usa_shifted <- states(cb = TRUE, year = 2020, class = "sf") |>
  shift_geometry() |>
  st_transform(5070) # Albers (best projection for mapping continental US)

usa_zcta <- zctas(cb = TRUE, year = 2020, class = "sf") |>
  select(ZCTA = ZCTA5CE20) |>
  shift_geometry() |>              # shift AK, HI, PR, and other territories
  st_transform(5070) # Albers

# Create point in WGS84 for Black Rock City
brc_wgs84 <- st_sf(
  name = "Black Rock City",
  geometry = st_sfc(st_point(c(-119.2065, 40.7864)), crs = 4326)
)

# Convert to Albers projection
brc_5070 <- st_transform(brc_wgs84, crs = 5070)

# Spatial join to get state info
usa_zcta <- usa_zcta |>
  st_join(usa_shifted, join = st_intersects, left = TRUE) |>
  rename(state_abbr = STUSPS, state_name = NAME)

# Aggregate census data by geography

# Dotdensity map
set.seed(123)        # reproducible dot sampling

# Working only with 2024 data:
# Create one set of tally tables (counts + weights in one)
census24_by_zip <- tally_zip_stats("census24", scale_to = 72000/5)

bm_zcta <- inner_join(usa_zcta, census24_by_zip, by = "ZCTA")

# Randomly place a number of dots within the ZCTA geometry
# that corresponds to the weighted number estimated from
# that zip code.
density_dots_us <- jitter_dots(bm_zcta)

# Bounding box around the states / territories where we have dots
# (excludes furthest away territories, i.e. c("GU", "VI", "MP", "AS"))
conus_bbox <- usa_shifted %>%
  filter(STUSPS %in% unique(density_dots_us$STUSPS)) %>%
  st_bbox()

ggplot() +
  geom_sf(data = usa_shifted, fill = "gray92", color = "white", size = 0.1) +
  geom_sf(data = density_dots_us, color = discreteColors[1], size = 0.1, alpha = 0.3, show.legend = FALSE) +
  geom_sf(data = brc_5070, shape = 8, size = 1, color = "gray10", show.legend = FALSE) +
  coord_sf(
    crs = 5070,
    xlim = c(conus_bbox["xmin"], conus_bbox["xmax"]),
    ylim = c(conus_bbox["ymin"], conus_bbox["ymax"])
  ) +
  labs(
    title = "Where do you usually reside (Within the US)?",
    subtitle = "1 dot  5 Burners"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
  )


# Spatial join to assign the state boundary each jitter point falls within
density_dots_us <- st_join(
  density_dots_us,
  usa_shifted %>% select(STUSPS),
  join = st_intersects,
  left = TRUE
)

# Only California and Nevada.

# First union the states to avoid too many computations,
# then trim out the areas of the zip that fall outside these states.
# bm_zcta_CA_NV <- density_dots_us |>
#   st_intersection(
#     usa_shifted |>
#       filter(STUSPS %in% c("CA", "NV")) |>
#       st_union() |>
#       st_make_valid()
#   )

conus_bbox_CA_NV <- usa_shifted %>%
  filter(STUSPS %in% c("CA", "NV")) %>%
  st_bbox()

# Assign relevant state classifications
density_dots_us_where <- density_dots_us %>%
  mutate(
    symbol_group = case_when(
      STUSPS == "CA" ~ "Within California",
      STUSPS == "NV" ~ "Within Nevada",
      TRUE ~ "Other location in U.S."
    ),
    symbol_group = factor(symbol_group, levels = c(
      "Within California",
      "Within Nevada",
      "Other location in U.S."
    ))
  )

ggplot() +
  geom_sf(data = usa_shifted, fill = "gray92", color = "white", size = 0.1) +
  geom_sf(data = density_dots_us_where, aes(color = symbol_group), size = 0.01, alpha = 0.7, show.legend = FALSE) +
  geom_sf(data = brc_5070, shape = 8, size = 2, color = "black", show.legend = FALSE) +
  scale_color_manual(values = discreteColors[1:3]) +
  coord_sf(
    crs = 5070,
    xlim = c(conus_bbox_CA_NV["xmin"], conus_bbox_CA_NV["xmax"]),
    ylim = c(conus_bbox_CA_NV["ymin"], conus_bbox_CA_NV["ymax"])
  ) +
  labs(
    title = "Where do you usually reside (Within the US)?",
    subtitle = "1 dot  5 Burners"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA),
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
  )


```

<!-- ### Canadian province residence -->

<!-- Postal code converted to province -->

<!-- ## Voting and politics -->

## Politics

### Voting history for the last four Federal US elections

<!-- Combine with voting eligiblity -->

<!-- Need to revisit this one when I have more time.  Probably separate -->

<!-- voter eligibility breakdowns and a lasagna plot for number of votes -->

<!-- would be better. -->

```{r}
#| label: politics-voted

voteEligible <- makePlotData(varName = "Are you eligible to vote in the United States?",
                             varNameTable,
                             designs = list(design13, design14, design15,
                                            design16, design17, design18,
                                            design19, design22, design23,
                                            design24),
                             years = c(2013:2019, 2022:2024),
                             levels = rep(list(c("no", "yes")), times = 10),
                             labels = c("Not eligible to vote", "Eligible"),
                             labelOrder = 1:2)
numberVotes <- makePlotData(varName = "Number of the last four Federal US elections voted among eligible voters?",
                            varNameTable = varNameTable,
                            designs = list(design13, design14, design15,
                                            design16, design17, design18,
                                            design19, design22, design23,
                                            design24),
                            years = c(2013:2019, 2022:2024),
                            levels = rep(list(as.character(0:4)), times = 10),
                            labels = c("Did not vote", "1 election",
                                       "2 elections", "3 elections",
                                       "4 elections"),
                            labelOrder = c(2:4,1,5))
numberVotes$est <- numberVotes$est * rep(voteEligible$est[voteEligible$labels == "Eligible"], each = 5)
numberVotes$lower <- numberVotes$lower * rep(voteEligible$est[voteEligible$labels == "Eligible"], each = 5)
numberVotes$upper <- numberVotes$upper * rep(voteEligible$est[voteEligible$labels == "Eligible"], each = 5)
numberVotes$labels <- as.character(numberVotes$labels)
voteEligible$labels <- as.character(voteEligible$labels)
numberVotes <- rbind(numberVotes, voteEligible[voteEligible$labels == "Not eligible to vote",])
numberVotes$labels <- factor(numberVotes$labels, levels = c("Did not vote",
                                                            "1 election",
                                                            "2 elections",
                                                            "3 elections",
                                                            "4 elections",
                                                            "Not eligible to vote"))

ggplot(numberVotes, aes(x = year, y = est, fill = labels)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_line(linewidth = 1.5, alpha = 0.7) +
  # geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2023),
                     labels = c(2013:2019, 2022:2023)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_fill_manual(values = gradientColors(6)[c(5:1,6)]) +
  labs(x = "", y = "Burning Man participants (%)",
       labels = "Number of elections voted",
       title = "How many of the last four US elections did you vote in?")

makeTableData(numberVotes) |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  kable_styling() |>
  column_spec(column = 1:11, width_min = "10.5em")
```

### Political party affiliation

```{r}
politicalParty <- makePlotData("With which political party are you currently affiliated in the United States, if any?",
                               varNameTable = varNameTable,
                               designs = list(design17, design18, design19,
                                              design22, design23, design24),
                               years = c(2017:2019, 2022:2024),
                               levels = c(rep(list(c("Democratic", "Green",
                                                     "Libertarian", "None",
                                                     "Other", "Republican")),
                                              times = 3),
                                          rep(list(c("Democratic Party",
                                                     "Green Party",
                                                     "Libertarian Party",
                                                     "None or unaffiliated",
                                                     "Other US Party",
                                                     "Republican Party")),
                                              times = 3)),
                               labels = c("Democratic Party", "Green Party",
                                          "Libertarian Party", "None or unaffiliated",
                                          "Other US Party", "Republican Party"),
                               labelOrder = c("Democratic Party", "Republican Party",
                                              "Libertarian Party", "Green Party",
                                              "Other US Party", "None or unaffiliated"))


party.dem.16 <- customPlotDat(c("Democratic"),
                              design = design16, "usparty",
                              2016, "Democratic Party")
party.rep.16 <- customPlotDat(c("Republican"),
                              design = design16, "usparty",
                              2016, "Republican Party")
party.lib.16 <- customPlotDat(c("Libertarian"),
                              design = design16, "usparty",
                              2016, "Libertarian Party")
party.grn.16 <- customPlotDat(c("Green"),
                              design = design16, "usparty",
                              2016, "Green Party")
party.oth.16 <- customPlotDat(c("Other", "Am_Indep_Party"),
                              design = design16, "usparty",
                              2016, "Other US Party")
party.nne.16 <- customPlotDat(c("None"),
                              design = design16, "usparty",
                              2016, "None or unaffiliated")
party.dem.15 <- customPlotDat(c("Democratic"),
                              design = design15, "usparty",
                              2015, "Democratic Party")
party.rep.15 <- customPlotDat(c("Republican"),
                              design = design15, "usparty",
                              2015, "Republican Party")
party.lib.15 <- customPlotDat(c("Libertarian"),
                              design = design15, "usparty",
                              2015, "Libertarian Party")
party.grn.15 <- customPlotDat(c("Green"),
                              design = design15, "usparty",
                              2015, "Green Party")
party.oth.15 <- customPlotDat(c("Other", "Am_Indep_Party"),
                              design = design15, "usparty",
                              2015, "Other US Party")
party.nne.15 <- customPlotDat(c("None"),
                              design = design15, "usparty",
                              2015, "None or unaffiliated")
party.dem.14 <- customPlotDat(c("Democratic"),
                              design = design14, "usparty",
                              2014, "Democratic Party")
party.rep.14 <- customPlotDat(c("Republican"),
                              design = design14, "usparty",
                              2014, "Republican Party")
party.lib.14 <- customPlotDat(c("Libertarian"),
                              design = design14, "usparty",
                              2014, "Libertarian Party")
party.grn.14 <- customPlotDat(c("Green"),
                              design = design14, "usparty",
                              2014, "Green Party")
party.oth.14 <- customPlotDat(c("Other", "Am_Indep_Party"),
                              design = design14, "usparty",
                              2014, "Other US Party")
party.nne.14 <- customPlotDat(c("None"),
                              design = design14, "usparty",
                              2014, "None or unaffiliated")
party.dem.13 <- customPlotDat(c("Democratic"),
                              design = design13, "usparty",
                              2013, "Democratic Party")
party.rep.13 <- customPlotDat(c("Republican"),
                              design = design13, "usparty",
                              2013, "Republican Party")
party.lib.13 <- customPlotDat(c("Libertarian"),
                              design = design13, "usparty",
                              2013, "Libertarian Party")
party.grn.13 <- customPlotDat(c("Green"),
                              design = design13, "usparty",
                              2013, "Green Party")
party.oth.13 <- customPlotDat(c("Other", "Am_Indep_Party"),
                              design = design13, "usparty",
                              2013, "Other US Party")
party.nne.13 <- customPlotDat(c("None"),
                              design = design13, "usparty",
                              2013, "None or unaffiliated")
pp16 <- rbind(party.dem.16, party.rep.16, party.lib.16,
              party.grn.16, party.oth.16, party.nne.16)
pp16$est <- pp16$est / sum(pp16$est)
pp16$lower <- pp16$lower / sum(pp16$est)
pp16$upper <- pp16$upper / sum(pp16$est)

pp15 <- rbind(party.dem.15, party.rep.15, party.lib.15,
              party.grn.15, party.oth.15, party.nne.15)
pp15$est <- pp15$est / sum(pp15$est)
pp15$lower <- pp15$lower / sum(pp15$est)
pp15$upper <- pp15$upper / sum(pp15$est)


pp14 <- rbind(party.dem.14, party.rep.14, party.lib.14,
              party.grn.14, party.oth.14, party.nne.14)
pp14$est <- pp14$est / sum(pp14$est)
pp14$lower <- pp14$lower / sum(pp14$est)
pp14$upper <- pp14$upper / sum(pp14$est)

pp13 <- rbind(party.dem.13, party.rep.13, party.lib.13,
              party.grn.13, party.oth.13, party.nne.13)
pp13$est <- pp13$est / sum(pp13$est)
pp13$lower <- pp13$lower / sum(pp13$est)
pp13$upper <- pp13$upper / sum(pp13$est)



politicalParty <- rbind(politicalParty, pp16, pp15, pp14, pp13)

ggplot(politicalParty, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 2.25, color = "black") +
  # geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2,
  #               linewidth = 1) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[c(1:3,5,4,6)]) +
  labs(x = "", y = "Burning Man participants eligible to vote (%)",
       color = "US politcal party \n affiliation",
       title = "With which political party are you currently affiliated \n in the United States, if any?")

makeTableData(politicalParty) |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:11, width_min = "10.5em") |>
  kable_styling()
```

### Political views

```{r}
#| label: politics-views
# politicalViews <- makePlotData("Generally, in terms of political views, rather than political parties, I consider myself to be primarily",
#                                varNameTable = varNameTable,
#                                designs = list(design19, design22, design23),
#                                years = c(2019, 2022, 2023),
#                                levels = c(list(c("Anarchist",
#                                                  "Centrist_or_moderate",
#                                                  "Conservative", "Green",
#                                                  "Liberal", "Libertarian",
#                                                  "Non_political", "Other",
#                                                  "Progressive", "Socialist")),
#                                           rep(list(c("Anarchist",
#                                                  "Centrist or moderate",
#                                                  "Conservative", "Green",
#                                                  "Liberal", "Libertarian",
#                                                  "None or non-political",
#                                                  "Other", "Progressive",
#                                                  "Socialist")), times = 2)),
#                                labels = c("Anarchist",
#                                           "Centrist or moderate",
#                                           "Conservative", "Green",
#                                           "Liberal", "Libertarian",
#                                           "None or non-political",
#                                           "Other", "Progressive",
#                                           "Socialist"),
#                                labelOrder = c("Liberal", "Progressive",
#                                               "Socialist", "Green",
#                                               "Centrist or moderate",
#                                               "Conservative", "Libertarian",
#                                               "Anarchist",
#                                               "None or non-political",
#                                               "Other"))
# 
# ggplot(politicalViews, aes(x = labels, y = est, fill = as.factor(year))) +
#   geom_bar(stat = "identity", position = "dodge") +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = discreteColors[1:3]) +
#   labs(x = "Political view", y = "Burning Man participants (%)", fill = "Year",
#        title = "Generally, in terms of political views, rather than political parties, \n I consider  myself to be primarily...") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# makeTableData(politicalViews) |>
#   kbl(col.names = c(2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped")  |>
#   column_spec(column = 1:4, width_min = "10.5em") |>
#   kable_styling()

politicalViews <- makePlotData("Generally, in terms of political views, rather than political parties, I consider myself to be primarily",
                               varNameTable = varNameTable,
                               designs = list(design19, design22, design23,
                                              design24),
                               years = c(2019, 2022:2024),
                               levels = c(list(c("Anarchist",
                                                 "Centrist_or_moderate",
                                                 "Conservative", "Green",
                                                 "Liberal", "Libertarian",
                                                 "Non_political", "Other",
                                                 "Progressive", "Socialist")),
                                          rep(list(c("Anarchist",
                                                 "Centrist or moderate",
                                                 "Conservative", "Green",
                                                 "Liberal", "Libertarian",
                                                 "None or non-political",
                                                 "Other", "Progressive",
                                                 "Socialist")), times = 2),
                                          rep(list(c("Anarchist",
                                                 "Centrist or moderate",
                                                 "Conservative", "Green",
                                                 "Liberal", "Libertarian",
                                                 "None, I consider myself to be apolitical",
                                                 "Other", "Progressive",
                                                 "Socialist")), times = 1)),
                               labels = c("Anarchist",
                                          "Centrist or moderate",
                                          "Conservative", "Green",
                                          "Liberal", "Libertarian",
                                          "None or apolitical",
                                          "Other", "Progressive",
                                          "Socialist"),
                               labelOrder = c("Liberal", "Progressive",
                                              "Socialist", "Green",
                                              "Centrist or moderate",
                                              "Conservative", "Libertarian",
                                              "Anarchist",
                                              "None or apolitical",
                                              "Other"))


ggplot(politicalViews, aes(x = labels, y = est, fill = as.factor(year))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = discreteColors[1:4]) +
  labs(x = "Political view", y = "Burning Man participants (%)", fill = "Year",
       title = "Generally, in terms of political views, rather than political parties, \n I consider  myself to be primarily...") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

makeTableData(politicalViews) |>
  kbl(col.names = c(2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:5, width_min = "10.5em") |>
  kable_styling() 
```

## Spirituality

### How do you describe your spirituality?

```{r}
#| label: spirituality-description
spirituality <- makePlotData("How do you describe your spirituality?",
                             varNameTable = varNameTable,
                             designs = list(design13, design14, design15,
                                                 design16, design17, design18,
                                                 design19, design22, design23,
                                            design24),
                             years = c(2013:2019, 2022:2024),
                             levels = c(rep(list(c("Agnostic", "Atheist", "Deist",
                                                   "IDK", "Religious",
                                                   "Spiritual_not_relig")),
                                          times = 7),
                                        rep(list(c("Agnostic", "Atheist", "Deist",
                                               "Don\'t know", "Religious",
                                               "Spiritual, but not religious")), times = 3)),
                             labels = c("Agnostic", "Atheist", "Deist",
                                        "I don\'t know", "Religious",
                                        "Spiritual, but \n not religious"),
                             labelOrder = c(6, 2, 1, 5, 3, 4))

ggplot(spirituality, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:6]) +
  labs(x = "", y = "Burning Man participants (%)", color = "Language",
       "How do you describe your spirituality?")

makeTableData(spirituality) |>
  kbl(col.names = c(2013:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:11, width_min = "10.5em") |>
  kable_styling() 
```

## Sexuality and Relationships

### Sexual orientation

```{r}
#| label: sexuality-orientation
soGroups <- list("Bicurious or heteroflexible" = c("Bicurious",
                                                   "Bicurious or heteroflexible"),
                 "Bisexual or pansexual" = c("Bisexual", 
                                             "Bisexual or pansexual"),
                 "Demi-sexual or aesexual" = c("Asexual", "demisexual",
                                               "Demi-sexual",
                                               "Demi-sexual or aesexual"),
                 "Gay, lesbian, or homosexual" = c("Gay_Lesbian",
                                                   "Gay, lesbian, or homosexual"),
                 "Heterosexual or straight" = c("Heterosexual", 
                                                "Heterosexual or straight"),
                 "Other or refuse labels" = c("Other", "other",
                                              "Refuse labels", 
                                              "Refuse_labels"))

sexualOrientation <- makePlotData("Which of these expressions best describes your sexual orientation?",
              varNameTable = varNameTable,
              designs = list(design13, design14, design15,
                             design16, design17, design18,
                             design19, design22, design23,
                             design24),
              years = c(2013:2019, 2022:2024),
              levels = c(rep(list(c("Asexual", "Bicurious",
                                    "Bisexual", "demisexual", "Gay_Lesbian",
                                    "Heterosexual", "other", "Refuse_labels")), times = 7),
                        rep(list(c("Asexual", "Bicurious or heteroflexible",
                                   "Bisexual or pansexual", "Demi-sexual",
                                   "Gay, lesbian, or homosexual",
                                   "Heterosexual or straight",
                                   "Other", "Refuse labels")), times = 2),
                        rep(list(c("Bicurious or heteroflexible",
                                   "Bisexual or pansexual",
                                   "Demi-sexual or aesexual",
                                   "Gay, lesbian, or homosexual",
                                   "Heterosexual or straight",
                                   "Other", "Refuse labels")), times = 1)),
              labels = c("Bicurious or heteroflexible",
                         "Bisexual or pansexual",
                         "Demi-sexual or aesexual",
                         "Gay, lesbian, or homosexual",
                         "Heterosexual or straight",
                         "Other or refuse labels"),
              labelOrder = c("Heterosexual or straight",
                             "Bisexual or pansexual",
                             "Bicurious or heteroflexible",
                             "Gay, lesbian, or homosexual",
                             "Demi-sexual or aesexual",
                             "Other or refuse labels"),
              groups = soGroups)


ggplot(sexualOrientation, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:6]) +
  labs(x = "", y = "Burning Man participants (%)",
       color = "Sexual orientation",
       title = "Which of these expressions best describes your sexual orientation?")


makeTableData(sexualOrientation) |>
  kbl(col.names = c(2013:2019, paste0("2022",footnote_marker_alphabet(1)), 2023:2024), row.names = TRUE, escape = FALSE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:11, width_min = "10.5em") |>
  footnote(alphabet = c("\'Demi-sexual\' and \'Other\' choices were added in 2022.")) |>
  kable_styling()
```

### Partner in the default world

```{r}
#| label: sexuality-partnered
partner <- makePlotData("In the default world, do you have a partner or partners?",
                        varNameTable = varNameTable,
                        designs = list(design15, design16, design17,
                                       design18, design19, design22,
                                       design23, design24),
                        years = c(2015:2019, 2022:2024),
                        levels = c(rep(list(c("Its_complicated", "No",
                                              "Married", "In_relationship")),
                                       times = 5),
                                   rep(list(c("It\'s complicated", "No",
                                          "Yes and we are married",
                                          "Yes and we are not married")), times = 3)),
                        labels = c("It\'s complicated",
                                   "No, I am not in a relationship",
                                   "Yes, and we are married",
                                   "Yes, and we are not married"),
                        labelOrder = c(3, 4, 2, 1))

ggplot(partner, aes(x = year, y = est, color = labels)) +
  geom_line(linewidth = 1.5, alpha = 0.7) +
  geom_point(size = 2.25) +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = c(2013:2019, 2022:2024),
                     labels = c(2013:2019, 2022:2024)) +
  scale_y_continuous(labels = percent, limits = c(0, NA)) +
  scale_color_manual(values = discreteColors[1:7]) +
  labs(x = "", y = "Burning Man participants (%)",
       color = "Do you have a partner?",
       title = "In the default world, do you have a partner or partners?")

makeTableData(partner) |>
  kbl(col.names = c(2015:2019, 2022:2024), row.names = TRUE) |>
  kable_paper("striped")  |>
  column_spec(column = 1:9, width_min = "10.5em") |>
  kable_styling() 
```
