```{r, echo=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "", echo = FALSE,
                      warning = FALSE, message = FALSE)
```

# Travel logistics

```{r}
# Preparation

# Read in all years of data
library(data.table)
library(survey)
library(ggplot2)
library(scales)
library(knitr)
library(kableExtra)
source(paste0(getwd(), "/_RCode/read_census_data.R"))
source(paste0(getwd(), "/_RCode/make_table_data.R"))
source(paste0(getwd(), "/_RCode/make_plot_data.R"))
source(paste0(getwd(), "/_RCode/additional_functions.R"))

design16$variables$bxbforother <- census16$bxbforother

gradientColors <- colorRampPalette(c("#EA008B", "#B0AEDC", "#554149"))
discreteColors <- c("#EA008B", "#B0AEDC", "#554149", "#A07200", "#AADA91", 
                    "#FF8189", "#FFCF50", "#6FCFEB", "#76236C", "#FFFF3B")
```

## Arrival and departure

### Arrival date

<!-- TODO: bargraphs for each year comparing arrival date -->

```{r}
# arrival <- makePlotData("I arrived in Black Rock City the first time in 2023…",
#                         varNameTable = varNameTable,
#                         designs = list(design23),
#                         years = 2023,
#                         levels = c("Wed 8/23 (pre-event)", "Sun 8/27",
#                                    "Tue 8/29", "Sat 8/26 (pre-event)",
#                                    "Mon 8/28", "Thu 8/24 (pre-event)",
#                                    "Fri 8/25 (pre-event)", "Wed 8/30",
#                                    "Before Wed 8/23 (pre-event)", "Thu 8/31",
#                                    "Fri 9/01", "Sat 9/02", "Sun 9/03",
#                                    "Tue 9/05 (post-event)", 
#                                    "After Tue 9/05 (post-event)"),
#                         labels = c("Wed 8/23 \n (pre-event)", "Sun 8/27",
#                                    "Tue 8/29", "Sat 8/26 \n (pre-event)",
#                                    "Mon 8/28", "Thu 8/24 \n (pre-event)",
#                                    "Fri 8/25 \n (pre-event)", "Wed 8/30",
#                                    "Before Wed 8/23 \n (pre-event)", "Thu 8/31",
#                                    "Fri 9/01", "Sat 9/02", "Sun 9/03",
#                                    "Tue 9/05 \n (post-event)", 
#                                    "After Tue 9/05 \n (post-event)"),
#                         labelOrder = c("Before Wed 8/23 \n (pre-event)", 
#                                        "Wed 8/23 \n (pre-event)",
#                                        "Thu 8/24 \n (pre-event)", 
#                                        "Fri 8/25 \n (pre-event)",
#                                        "Sat 8/26 \n (pre-event)", "Sun 8/27",
#                                        "Mon 8/28", "Tue 8/29", "Wed 8/30",
#                                        "Thu 8/31", "Fri 9/01", "Sat 9/02",
#                                        "Sun 9/03", "Mon 9/04", 
#                                        "Tue 9/05 \n (post-event)",
#                                        "After Tue 9/05 \n (post-event)"))
# 
# ggplot(arrival, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Arrival date", y = "Burning Man participants in 2023 (%)",
#        title = "I arrived in Black Rock City the first time in 2023…") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# makeTableData(arrival) |>
#   kbl(col.names = c(2022),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:2, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Point of entry

```{r}
# pointOfEntry <- makePlotData("How did you arrive at Black Rock City? Select the best answer.",
#                              varNameTable = varNameTable,
#                              designs = list(design15, design16, design17,
#                                             design18, design19, design22,
#                                             design23),
#                              years = c(2015:2019, 2022:2023),
#                              levels = c(rep(list(c("Airport", "Burner_Express",
#                                                    "Gate", "Other",
#                                                    "Other_shuttle",
#                                                    "Point_1")), times = 5),
#                                         rep(list(c("BRC airport",
#                                         "Gate in a Burner Express Bus",
#                                         "Gate in a vehicle",
#                                         "Gate with another shuttle service",
#                                         "Other", "Point 1")), times = 2)),
#                              labels = c("BRC airport",
#                                         "Gate in a Burner Express Bus",
#                                         "Gate in a vehicle",
#                                         "Gate with another shuttle service",
#                                         "Other", "Point 1"),
#                              labelOrder = c(3,2,6,1,4,5))
# 
# ggplot(pointOfEntry, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Point of entry", y = "Burning Man participants (%)",
#        title = "How did you arrive at Black Rock City?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# makeTableData(pointOfEntry) |>
#   kbl(col.names = c(2015:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Departure date

<!-- TODO: bargraphs for each year comparing departure date -->

```{r}
# plannedDeparture <- makePlotData("I planned to leave Black Rock City…",
#                           varNameTable = varNameTable,
#                           designs = list(design23),
#                           years = 2023,
#                           levels = c("Tue 9/05 (post-event)", "Sun 9/03", 
#                                      "Mon 9/04", "Tue 8/29", "Sat 9/02",
#                                      "Mon 8/28", "Sun 8/27", "Fri 9/01", 
#                                      "Thu 8/31", "After Tue 9/05 (post-event)",
#                                      "Wed 8/30", "Before Sun 8/27 (pre-event)"),
#                           labels = c("Tue 9/05 \n (post-event)", "Sun 9/03", 
#                                      "Mon 9/04", "Tue 8/29", "Sat 9/02",
#                                      "Mon 8/28", "Sun 8/27", "Fri 9/01", 
#                                      "Thu 8/31", "After Tue 9/05 \n (post-event)",
#                                      "Wed 8/30", "Before Sun 8/27 \n (pre-event)"),
#                           labelOrder = c("Before Sun 8/27 \n (pre-event)", 
#                                          "Sun 8/27", "Mon 8/28", "Tue 8/29", 
#                                          "Wed 8/30", "Thu 8/31", "Fri 9/01", 
#                                          "Sat 9/02", "Sun 9/03", "Mon 9/04", 
#                                          "Tue 9/05 \n (post-event)", 
#                                          "After Tue 9/05 \n (post-event)"))
# 
# actualDeparture <- makePlotData("I actually left Black Rock City…",
#                           varNameTable = varNameTable,
#                           designs = list(design23),
#                           years = 2023,
#                           levels = c("Tue 9/05 (post-event)", "Sun 9/03", 
#                                      "Mon 9/04", "Tue 8/29", "Sat 9/02",
#                                      "Mon 8/28", "Sun 8/27", "Fri 9/01", 
#                                      "Thu 8/31", "After Tue 9/05 (post-event)",
#                                      "Wed 8/30", "Before Sun 8/27 (pre-event)"),
#                           labels = c("Tue 9/05 \n (post-event)", "Sun 9/03", 
#                                      "Mon 9/04", "Tue 8/29", "Sat 9/02",
#                                      "Mon 8/28", "Sun 8/27", "Fri 9/01", 
#                                      "Thu 8/31", "After Tue 9/05 \n (post-event)",
#                                      "Wed 8/30", "Before Sun 8/27 \n (pre-event)"),
#                           labelOrder = c("Before Sun 8/27 \n (pre-event)", 
#                                          "Sun 8/27", "Mon 8/28", "Tue 8/29", 
#                                          "Wed 8/30", "Thu 8/31", "Fri 9/01", 
#                                          "Sat 9/02", "Sun 9/03", "Mon 9/04", 
#                                          "Tue 9/05 \n (post-event)", 
#                                          "After Tue 9/05 \n (post-event)"))
# 
# departure <- rbind(plannedDeparture, actualDeparture)
# departure$`Planned or actual` <- rep(c("Planned", "Actual"), each = 12, 
#                                      times = 1)
# 
# ggplot(departure, aes(x = labels, y = est, fill = `Planned or actual`)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = discreteColors) +
#   labs(x = "Departure date", y = "Burning Man participants in 2023 (%)",
#        title = "I planned to leave Black Rock City…") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# plannedDepartureTable <- makeTableData(plannedDeparture) 
# actualDepartureTable <- makeTableData(actualDeparture)
# cbind(plannedDepartureTable, actualDepartureTable) |>
#   kbl(col.names = c("2023 (planned)", "2023 (actual)"),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:3, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Departure delay

```{r}
# departureCodeSwitch <- function(x){
#   if(is.na(x)){return(NA)}
#   switch(as.character(x),
#          "Before Sun 8/27 (pre-event)" = 0, 
#          "Sun 8/27" = 1, 
#          "Mon 8/28" = 2, 
#          "Tue 8/29" = 3, 
#          "Wed 8/30" = 4, 
#          "Thu 8/31" = 5, 
#          "Fri 9/01" = 6, 
#          "Sat 9/02" = 7, 
#          "Sun 9/03" = 8, 
#          "Mon 9/04" = 9, 
#          "Tue 9/05 (post-event)" = 10, 
#          "After Tue 9/05 (post-event)" = 11)
# }
#   
# codedPlanned <- sapply(census23$plannedLeaveBRC, departureCodeSwitch)
# codedActual <- sapply(census23$leftBRC, departureCodeSwitch)
# delayDays <- data.frame(daysDelayed = codedActual - codedPlanned,
#                         cweights = census23$weights)
# # design23$variables$daysDelayed <- codedActual - codedPlanned
# 
# ggplot(delayDays, aes(x = daysDelayed, weight = cweights)) +
#   geom_bar(fill = "#EA008B") +
#   labs(x = "Days delayed", y = "Burning Man participants (%)",
#        title = "Days difference between planned and actual departure") +
#   scale_y_continuous(breaks = c(0, 753, 1501, 2258), 
#                      labels = c("0%", "10%", "20%", "30%")) +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

### Point of departure

```{r}
# pointOfDeparture <- makePlotData("How did you depart from Black Rock City? Select the best answer.",
#                                  varNameTable = varNameTable,
#                                  designs = list(design18, design19, design22,
#                                                 design23),
#                                  years = c(2018:2019, 2022:2023),
#                                  levels = c(rep(list(c("Airport",
#                                                        "Burner_Express",
#                                                        "Gate_diffvehicle",
#                                                        "Gate_samevehicle",
#                                                        "Other",
#                                                        "Other_shuttle",
#                                                        "Point_1")), times = 2),
#                                             rep(list(c("BRC airport",
#                                             "Gate in a Burner Express Bus",
#                                             "Gate in a different vehicle",
#                                             "Gate in the same vehicle",
#                                             "Gate with another shuttle service",
#                                             "Other", "Point 1")), times = 2)),
#                                  labels = c("BRC airport",
#                                             "Gate in a Burner Express Bus",
#                                             "Gate in a different vehicle",
#                                             "Gate in the same vehicle",
#                                             "Gate with another shuttle service",
#                                             "Other", "Point 1"),
#                                  labelOrder = c(4, 3, 2, 7, 1, 5, 6))
# 
# ggplot(pointOfDeparture, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Point of departure", y = "Burning Man participants (%)",
#        title = "How did you depart from Black Rock City?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
# 
# makeTableData(pointOfDeparture) |>
#   kbl(col.names = c(2018:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:5, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

## Flying to Black Rock City

### Flew in an airplane to get (at least part of the way) to Black Rock City this year?

```{r}
# # The flyyn variable was not created in the data sets from Hunter in 2014-2017.
# 
# design14$variables$flyyn <- ifelse(design14$variables$fly == "No", "no", "yes")
# design15$variables$flyyn <- ifelse(design15$variables$fly == "No", "no", "yes")
# design16$variables$flyyn <- ifelse(design16$variables$fly == "No", "no", "yes")
# design17$variables$flyyn <- ifelse(design17$variables$fly == "No", "no", "yes")
# 
# flyyn <- makePlotData("Did you fly in an airplane to get (at least part of the way) to Black Rock City this year?",
#                       varNameTable = varNameTable,
#                       designs = list(design14, design15, design16, design17,
#                                      design18, design19, design22, design23),
#                       years = c(2014:2019, 2022:2023),
#                       levels = c(rep(list("yes"), times = 6), 
#                                  rep(list("Yes"), times = 2)),
#                       labels = "Flew (at least partway) \n to Black Rock City")
# 
# ggplot(flyyn, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2014:2019, 2022:2023), 
#                      labels = c(2014:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = c("#EA008B")) +
#   guides(color = "none") +
#   labs(x = "", y = "", color = "Burning Man participants (%)")
# 
# makeTableData(flyyn) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### If you flew, what was your final arrival airport?

```{r}
# #In previous years the airport variables was processed afterwards
# # to add the "no" and "BRC" options pulled from flyyn and travelbrc questions.
# # I am just modifying it here post-hoc.  Additionally, 2015 has an error in
# # the creation of this variable.
# 
# # Salt Lake City wasn't added as an option until 2019.  I am adding results from
# #   previous years using qaulitative response.  TODO: make footnote
# 
# # I am also making the No category NA since the population of interest here is
# #   people who flew.
# 
# design23$variables$arrivalAirport <- ifelse(design23$variables$howArriveBRC == "BRC airport",
#                                             "BRC", design23$variables$arrivalAirport)
# design22$variables$arrivalAirport <- ifelse(design22$variables$howArriveBRC == "BRC airport",
#                                             "BRC", design22$variables$arrivalAirport)
# design15$variables$fly <- ifelse(design15$variables$travelbrc == "Airport",
#                                  "BRC", design15$variables$fly)
# 
# design14$variables$fly <- ifelse(grepl("([Ss][Ll][Cc])|([Ss]alt)",
#                                        design14$variables$fly_TEXT),
#                                  "Salt_Lake_City", design14$variables$fly)
# design15$variables$fly <- ifelse(grepl("([Ss][Ll][Cc])|([Ss]alt)",
#                                        design15$variables$fly_TEXT),
#                                  "Salt_Lake_City", design15$variables$fly)
# design16$variables$fly <- ifelse(grepl("([Ss][Ll][Cc])|([Ss]alt)",
#                                        design16$variables$flyother),
#                                  "Salt_Lake_City", design16$variables$fly)
# design17$variables$fly <- ifelse(grepl("([Ss][Ll][Cc])|([Ss]alt)",
#                                        design17$variables$flyother),
#                                  "Salt_Lake_City", design17$variables$fly)
# design18$variables$fly <- ifelse(grepl("([Ss][Ll][Cc])|([Ss]alt)",
#                                        design18$variables$flyother),
#                                  "Salt_Lake_City", design18$variables$fly)
# 
# design14$variables$fly <- ifelse(design14$variables$fly == "No", NA,
#                                  design14$variables$fly)
# design15$variables$fly <- ifelse(design15$variables$fly == "No", NA,
#                                  design15$variables$fly)
# design16$variables$fly <- ifelse(design16$variables$fly == "No", NA,
#                                  design16$variables$fly)
# design17$variables$fly <- ifelse(design17$variables$fly == "No", NA,
#                                  design17$variables$fly)
# design18$variables$fly <- ifelse(design18$variables$fly == "No", NA,
#                                  design18$variables$fly)
# design19$variables$fly <- ifelse(design19$variables$fly == "No", NA,
#                                  design19$variables$fly)
# 
# airport <- makePlotData("What was your final arrival airport?",
#                         varNameTable = varNameTable,
#                         designs = list(design14, design15, design16,
#                                        design17, design18, design19,
#                                        design22, design23),
#                         years = c(2014:2019, 2022:2023),
#                         levels = c(rep(list(c("BRC", "Las_Vegas", "LA",
#                                               "Oakland", "Other", "Reno",
#                                               "Sacramento", "Salt_Lake_City",
#                                               "SF")), times = 6),
#                                    rep(list(c("BRC","Las Vegas", "Los Angeles",
#                                           "Oakland", "Other", "Reno",
#                                           "Sacramento", "Salt Lake City",
#                                           "San Francisco")), times = 2)),
#                         labels = c("BRC (88NV)","Las Vegas", "Los Angeles",
#                                    "Oakland", "Other", "Reno",
#                                    "Sacramento", "Salt Lake City",
#                                    "San Francisco"),
#                         labelOrder = c(6, 9, 8, 3, 7, 2, 1, 4, 5))
# 
# airport2 <- makePlotData("What was your final arrival airport?",
#                         varNameTable = varNameTable,
#                         designs = list(design14, design15, design16,
#                                        design17, design18, design19,
#                                        design22, design23),
#                         years = c(2014:2019, 2022:2023),
#                         levels = c(rep(list(c("BRC", "Las_Vegas", "LA",
#                                               "Oakland", "Other", "Reno",
#                                               "Sacramento", "Salt_Lake_City",
#                                               "SF")), times = 6),
#                                    rep(list(c("BRC","Las Vegas", "Los Angeles",
#                                           "Oakland", "Other", "Reno",
#                                           "Sacramento", "Salt Lake City",
#                                           "San Francisco")), times = 2)),
#                         groups = c(1, 2, 3, 2, 2, 4, 5, 6, 7),
#                         labels = c("BRC (88NV)","Other", "Los Angeles",
#                                    "Reno", "Sacramento", "Salt Lake City",
#                                    "San Francisco"),
#                         labelOrder = c(4, 7, 6, 3, 5, 1, 2))
# 
# 
# ggplot(airport2, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2014:2019, 2022:2023), 
#                      labels = c(2014:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors) +
#   labs(x = "", y = "Burning Man Partcipants who flew (%)", color = "")
# 
# 
# makeTableData(airport2) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

## Vehicle logistics

### How many people were in your vehicle when you arrived at the Gate?

<!-- Need to get original raw data from Hunter for this question -->

<!-- Need to make an answer of 0 NA on the cleaning script -->

```{r}
# nbvehicle23 <- makePlotData("How many people were in your vehicle when you arrived at the Gate (including you)?",
#                             varNameTable = varNameTable,
#                             years = 2023,
#                             designs = list(design23),
#                             levels = as.character(c(0:10, 16, 20, 22, 33)),
#                             groups = c(1,1,2,3,4,5,6,6,7,7,8,8,9,9,9),
#                             labels = c("1", "2", "3", "4", "5", "6-7", "8-9",
#                                        "10-19", "20 or more"))
# nbvehicle22 <- makePlotData("How many people were in your vehicle when you arrived at the Gate (including you)?",
#                             varNameTable = varNameTable,
#                             years = 2022,
#                             designs = list(design22),
#                             levels = as.character(c(0:13, 21, 22)),
#                             groups = c(1,1,2,3,4,5,6,6,7,7,8,8,8,8,9,9),
#                             labels = c("1", "2", "3", "4", "5", "6-7", "8-9",
#                                        "10-19", "20 or more"))
# nbvehicle13to19 <- makePlotData("How many people were in your vehicle when you arrived at the Gate (including you)?",
#                             varNameTable = varNameTable,
#                             years = 2013:2019,
#                             designs = list(design13, design14, design15,
#                                            design16, design17, design18,
#                                            design19),
#                             levels = as.character(c("1", "2", "3", "4", "5",
#                                                     "_6or7", "_8or9", "_10to19",
#                                                     "_20_or_more")),
#                             labels = c("1", "2", "3", "4", "5", "6-7", "8-9",
#                                        "10-19", "20 or more"))
# nbvehicle <- rbind(nbvehicle13to19, nbvehicle22, nbvehicle23)
# 
# ggplot(nbvehicle[nbvehicle$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Number of people", 
#        y = "Burning Man participants who entered through main gate (%)",
#        title = "How many people were in your vehicle when you arrived at the Gate?") +
#   theme_bw()
# 
# makeTableData(nbvehicle) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Vehicle passengers under 18 years old

```{r}
# nb0to12 <- rbind(c(as.numeric(svyciprop(~nb012vehicle > 0, design13)),
#                    attr(svyciprop(~nb012vehicle > 0, design13), "ci")),
#                  c(as.numeric(svyciprop(~nb012vehicle > 0, design14)),
#                    attr(svyciprop(~nb012vehicle > 0, design14), "ci")),
#                  c(as.numeric(svyciprop(~nb012vehicle2 != 0, design15)),
#                    attr(svyciprop(~nb012vehicle2 != 0, design15), "ci")),
#                  c(as.numeric(svyciprop(~nb012vehicle2 != 0, design16)),
#                    attr(svyciprop(~nb012vehicle2 != 0, design16), "ci")),
#                  c(as.numeric(svyciprop(~nb012vehicle > 0, design17)),
#                    attr(svyciprop(~nb012vehicle > 0, design17), "ci")),
#                  c(as.numeric(svyciprop(~nb012vehicle > 0, design18)),
#                    attr(svyciprop(~nb012vehicle > 0, design18), "ci")),
#                  c(as.numeric(svyciprop(~nb012vehicle > 0, design19)),
#                    attr(svyciprop(~nb012vehicle > 0, design19), "ci")),
#                  c(as.numeric(svyciprop(~vehicleUnder13 > 0, design22)),
#                    attr(svyciprop(~vehicleUnder13 > 0, design22), "ci")),
#                  c(as.numeric(svyciprop(~vehicleUnder13 > 0, design23)),
#                    attr(svyciprop(~vehicleUnder13 > 0, design23), "ci")))
# nb0to12 <- as.data.frame(nb0to12)
# names(nb0to12) <- c("est", "lower", "upper")
# nb0to12$year <- c(2013:2019, 2022:2023)
# nb0to12$labels <- "At least one person under 13 \n years old in car"
# 
# 
# nb13to17 <- rbind(c(as.numeric(svyciprop(~nb1317vehicle > 0, design13)),
#                    attr(svyciprop(~nb1317vehicle > 0, design13), "ci")),
#                  c(as.numeric(svyciprop(~nb1317vehicle > 0, design14)),
#                    attr(svyciprop(~nb1317vehicle > 0, design14), "ci")),
#                  c(as.numeric(svyciprop(~nb1317vehicle2 != 0, design15)),
#                    attr(svyciprop(~nb1317vehicle2 != 0, design15), "ci")),
#                  c(as.numeric(svyciprop(~nb1317vehicle2 != 0, design16)),
#                    attr(svyciprop(~nb1317vehicle2 != 0, design16), "ci")),
#                  c(as.numeric(svyciprop(~nb1317vehicle > 0, design17)),
#                    attr(svyciprop(~nb1317vehicle > 0, design17), "ci")),
#                  c(as.numeric(svyciprop(~nb1317vehicle > 0, design18)),
#                    attr(svyciprop(~nb1317vehicle > 0, design18), "ci")),
#                  c(as.numeric(svyciprop(~nb1317vehicle > 0, design19)),
#                    attr(svyciprop(~nb1317vehicle > 0, design19), "ci")),
#                  c(as.numeric(svyciprop(~vehicle13to17 > 0, design22)),
#                    attr(svyciprop(~vehicle13to17 > 0, design22), "ci")),
#                  c(as.numeric(svyciprop(~vehicle13to17 > 0, design23)),
#                    attr(svyciprop(~vehicle13to17 > 0, design23), "ci")))
# 
# nb13to17 <- as.data.frame(nb13to17)
# names(nb13to17) <- c("est", "lower", "upper")
# nb13to17$year <- c(2013:2019, 2022:2023)
# nb13to17$labels <- "At least one person 13 to 17 \n years old in car"
# 
# minorInVehicle <- rbind(nb0to12, nb13to17)
# 
# minorInVehicle$labels <- factor(minorInVehicle$labels,
#                                 levels = c("At least one person under 13 \n years old in car",
#                                            "At least one person 13 to 17 \n years old in car"))
# 
# ggplot(minorInVehicle, aes(x = year, y = est, fill = labels, color = labels)) +
#   geom_area(linewidth = 1.05, alpha = 0.7) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank(),
#         axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
#   scale_x_continuous(breaks = c(2013:2019, 2022:2023), 
#                      labels = c(2013:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, 0.1)) +
#   scale_fill_manual(values = gradientColors(2)[2:1]) +
#   scale_color_manual(values = gradientColors(2)[2:1]) +
#   guides(color = "none") +
#   labs(x = "", y = "Burning Man participants who entered through main gate (%)", color = "",
#        fill = "Minors in the car",
#        title = "Were any people in your vehicle under age 18?")
# 
# makeTableData(minorInVehicle) |>
#   kbl(col.names = c(2013:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:10, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Vehicle type

<!-- Only doing 2022 to save time, the question format is a bit fudgey -->

<!-- across years and will take some care -->

```{r}
# vehicleType <- makePlotData("In what type of vehicle did you travel in to Black Rock City this year?",
#                             varNameTable = varNameTable,
#                             designs = list(design23),
#                             years = 2023,
#                             levels = c("Bus", "Car", "Full-size van",
#                                        "Mini-van", "Motorcycle",
#                                        "Moving truck or box truck", "Other",
#                                        "Pick-up truck", "RV",
#                                        "Semi-truck towing trailer", "SUV"),
#                             labelOrder = c(7,5,4,3,10,9,1,2,11,6,8))
# 
# ggplot(vehicleType[vehicleType$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Vehicle type", y = "Burning Man participants in 2023 (%)",
#        title = "In what type of vehicle did you travel in to Black Rock City this year?") +
#   theme_bw() +
#   coord_flip()
# 
# makeTableData(vehicleType)[11:1,] |>
#   kbl(col.names = c(2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:2, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Towing a trailer

<!-- Something odd is going on here with the very large category -->

<!-- In 2019 353 very large, in 2022 6 very large -->

<!-- Only reporting 2022 until this is resolved -->

```{r}
# towing <- makePlotData("Was your vehicle towing a trailer?",
#                        varNameTable = varNameTable,
#                        designs = list(design23),
#                        years = 2023,
#                        levels = c("Don\'t remember", "Large", "Medium",
#                                   "No trailer", "Small", "Very large"),
#                        labels = c("I don\'t remember", "Large", "Medium",
#                                   "No trailer", "Small", "Very large"),
#                        labelOrder = rev(c(4, 5, 3, 2, 6, 1)))
# 
# ggplot(towing[towing$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Vehicle type", y = "Burning Man participants in 2023 (%)",
#        title = "Was your vehicle towing a trailer?") +
#   theme_bw() +
#   coord_flip()
# 
# makeTableData(towing)[6:1,] |>
#   kbl(col.names = c(2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:2, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Vehicle fuel type

<!-- Responses channged in 2022.  Could show previous years, but maybe -->

<!--  it's better to not. -->

```{r}
# vehicleFuelType <- makePlotData("What kind of fuel did your vehicle run on?",
#                                 varNameTable = varNameTable,
#                                 designs = list(design23),
#                                 years = 2023,
#                                 levels = c("Battery powered",
#                                            "Bio-diesel or other bio-fuel",
#                                            "Diesel", "I don't know",
#                                            "Premium gasoline",
#                                            "Regular gasoline"),
#                                 labelOrder = rev(c(6, 5, 3, 2, 1, 4)))
# 
# ggplot(vehicleFuelType[vehicleFuelType$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Vehicle type", y = "Burning Man participants in 2023 (%)",
#        title = "What kind of fuel did your vehicle run on?") +
#   theme_bw() +
#   coord_flip()
# 
# makeTableData(vehicleFuelType)[6:1,] |>
#   kbl(col.names = c(2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:2, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Approximately how many miles to the gallon did your vehicle get on the way to Black Rock City?

<!-- TODO:clean mpg variable in cleaning script -->

```{r}
# design23$variables$mpg2 <- ifelse(design23$variables$vehicleMPG > 100, NA,
#                                   design23$variables$vehicleMPG)
# design22$variables$mpg2 <- ifelse(design22$variables$vehicleMPG > 100, NA,
#                                   design22$variables$vehicleMPG)
# design19$variables$mpg2 <- ifelse(design19$variables$mpgtobrc > 100, NA,
#                                   design19$variables$mpgtobrc)
# mpg <- data.frame(mpg = c(design23$variables$mpg2, design22$variables$mpg2, 
#                           design19$variables$mpg2),
#                   weights = c(design23$variables$weights,
#                               design22$variables$weights,
#                               design19$variables$weightbfpublic),
#                   year = c(rep(2023, times = nrow(census23)),
#                            rep(2022, times = nrow(census22)),
#                            rep(2019, times = nrow(census19))))
# 
# 
# mpg.mean.23 <- svymean(~mpg2, design23, na.rm = TRUE)
# mpg.se.23 <- sqrt(attr(mpg.mean.23, "var"))
# mpg.mean.22 <- svymean(~mpg2, design22, na.rm = TRUE)
# mpg.se.22 <- sqrt(attr(mpg.mean.22, "var"))
# mpg.mean.19 <- svymean(~mpg2, design19, na.rm = TRUE)
# mpg.se.19 <- sqrt(attr(mpg.mean.19, "var"))
# mpg.means <- data.frame(mpg = c(as.numeric(mpg.mean.23),
#                                 as.numeric(mpg.mean.22),
#                                 as.numeric(mpg.mean.19)),
#                         lower = c(as.numeric(mpg.mean.23) - 1.965 * mpg.se.23,
#                                   as.numeric(mpg.mean.22) - 1.965 * mpg.se.22,
#                                   as.numeric(mpg.mean.19) - 1.965 * mpg.se.19),
#                         upper = c(as.numeric(mpg.mean.23) + 1.965 * mpg.se.23,
#                                   as.numeric(mpg.mean.22) + 1.965 * mpg.se.22,
#                                   as.numeric(mpg.mean.19) + 1.965 * mpg.se.19),
#                         year = c(2023, 2022, 2019))
# 
# ggplot(mpg[mpg$year == 2023,], aes(x = mpg, weight = weights)) +
#   geom_density(fill = "#EA008B", alpha = 0.5, bw = 3, linewidth = 1.01) +
#   geom_segment(x = mpg.means$mpg[mpg.means$year == 2023],
#                xend = mpg.means$mpg[mpg.means$year == 2023],
#                y = 0, yend = 0.04, color = "#4C4C4C",
#              linewidth = 1.1) +
#   annotate("text", x = 40, y = 0.0418, label = "Average miles per gallon to Black Rock City (18.9 MPG)") +
#   theme_bw(13) +
#   labs(x = "Miles per gallon to Black Rock City in 2023", y = "Density")
# 
# mpg.qs19 <- svyquantile(~mpgtobrc, design19, c(0.25, 0.5, 0.75), na.rm = TRUE)$mpgtobrc
# mpg.qs19 <- apply(mpg.qs19, 1, function(x){paste0(x[1], " (", x[2], ", ", x[3], ")")})
# mpg.qs22 <- svyquantile(~vehicleMPG, design22, c(0.25, 0.5, 0.75), na.rm = TRUE)$vehicleMPG
# mpg.qs22 <- apply(mpg.qs22, 1, function(x){paste0(x[1], " (", x[2], ", ", x[3], ")")})
# mpg.qs23 <- svyquantile(~vehicleMPG, design23, c(0.25, 0.5, 0.75), na.rm = TRUE)$vehicleMPG
# mpg.qs23 <- apply(mpg.qs23, 1, function(x){paste0(x[1], " (", x[2], ", ", x[3], ")")})
# 
# fdf <- paste0("%.", 1, "f")
# mpg.mn19 <- paste0(sprintf(fdf, round(mpg.means$mpg[3],1)), " (",
#                    sprintf(fdf, round(mpg.means$lower[3], 1)), ", ",
#                    sprintf(fdf, round(mpg.means$upper[3], 1)), ")")
# mpg.mn22 <- paste0(sprintf(fdf, round(mpg.means$mpg[2],1)), " (",
#                    sprintf(fdf, round(mpg.means$lower[2], 1)), ", ",
#                    sprintf(fdf, round(mpg.means$upper[2], 1)), ")")
# mpg.mn23 <- paste0(sprintf(fdf, round(mpg.means$mpg[1],1)), " (",
#                    sprintf(fdf, round(mpg.means$lower[1], 1)), ", ",
#                    sprintf(fdf, round(mpg.means$upper[1], 1)), ")")
# mpg.tab <- as.table(cbind(c(mpg.mn19, mpg.qs19), c(mpg.mn22, mpg.qs22), 
#                           c(mpg.mn23, mpg.qs23)))
# rownames(mpg.tab) <- c("Mean (Miles per gallon)", "25^th^ percentile",
#                        "Median", "75^th^ percentile")
# 
# mpg.tab |>
#   kbl(col.names = c(2019, 2022, 2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:3, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

## Route to BRC

### How many total miles did you drive to get to Black Rock City?

```{r}
# med15 <- svyquantile(~milestotal, design15, 0.5, na.rm = TRUE)[[1]]
# med16 <- svyquantile(~milestotal, design16, 0.5, na.rm = TRUE)[[1]]
# med17 <- svyquantile(~as.numeric(milestotal), design17, 0.5, na.rm = TRUE)[[1]]
# med18 <- svyquantile(~milestotal, design18, 0.5, na.rm = TRUE)[[1]]
# med19 <- svyquantile(~milestotal, design19, 0.5, na.rm = TRUE)[[1]]
# med22 <- svyquantile(~vehicleMiles, design22, 0.5, na.rm = TRUE)[[1]]
# med23 <- svyquantile(~vehicleMiles, design23, 0.5, na.rm = TRUE)[[1]]
# miles.median <- rbind(med15, med16, med17, med18, med19, med22, med23)
# miles.median <- apply(miles.median, 1, function(x){
#   paste0(x[1], " (", x[2], ", ", x[3], ")")})
# 
# q2515 <- svyquantile(~milestotal, design15, 0.25, na.rm = TRUE)[[1]]
# q2516 <- svyquantile(~milestotal, design16, 0.25, na.rm = TRUE)[[1]]
# q2517 <- svyquantile(~as.numeric(milestotal), design17, 0.25, na.rm = TRUE)[[1]]
# q2518 <- svyquantile(~milestotal, design18, 0.25, na.rm = TRUE)[[1]]
# q2519 <- svyquantile(~milestotal, design19, 0.25, na.rm = TRUE)[[1]]
# q2522 <- svyquantile(~vehicleMiles, design22, 0.25, na.rm = TRUE)[[1]]
# q2523 <- svyquantile(~vehicleMiles, design23, 0.25, na.rm = TRUE)[[1]]
# miles.q25 <- rbind(q2515, q2516, q2517, q2518, q2519, q2522, q2523)
# miles.q25 <- apply(miles.q25, 1, function(x){
#   paste0(x[1], " (", x[2], ", ", x[3], ")")})
# 
# q7515 <- svyquantile(~milestotal, design15, 0.75, na.rm = TRUE)[[1]]
# q7516 <- svyquantile(~milestotal, design16, 0.75, na.rm = TRUE)[[1]]
# q7517 <- svyquantile(~as.numeric(milestotal), design17, 0.75, na.rm = TRUE)[[1]]
# q7518 <- svyquantile(~milestotal, design18, 0.75, na.rm = TRUE)[[1]]
# q7519 <- svyquantile(~milestotal, design19, 0.75, na.rm = TRUE)[[1]]
# q7522 <- svyquantile(~vehicleMiles, design22, 0.75, na.rm = TRUE)[[1]]
# q7523 <- svyquantile(~vehicleMiles, design23, 0.75, na.rm = TRUE)[[1]]
# miles.q75 <- rbind(q7515, q7516, q7517, q7518, q7519, q7522, q7523)
# miles.q75 <- apply(miles.q75, 1, function(x){
#   paste0(x[1], " (", x[2], ", ", x[3], ")")})
# 
# q9915 <- svyquantile(~milestotal, design15, 0.99, na.rm = TRUE)[[1]]
# q9916 <- svyquantile(~milestotal, design16, 0.99, na.rm = TRUE)[[1]]
# q9917 <- svyquantile(~as.numeric(milestotal), design17, 0.99, na.rm = TRUE)[[1]]
# q9918 <- svyquantile(~milestotal, design18, 0.99, na.rm = TRUE)[[1]]
# q9919 <- svyquantile(~milestotal, design19, 0.99, na.rm = TRUE)[[1]]
# q9922 <- svyquantile(~vehicleMiles, design22, 0.99, na.rm = TRUE)[[1]]
# q9923 <- svyquantile(~vehicleMiles, design23, 0.99, na.rm = TRUE)[[1]]
# 
# 
# design15$variables$miles2 <- ifelse(design15$variables$milestotal < q9915[1],
#                                     design15$variables$milestotal, NA)
# design16$variables$miles2 <- ifelse(design16$variables$milestotal < q9916[1],
#                                     design16$variables$milestotal, NA)
# design17$variables$miles2 <- ifelse(as.numeric(design17$variables$milestotal) < q9917[1],
#                                     as.numeric(design17$variables$milestotal), NA)
# design18$variables$miles2 <- ifelse(design18$variables$milestotal < q9918[1],
#                                     design18$variables$milestotal, NA)
# design19$variables$miles2 <- ifelse(design19$variables$milestotal < q9919[1],
#                                     design19$variables$milestotal, NA)
# design22$variables$miles2 <- ifelse(design22$variables$vehicleMiles < q9922[1],
#                                     design22$variables$vehicleMiles, NA)
# design23$variables$miles2 <- ifelse(design23$variables$vehicleMiles < q9923[1],
#                                     design23$variables$vehicleMiles, NA)
# mean15 <- svymean(~miles2, design15, na.rm = TRUE)
# mean16 <- svymean(~miles2, design16, na.rm = TRUE)
# mean17 <- svymean(~miles2, design17, na.rm = TRUE)
# mean18 <- svymean(~miles2, design18, na.rm = TRUE)
# mean19 <- svymean(~miles2, design19, na.rm = TRUE)
# mean22 <- svymean(~miles2, design22, na.rm = TRUE)
# mean23 <- svymean(~miles2, design23, na.rm = TRUE)
# 
# milesMeans <- c(paste0(sprintf(fdf, round(as.numeric(mean15), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean15) - 1.965 * sqrt(attr(mean15, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean15) + 1.965 * sqrt(attr(mean15, "var")), 1)), ")"),
#                 paste0(sprintf(fdf, round(as.numeric(mean16), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean16) - 1.965 * sqrt(attr(mean16, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean16) + 1.965 * sqrt(attr(mean16, "var")), 1)), ")"),
#                 paste0(sprintf(fdf, round(as.numeric(mean17), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean17) - 1.965 * sqrt(attr(mean17, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean17) + 1.965 * sqrt(attr(mean17, "var")), 1)), ")"),
#                 paste0(sprintf(fdf, round(as.numeric(mean18), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean18) - 1.965 * sqrt(attr(mean18, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean18) + 1.965 * sqrt(attr(mean18, "var")), 1)), ")"),
#                 paste0(sprintf(fdf, round(as.numeric(mean19), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean19) - 1.965 * sqrt(attr(mean19, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean19) + 1.965 * sqrt(attr(mean19, "var")), 1)), ")"),
#                 paste0(sprintf(fdf, round(as.numeric(mean22), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean22) - 1.965 * sqrt(attr(mean22, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean22) + 1.965 * sqrt(attr(mean22, "var")), 1)), ")"),
#                 paste0(sprintf(fdf, round(as.numeric(mean23), 1)), " (",
#                        sprintf(fdf, round(as.numeric(mean23) - 1.965 * sqrt(attr(mean23, "var")), 1)), ", ",
#                        sprintf(fdf, round(as.numeric(mean23) + 1.965 * sqrt(attr(mean23, "var")), 1)), ")"))
# 
# ggplot(design23$variables, aes(x = miles2, weight = weights)) +
#   geom_density(fill = "#EA008B", alpha = 0.5, bw = 300, linewidth = 1.01) +
#   geom_segment(x = mean23[1],
#                xend = mean23[1],
#                y = 0, yend = 0.0005, color = "#4C4C4C",
#                linewidth = 1.1) +
#   scale_y_continuous(labels = number) +
#   scale_x_continuous(labels = comma) +
#   annotate("text", x = 2850, y = 0.0005, label = "Average miles driven (1190.4 miles)") +
#   theme_bw(13) +
#   labs(x = "Miles driven to Black Rock City in 2023", y = "Density",
#        title = "How many total miles did you drive to get to Black Rock City?")
# 
# milesTable <- as.table(rbind(milesMeans, miles.q25, miles.median, miles.q75))
# rownames(milesTable) <- c("Mean (Miles)", "25^th^ percentile",
#                           "Median", "75^th^ percentil")
# milesTable |>
#   kbl(col.names = c(2015:2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Route through Nevada to Black Rock City

```{r}
# route <- makePlotData("From the list below, select the option that best describes the route through Nevada that you took to get to BRC.",
#                       designs = list(design19, design22, design23),
#                       varNameTable = varNameTable,
#                       years = c(2019, 2022:2023),
#                       levels = c(list(c("Another_route", "From_AZ_border",
#                                         "From_CA_via_US6_US95",
#                                         "From_LA_to_BRC_via_US395",
#                                         "From_LA_to_Reno_to_BRC_via_US395",
#                                         "From_Las_Vegas",
#                                         "From_North_via_route447",
#                                         "From_Reno",
#                                         "From_SF_to_Reno_to_BRC_via_I80",
#                                         "From_South_CA_via_I15",
#                                         "From_Utah_border", "IDK")),
#                                  rep(list(c("Different route",
#                                         "From the Arizona border via US-93/US-95",
#                                         "From Central or Southern California via US-6/US-95",
#                                         "From Los Angeles / San Diego DIRECT to BRC via US-395",
#                                         "From Los Angeles / San Diego to RENO to BRC via US-395",
#                                         "From Las Vegas, NV",
#                                         "From Washington/Oregon/Northern California on Route 447",
#                                         "From Reno, NV",
#                                         "From San Francisco/Sacramento to RENO to BRC via I-80",
#                                         "From Southern California to Las Vegas to BRC via I-15",
#                                         "From the Utah border via I-80",
#                                         "Don't know")), times = 2)),
#                       labels = c("Different route",
#                                  "From the Arizona border \n via US-93/US-95",
#                                  "From Central or \n Southern California \n via US-6/US-95",
#                                  "From Los Angeles \n or San Diego DIRECT \n to BRC via US-395",
#                                  "From Los Angeles or \n San Diego to RENO \n to BRC via US-395",
#                                  "From Las Vegas, NV",
#                                  "From Washington, Oregon, \n Northern California \n on Route 447",
#                                  "From Reno, NV",
#                                  "From San Francisco or \n Sacrament to RENO \n to BRC via I-80",
#                                  "From Southern California \n to Las Vegas \n to BRC via I-15",
#                                  "From the Utah border \n via I-80",
#                                  "I don\'t know"),
#                       labelOrder = c(12, 10, 3, 2, 1, 6, 5, 4, 11, 7, 8, 9))
# 
# ggplot(route, aes(x = labels, y = est, fill = as.factor(year))) +
#   geom_bar(stat = "identity", position = "dodge") +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = discreteColors[1:3]) +
#   labs(x = "Route to Black Rock City", y = "Burning Man participants who entered through the main gate (%)", fill = "",
#        title = "Which route did you take through Nevada to get to BRC?") +
#   theme_bw() +
#   coord_flip()
# 
# makeTableData(route)[12:1,] |>
#   kbl(col.names = c(2019, 2022:2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:4, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

## Burner Express Bus (BXB)

### BXB routes

```{r}
# design14$variables$bxb_anyRoute <- (design14$variables$bxb_sftobrc == "yes") |
#   (design14$variables$bxb_renotobrc == "yes") |
#   (design14$variables$bxb_brctosf == "yes") |
#   (design14$variables$bxb_brctoreno == "yes")
# design14$variables$bxb_anyRoute[is.na(design14$variables$bxb_anyRoute)] <- FALSE
# 
# design15$variables$bxb_anyRoute <- (design15$variables$bxb_sftobrc == "yes") |
#   (design15$variables$bxb_renotobrc == "yes") |
#   (design15$variables$bxb_brctosf == "yes") |
#   (design15$variables$bxb_brctoreno == "yes")
# design15$variables$bxb_anyRoute[is.na(design15$variables$bxb_anyRoute)] <- FALSE
# 
# design16$variables$bxb_anyRoute <- (design16$variables$bxb_sftobrc == "yes") |
#   (design16$variables$bxb_renotobrc == "yes") |
#   (design16$variables$bxb_brctosf == "yes") |
#   (design16$variables$bxb_brctoreno == "yes")
# design16$variables$bxb_anyRoute[is.na(design16$variables$bxb_anyRoute)] <- FALSE
# 
# design17$variables$bxb_anyRoute <- (design17$variables$bxb_sftobrc == "yes") |
#   (design17$variables$bxb_renotobrc == "yes") |
#   (design17$variables$bxb_brctosf == "yes") |
#   (design17$variables$bxb_brctoreno == "yes")
# design17$variables$bxb_anyRoute[is.na(design17$variables$bxb_anyRoute)] <- FALSE
# 
# design18$variables$bxb_anyRoute <- (design18$variables$bxb_sftobrc == "yes") |
#   (design18$variables$bxb_renotobrc == "yes") |
#   (design18$variables$bxb_brctosf == "yes") |
#   (design18$variables$bxb_brctoreno == "yes")
# design18$variables$bxb_anyRoute[is.na(design18$variables$bxb_anyRoute)] <- FALSE
# 
# design19$variables$bxb_anyRoute <- (design19$variables$bxb_sftobrc == "yes") |
#   (design19$variables$bxb_renotobrc == "yes") |
#   (design19$variables$bxb_brctosf == "yes") |
#   (design19$variables$bxb_brctoreno == "yes")
# design19$variables$bxb_anyRoute[is.na(design19$variables$bxb_anyRoute)] <- FALSE
# 
# design22$variables$BXBRoute.any <- design22$variables$BXBRoute.SFToBRC |
#   design22$variables$BXBRoute.RenoToBRC |
#   design22$variables$BXBRoute.BRCToSF |
#   design22$variables$BXBRoute.BRCToReno
# 
# design23$variables$BXBRoute.any <- design23$variables$BXBRoute.SFToBRC |
#   design23$variables$BXBRoute.RenoToBRC |
#   design23$variables$BXBRoute.BRCToSF |
#   design23$variables$BXBRoute.BRCToReno
# 
# bxbDesign14 <- subset(design14, bxb_anyRoute)
# bxbDesign14$variables$bxb_sftobrc[is.na(bxbDesign14$variables$bxb_sftobrc)] <- "no"
# bxbDesign14$variables$bxb_renotobrc[is.na(bxbDesign14$variables$bxb_renotobrc)] <- "no"
# bxbDesign14$variables$bxb_brctosf[is.na(bxbDesign14$variables$bxb_brctosf)] <- "no"
# bxbDesign14$variables$bxb_brctoreno[is.na(bxbDesign14$variables$bxb_brctoreno)] <- "no"
# 
# bxbDesign15 <- subset(design15, bxb_anyRoute)
# bxbDesign15$variables$bxb_sftobrc[is.na(bxbDesign15$variables$bxb_sftobrc)] <- "no"
# bxbDesign15$variables$bxb_renotobrc[is.na(bxbDesign15$variables$bxb_renotobrc)] <- "no"
# bxbDesign15$variables$bxb_brctosf[is.na(bxbDesign15$variables$bxb_brctosf)] <- "no"
# bxbDesign15$variables$bxb_brctoreno[is.na(bxbDesign15$variables$bxb_brctoreno)] <- "no"
# 
# bxbDesign16 <- subset(design16, bxb_anyRoute)
# bxbDesign16$variables$bxb_sftobrc[is.na(bxbDesign16$variables$bxb_sftobrc)] <- "no"
# bxbDesign16$variables$bxb_renotobrc[is.na(bxbDesign16$variables$bxb_renotobrc)] <- "no"
# bxbDesign16$variables$bxb_brctosf[is.na(bxbDesign16$variables$bxb_brctosf)] <- "no"
# bxbDesign16$variables$bxb_brctoreno[is.na(bxbDesign16$variables$bxb_brctoreno)] <- "no"
# 
# bxbDesign17 <- subset(design17, bxb_anyRoute)
# bxbDesign17$variables$bxb_sftobrc[is.na(bxbDesign17$variables$bxb_sftobrc)] <- "no"
# bxbDesign17$variables$bxb_renotobrc[is.na(bxbDesign17$variables$bxb_renotobrc)] <- "no"
# bxbDesign17$variables$bxb_brctosf[is.na(bxbDesign17$variables$bxb_brctosf)] <- "no"
# bxbDesign17$variables$bxb_brctoreno[is.na(bxbDesign17$variables$bxb_brctoreno)] <- "no"
# 
# bxbDesign18 <- subset(design18, bxb_anyRoute)
# bxbDesign18$variables$bxb_sftobrc[is.na(bxbDesign18$variables$bxb_sftobrc)] <- "no"
# bxbDesign18$variables$bxb_renotobrc[is.na(bxbDesign18$variables$bxb_renotobrc)] <- "no"
# bxbDesign18$variables$bxb_brctosf[is.na(bxbDesign18$variables$bxb_brctosf)] <- "no"
# bxbDesign18$variables$bxb_brctoreno[is.na(bxbDesign18$variables$bxb_brctoreno)] <- "no"
# 
# bxbDesign19 <- subset(design19, bxb_anyRoute)
# bxbDesign19$variables$bxb_sftobrc[is.na(bxbDesign19$variables$bxb_sftobrc)] <- "no"
# bxbDesign19$variables$bxb_renotobrc[is.na(bxbDesign19$variables$bxb_renotobrc)] <- "no"
# bxbDesign19$variables$bxb_brctosf[is.na(bxbDesign19$variables$bxb_brctosf)] <- "no"
# bxbDesign19$variables$bxb_brctoreno[is.na(bxbDesign19$variables$bxb_brctoreno)] <- "no"
# 
# bxbDesign22 <- subset(design22, BXBRoute.any)
# bxbDesign23 <- subset(design23, BXBRoute.any)
# 
# bxbroute <- makePlotData("Which route(s) did you take on the Burner Express Bus?",
#                           varNameTable = varNameTable,
#                           designs = list(bxbDesign14, bxbDesign15, bxbDesign16,
#                                          bxbDesign17, bxbDesign18, bxbDesign19,
#                                          bxbDesign22, bxbDesign23),
#                           years = c(2014:2019, 2022:2023),
#                           levels = c(rep(list("yes"), times = 6),
#                                      rep(list(TRUE), times = 2)),
#                           labels = c("From San Francisco to Black Rock City",
#                                      "From Reno to Black Rock City",
#                                      "From Black Rock City to San Francisco",
#                                      "From Black Rock City to Reno"))
#  
# ggplot(bxbroute, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank(),
#         axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
#   scale_x_continuous(breaks = c(2014:2019, 2022:2023), labels = c(2014:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent) +
#   scale_color_manual(values = discreteColors) +
#   labs(x = "", y = "", color = "BXB route",
#        title = "Which route(s) did you take on the Burner Express Bus?")
# 
# makeTableData(bxbroute) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### BXB camping

```{r}
# 
# #TODO make foot note for response option change in 2016
# 
# bxbcamp <- makePlotData("Did you camp in Burner Express Camping?",
#                         varNameTable = varNameTable,
#                         designs = list(bxbDesign16, bxbDesign17, bxbDesign18,
#                                        bxbDesign19, bxbDesign22, bxbDesign23),
#                         years = c(2016:2019, 2022:2023),
#                         levels = c(rep(list(c("idk", "no",
#                                               "yes_and_would_again",
#                                               "yes_but_would_not_again")), times = 4),
#                                    rep(list(c("I don't know",
#                                           "No, I did not camp in Burner Express Camping",
#                                           "Yes, and I would camp there again",
#                                           "Yes, but I would not camp there again")), times = 2)),
#                         labels = c("I don\'t know",
#                                           "No, I did not camp in \n Burner Express Camping",
#                                           "Yes, and I would \n camp there again",
#                                           "Yes, but I would not \n camp there again"),
#                         labelOrder = c(3,4,2,1))
# 
# ggplot(bxbcamp, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2016:2019, 2022:2023), 
#                      labels = c(2016:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent) +
#   scale_color_manual(values = discreteColors) +
#   labs(x = "", y = "BXB Riders (%)", color = "BXB camping",
#        title = "Did you camp in Burner Express Camping?")
# 
# makeTableData(bxbcamp) |>
#   kbl(col.names = c(2016:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:7, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### BXB satellitte shuttle

```{r}

# bxbshuttle <- makePlotData("Did you ride the satellite shuttle that operates within Black Rock City?",
#                         varNameTable = varNameTable,
#                         designs = list(bxbDesign16, bxbDesign17, bxbDesign18,
#                                        bxbDesign19, bxbDesign22, bxbDesign23),
#                         years = c(2016:2019, 2022:2023),
#                         levels = c(rep(list(c("idk", "no", "yes")), times = 4),
#                                    rep(list(c("Don't know", "No", "Yes")), times = 2)),
#                         labels = c("I don\'t know", "No", "Yes"),
#                         labelOrder = c(3,2,1))
# 
# ggplot(bxbshuttle, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2016:2019, 2022:2023), 
#                      labels = c(2016:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent) +
#   scale_color_manual(values = discreteColors) +
#   labs(x = "", y = "BXB Riders", color = "Took the BXB \n satellite shuttle",
#        title = "Did you ride the satellite shuttle that \n operates within Black Rock City?")
# 
# makeTableData(bxbshuttle) |>
#   kbl(col.names = c(2016:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:7, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### Reasons for choosing to take BXB

```{r}
# 
# bxbreason <- makePlotData("What were your main reasons for choosing to take a Burner Express Bus?",
#                           varNameTable = varNameTable,
#                           designs = list(bxbDesign16,
#                                          bxbDesign17, bxbDesign18, bxbDesign19,
#                                          bxbDesign22, bxbDesign23),
#                           years = c(2016:2019, 2022:2023),
#                           levels = c(rep(list("yes"), times = 4),
#                                      rep(list(TRUE), times = 2)),
#                           labels = c("Cost",
#                                      "Do not have to drive",
#                                      "Avoid gate traffic",
#                                      "Help reduce road congestion",
#                                      "I\'ve used Burner Express in the past \n and wanted to do it again",
#                                      "Other"),
#                           labelOrder = c(1,2,3,4,5,6))
# 
# ggplot(bxbreason, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2016:2019, 2022:2023), labels = c(2016:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent) +
#   scale_color_manual(values = discreteColors) +
#   labs(x = "", y = "", color = "Reason to take BXB",
#        title = "What were your main reasons for choosing \n to take a Burner Express Bus?")
# 
# makeTableData(bxbreason) |>
#   kbl(col.names = c(2016:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:7, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Value of Burner Express Bus ticket based on satisfaction

```{r}
# 
# bxbprice <- makePlotData("Based on your level of satisfaction with the program, would you say that the price of a Burner Express Bus ticket was",
#                         varNameTable = varNameTable,
#                         designs = list(bxbDesign14, bxbDesign15, bxbDesign16,
#                                        bxbDesign17, bxbDesign18,
#                                        bxbDesign19, bxbDesign22, bxbDesign23),
#                         years = c(2014:2019, 2022:2023),
#                         levels = c(rep(list(c("overpriced", "right_price", "underpriced")), times = 6),
#                                    rep(list(c("Overpriced", "Just right", "Underpriced")), times = 2)),
#                         labels = c("Overpriced", "Just right", "Underpriced"),
#                         labelOrder = c(1,2,3))
# 
# ggplot(bxbprice, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2014:2019, 2022:2023), labels = c(2014:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent) +
#   scale_color_manual(values = gradientColors(3)) +
#   labs(x = "", y = "", color = "Took the BXB \n satellite shuttle",
#        title = "Would you say that the price of a Burner Express Bus ticket was...")
# 
# makeTableData(bxbprice) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### How would you rate your Burner Express Bus ticket purchase experience?

```{r}
# 
# bxbticketexp <- makePlotData("How would you rate your ticket purchasing experience on a scale of 1-10, where 1 = terrible and 10 = absolutely fantastic?",
#                              varNameTable = varNameTable,
#                              designs = list(bxbDesign16, bxbDesign17, bxbDesign18,
#                                             bxbDesign19, bxbDesign22, bxbDesign23),
#                              years = c(2016:2019, 2022:2023),
#                              levels = c(rep(list(c("terrible",
#                                                    as.character(2:9),
#                                                    "absolutely_fantastic")),
#                                             times = 4),
#                                         rep(list(c(as.character(1:10))), times = 2)),
#                              labels = c("1 (terrible)", as.character(2:9),
#                                         "10 (absolutely fantastic)"),
#                              labelOrder = 10:1)
# 
# bxbDesign16$variables$bxbticketexp2 <- as.numeric(ifelse(
#   bxbDesign16$variables$bxbticketexp == "terrible", 1,
#   ifelse(bxbDesign16$variables$bxbticketexp == "absolutely_fantastic", 10,
#          bxbDesign16$variables$bxbticketexp)))
# bxbDesign17$variables$bxbticketexp2 <- as.numeric(ifelse(
#   bxbDesign17$variables$bxbticketexp == "terrible", 1,
#   ifelse(bxbDesign17$variables$bxbticketexp == "absolutely_fantastic", 10,
#          bxbDesign17$variables$bxbticketexp)))
# bxbDesign18$variables$bxbticketexp2 <- as.numeric(ifelse(
#   bxbDesign18$variables$bxbticketexp == "terrible", 1,
#   ifelse(bxbDesign18$variables$bxbticketexp == "absolutely_fantastic", 10,
#          bxbDesign18$variables$bxbticketexp)))
# bxbDesign19$variables$bxbticketexp2 <- as.numeric(ifelse(
#   bxbDesign19$variables$bxbticketexp == "terrible", 1,
#   ifelse(bxbDesign19$variables$bxbticketexp == "absolutely_fantastic", 10,
#          bxbDesign19$variables$bxbticketexp)))
# 
# 
# 
# bxbTicketExpPlotDat <- data.frame(score = c(bxbDesign16$variables$bxbticketexp2,
#                                             bxbDesign17$variables$bxbticketexp2,
#                                             bxbDesign18$variables$bxbticketexp2,
#                                             bxbDesign19$variables$bxbticketexp2,
#                                             bxbDesign22$variables$BXBPurchasingExperience,
#                                             bxbDesign23$variables$BXBPurchasingExperience),
#                                   year = c(rep(2016, times = nrow(bxbDesign16$variables)),
#                                            rep(2017, times = nrow(bxbDesign17$variables)),
#                                            rep(2018, times = nrow(bxbDesign18$variables)),
#                                            rep(2019, times = nrow(bxbDesign19$variables)),
#                                            rep(2022, times = nrow(bxbDesign22$variables)),
#                                            rep(2023, times = nrow(bxbDesign23$variables))),
#                                   weights = c(bxbDesign16$variables$weightbmorg1,
#                                               bxbDesign17$variables$weightbfarrival,
#                                               bxbDesign18$variables$weightbfarrival,
#                                               bxbDesign19$variables$weightbfarrival,
#                                               bxbDesign22$variables$weights,
#                                               bxbDesign23$variables$weights))
# 
# ggplot(bxbTicketExpPlotDat, aes(x = as.factor(year), y = score, weight = weights)) +
#   geom_violin(bw = 1, fill  = "#EA008B", alpha = 0.7) +
#   theme_bw() +
#   labs(y = "Satisfaction score", x = "",
#        title = "How would you rate your Burner Express Bus \n ticket purchasing experience?") +
#   scale_y_continuous(breaks = 1:10, labels = c("1 (Terrible)", 
#                                                as.character(2:9),
#                                                "10 (Absolutely fantastic)")) +
#   theme(panel.grid.minor.y = element_blank())
# 
# makeTableData(bxbticketexp) |>
#   kbl(col.names = c(2016:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:7, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### How would you rate your overall Burner Express Bus experience?

```{r}
# 
# bxbexp <- makePlotData("How would you rate your overall Burner Express Bus experience on a scale of 1-10, where 1 = terrible and 10 = absolutely fantastic?",
#                              varNameTable = varNameTable,
#                              designs = list(bxbDesign14, bxbDesign15, bxbDesign16,
#                                             bxbDesign17, bxbDesign18,
#                                             bxbDesign19, bxbDesign22, bxbDesign23),
#                              years = c(2014:2019, 2022:2023),
#                              levels = c(rep(list(c("terrible",
#                                                    as.character(2:9),
#                                                    "absolutely_fantastic")),
#                                             times = 6),
#                                         rep(list(c(as.character(1:10))), times = 2)),
#                              labels = c("1 (terrible)", as.character(2:9),
#                                         "10 (absolutely fantastic)"),
#                              labelOrder = 10:1)
# 
# bxbDesign14$variables$bxbexp2 <- as.numeric(ifelse(
#   bxbDesign14$variables$bxbexp == "terrible", 1,
#   ifelse(design14$variables$bxbexp == "absolutely_fantastic", 10,
#          design14$variables$bxbexp)))
# 
# bxbDesign15$variables$bxbexp2 <- as.numeric(ifelse(
#   bxbDesign15$variables$bxbexp == "terrible", 1,
#   ifelse(design15$variables$bxbexp == "absolutely_fantastic", 10,
#          design15$variables$bxbexp)))
# 
# bxbDesign16$variables$bxbexp2 <- as.numeric(ifelse(
#   bxbDesign16$variables$bxbexp == "terrible", 1,
#   ifelse(design16$variables$bxbexp == "absolutely_fantastic", 10,
#          design16$variables$bxbexp)))
# 
# bxbDesign17$variables$bxbexp2 <- as.numeric(ifelse(
#   bxbDesign17$variables$bxbexp == "terrible", 1,
#   ifelse(design17$variables$bxbexp == "absolutely_fantastic", 10,
#          design17$variables$bxbexp)))
# 
# bxbDesign18$variables$bxbexp2 <- as.numeric(ifelse(
#   bxbDesign18$variables$bxbexp == "terrible", 1,
#   ifelse(design18$variables$bxbexp == "absolutely_fantastic", 10,
#          design18$variables$bxbexp)))
# 
# bxbDesign19$variables$bxbexp2 <- as.numeric(ifelse(
#   bxbDesign19$variables$bxbexp == "terrible", 1,
#   ifelse(design19$variables$bxbexp == "absolutely_fantastic", 10,
#          design19$variables$bxbexp)))
# 
# bxbExpPlotDat <- data.frame(score = c(bxbDesign14$variables$bxbexp2,
#                                       bxbDesign15$variables$bxbexp2,
#                                       bxbDesign16$variables$bxbexp2,
#                                       bxbDesign17$variables$bxbexp2,
#                                       bxbDesign18$variables$bxbexp2,
#                                       bxbDesign19$variables$bxbexp2,
#                                       bxbDesign22$variables$BXBOverallExperience,
#                                       bxbDesign23$variables$BXBOverallExperience),
#                             year = c(rep(2014, times = nrow(bxbDesign14$variables)),
#                                      rep(2015, times = nrow(bxbDesign15$variables)),
#                                      rep(2016, times = nrow(bxbDesign16$variables)),
#                                      rep(2017, times = nrow(bxbDesign17$variables)),
#                                      rep(2018, times = nrow(bxbDesign18$variables)),
#                                      rep(2019, times = nrow(bxbDesign19$variables)),
#                                      rep(2022, times = nrow(bxbDesign22$variables)),
#                                      rep(2023, times = nrow(bxbDesign23$variables))),
#                             weights = c(bxbDesign14$variables$weightbmorg,
#                                         bxbDesign15$variables$weightbmorg1,
#                                         bxbDesign16$variables$weightbmorg1,
#                                         bxbDesign17$variables$weightbfarrival,
#                                         bxbDesign18$variables$weightbfarrival,
#                                         bxbDesign19$variables$weightbfarrival,
#                                         bxbDesign22$variables$weights,
#                                         bxbDesign23$variables$weights))
# 
# ggplot(bxbExpPlotDat, aes(x = as.factor(year), y = score, weight = weights)) +
#   geom_violin(bw = 1, fill  = "#EA008B", alpha = 0.7) +
#   theme_bw() +
#   labs(y = "Satisfaction score", x = "",
#        title = "How would you rate your overall Burner Express Bus experience?") +
#   scale_y_continuous(breaks = 1:10, labels = c("1 (Terrible)", 
#                                                as.character(2:9),
#                                                "10 (Absolutely fantastic)")) +
#   theme(panel.grid.minor.y = element_blank())
# 
# makeTableData(bxbexp) |>
#   kbl(col.names = c(2014:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:9, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

## Visiting Nevada

### Did you stop at any locations in Gerlach?

```{r}
# gerlachStops23 <- makePlotData("As you passed through the town of Gerlach, did you stop at/visit any of the following locations?",
#                              varNameTable = varNameTable,
#                              designs = list(design23),
#                              years = 2023,
#                              levels = rep(list(TRUE), times = 1),
#                              labels = c("The Gerlach Burning Man Project office",
#                                         "The 360",
#                                         "The Oasis",
#                                         "The Desert Club (Hotel)",
#                                         "High Rock Pizza",
#                                         "Granite Point RV Park",
#                                         "Miners Club",
#                                         "Bruno\'s Country Club",
#                                         "Joe\'s Gerlach Club",
#                                         "Roadside vendors (food)",
#                                         "Roadside vendors (non-food)",
#                                         "Friends of Black Rock City",
#                                         "Other",
#                                         "I did not stop"),
#                              labelOrder = c(11, 5, 8, 10, 1, 7, 3, 9, 12, 4, 2, 6, 13, 14)[14:1])
# 
# gerlachStops22 <- makePlotData("As you passed through the town of Gerlach, did you stop at/visit any of the following locations?",
#                                #Removing friends of black rock
#                                varNameTable = varNameTable[!grepl("Friends of Black Rock City",
#                                                                   varNameTable$option),], 
#                              designs = list(design22),
#                              years = 2022,
#                              levels = rep(list(TRUE), times = 1),
#                              labels = c("The Gerlach Burning Man Project office",
#                                         "The 360",
#                                         "The Oasis",
#                                         "The Desert Club (Hotel)",
#                                         "High Rock Pizza",
#                                         "Granite Point RV Park",
#                                         "Miners Club",
#                                         "Bruno\'s Country Club",
#                                         "Joe\'s Gerlach Club",
#                                         "Roadside vendors (food)",
#                                         "Roadside vendors (non-food)",
#                                         "Other",
#                                         "I did not stop"),
#                              labelOrder = c(13,12,4,6,9,2,3,7,1,5,8,10,11))
# 
# gerlachStops22$labels <- factor(gerlachStops22$labels, 
#                                 levels = levels(gerlachStops23$labels))
# gerlachStops <- rbind(gerlachStops23, gerlachStops22)
# 
# 
# ggplot(gerlachStops, aes(x = labels, y = est, fill = as.factor(year), 
#                          group = year)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   scale_y_continuous(labels = percent) +
#   scale_fill_manual(values = discreteColors[2:1]) +
#   labs(x = "Stops in Gerlach", y = "Percent of participants",
#        fill = "",
#        title = "As you passed through the town of Gerlach, \n did you visit any of the following locations?") +
#   theme_bw() +
#   coord_flip() + 
#   guides(fill = guide_legend(reverse = TRUE))
# 
# table22 <- makeTableData(gerlachStops22)
# t22 <- matrix(c(table22[1:5, 1], "N/A", table22[6:13, 1]))
# t22 <- as.table(t22)
# colnames(t22) <- "2022"
# rownames(t22) <- c(rownames(table22)[1:5], "Friends of Black Rock City",
#                    rownames(table22)[6:13])
# table23 <- makeTableData(gerlachStops23)
# 
# #TODO add footnote for FoBRC option being added
# 
# cbind(table23, t22)[14:1,] |>
#   kbl(col.names = c(2022, 2023), row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   column_spec(column = 1:3, width_min = "10.5em") |>
#   kable_styling() |>
#   scroll_box(width = "100%")
```

### Visiting parks or recreation areas

```{r}
# #TODO add in 2013 and 2014.  Question options changed in 2015
# 
# parks <- makePlotData("Did you visit any parks and/or recreation areas this year on your way to and/or from Black Rock City?",
#                       varNameTable = varNameTable,
#                       designs = list(design15, design16, design17, design18,
#                                      design19, design22, design23),
#                       years = c(2015:2019, 2022:2023),
#                       levels = c(list(c("No", "Not_sure", "Yes_2+_places",
#                                         "Yes_one_place")),
#                                  rep(list(c("No", "Not_sure",
#                                             "Yes_2places_or_more",
#                                             "Yes_one_place")), times = 4),
#                                  rep(list(c("No", "Not sure",
#                                         "More than one place",
#                                         "One place")), times = 2)),
#                       labels = c("No", "Not sure",
#                                  "Yes, more than one place",
#                                  "Yes, one place"),
#                       labelOrder = c(4,3,1,2))
# 
# ggplot(parks, aes(x = year, y = est, color = labels)) +
#   geom_line(linewidth = 1.5, alpha = 0.7) +
#   geom_point(size = 2.25) +
#   theme_bw(13) +
#   theme(panel.grid.minor = element_blank()) +
#   scale_x_continuous(breaks = c(2015:2019, 2022:2023), labels = c(2015:2019, 2022:2023)) +
#   scale_y_continuous(labels = percent, limits = c(0, NA)) +
#   scale_color_manual(values = discreteColors) +
#   labs(x = "Burning Man participants (%)", y = "", 
#        color = "Parks or recreation visited",
#        title = "Did you visit any parks or recreation areas this year \n on your way to or from Black Rock City?")
# 
# 
# makeTableData(parks) |>
#   kbl(col.names = c(2015:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

### Reasons for visiting public lands

```{r}
# publicLands <- makePlotData("On your trip to and/or from the Burning Man event, are you visiting (or did you visit) public lands within a 30-mile radius of Black Rock City for any of the following reasons?",
#                             varNameTable = varNameTable,
#                             designs = list(design17, design18, design19,
#                                            design22, design23),
#                             years = c(2017:2019, 2022:2023),
#                             levels = c(rep(list(c("yes")), times = 3),
#                                        rep(list(c(TRUE)), times = 2)),
#                             labels = c("Camping", "Hiking",
#                                        "Boating or swimming",
#                                        "Hotsprings", "Wind sailing",
#                                        "Burning Man only", "Other"),
#                             labelOrder = c(6, 1, 3, 4, 2, 5, 7))
# 
# ggplot(publicLands[publicLands$year == 2023,], aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Reason for public lands visit", y = "Burning Man participants (%)",
#        title = "Are you visiting public lands within a 30-mile radius of Black Rock City \n for any of the following reasons?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
#   # facet_wrap(~as.factor(year), nrow = 1)
# 
# makeTableData(publicLands) |>
#   kbl(col.names = c(2017:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:6, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

<!-- ### Most visited Nevada cities or communities going to or from the Burning Man Event -->

<!-- This could maybe be a map? -->

### Return to the Black Rock Desert

```{r}
# returnBRD <- makePlotData("Do you intend to come back to the Black Rock Desert outside of the Burning Man event?",
#                           varNameTable = varNameTable,
#                           designs = list(design17, design18, design19,
#                                          design22, design23),
#                           years = c(2017:2019, 2022:2023),
#                           levels = c(rep(list(c("maybe", "no", "yes")), times = 3),
#                                      rep(list(c("Maybe", "No", "Yes")), times = 2)),
#                           labels = c("Maybe", "No", "Yes"),
#                           labelOrder = c(3, 1, 2))
# 
# ggplot(returnBRD, aes(x = labels, y = est)) +
#   geom_bar(stat = "identity", fill = "#EA008B") +
#   scale_y_continuous(labels = percent) +
#   labs(x = "Intend to return to Black Rock Desert", 
#        y = "Burning Man participants (%)",
#        title = "Do you intend to come back to the Black Rock Desert \n outside of the Burning Man event?") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
#   facet_wrap(~as.factor(year), nrow = 1)
# 
# makeTableData(returnBRD) |>
#   kbl(col.names = c(2017:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:5, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

## Expenses

### How much did you spend this year to travel to and from Black Rock City (not including your ticket)?

```{r}
# qs15 <- svyquantile(~bmspending, design15,
#                     c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                     na.rm = TRUE)[[1]]
# qs16 <- svyquantile(~bmspending, design16,
#                      c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                      na.rm = TRUE)[[1]]
# qs17 <- svyquantile(~bmspending, design17,
#                     c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                     na.rm = TRUE)[[1]]
# qs18 <- svyquantile(~bmspending, design18,
#                     c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                     na.rm = TRUE)[[1]]
# qs19 <- svyquantile(~bmspending, design19,
#                       c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                       na.rm = TRUE)[[1]]
# qs22 <- svyquantile(~spendToGoToBRC, design22,
#                     c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                     na.rm = TRUE)[[1]]
# qs23 <- svyquantile(~spendToGoToBRC, design23,
#                     c(0.01, 0.10, 0.25, 0.5, 0.75, 0.9, 0.99),
#                     na.rm = TRUE)[[1]]
# spend <- rbind(qs15, qs16, qs17, qs18, qs19, qs22, qs23)
# 
# spend2 <- data.frame(est = spend[,1], year = rep(c(2015:2019, 2022:2023), each = 7),
#                      percentiles = factor(c("1%", "10%", "25%", "50% (median)",
#                                             "75%", "90%", "99%"),
#                                           levels = c("99%", "90%",
#                                                      "75%", "50% (median)",
#                                                      "25%", "10%", "1%")))
# spend2$est[spend2$percentiles == "99%"] <- spend2$est[spend2$percentiles == "99%"] -
#   spend2$est[spend2$percentiles == "90%"]
# spend2$est[spend2$percentiles == "90%"] <- spend2$est[spend2$percentiles == "90%"] -
#   spend2$est[spend2$percentiles == "75%"]
# spend2$est[spend2$percentiles == "75%"] <- spend2$est[spend2$percentiles == "75%"] -
#   spend2$est[spend2$percentiles == "50% (median)"]
# spend2$est[spend2$percentiles == "50% (median)"] <- spend2$est[spend2$percentiles == "50% (median)"] -
#   spend2$est[spend2$percentiles == "25%"]
# spend2$est[spend2$percentiles == "25%"] <- spend2$est[spend2$percentiles == "25%"] -
#   spend2$est[spend2$percentiles == "10%"]
# spend2$est[spend2$percentiles == "10%"] <- spend2$est[spend2$percentiles == "10%"] -
#   spend2$est[spend2$percentiles == "1%"]
# 
# ggplot(spend2, aes(x = year, y = est, color = percentiles, fill = percentiles)) +
#   geom_area(linewidth = 1.05, alpha = 0.7) +
#   theme_bw(13) +
#   labs(x = "", y = "Amount spent to go to Burning Man (USD)",
#        fill = "Percentile",
#        title = "How much did you spend this year to travel \n to and from Black Rock City?") +
#   guides(color = "none") +
#   scale_y_continuous(labels = scales::dollar) +
#   scale_x_continuous(breaks = c(2015:2019, 2022:2023), 
#                      labels = c(2015:2019, 2022:2023))
# 
# spendTableValues <- matrix(apply(spend, 1, function(x){
#   paste0("$", x[1], " ( $", x[2], ", $", x[3], ")")}),
#   nrow = 7)
# 
# rownames(spendTableValues) <- c("1%", "10%", "25%", "50% (median)",
#                                 "75%", "90%", "99%")
# 
# spendTableValues |>
#   kbl(col.names = c(2015:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   scroll_box(width = "100%")

```

### Spending in Nevada

```{r}
# fuel15 <- weighted.mean2(census15$nvspendfuel, census15$weightbmorg1,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food15 <- weighted.mean2(census15$nvspendfood, census15$weightbmorg1,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging15 <- weighted.mean2(census15$nvspendlodging, census15$weightbmorg1,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival15 <- weighted.mean2(census15$nvspendsurvival, census15$weightbmorg1,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun15 <- weighted.mean2(census15$nvspendfun, census15$weightbmorg1,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# fuel16 <- weighted.mean2(census16$nvspendfuel, census16$weightbmorg1,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food16 <- weighted.mean2(census16$nvspendfood, census16$weightbmorg1,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging16 <- weighted.mean2(census16$nvspendlodging, census16$weightbmorg1,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival16 <- weighted.mean2(census16$nvspendsurvival, census16$weightbmorg1,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun16 <- weighted.mean2(census16$nvspendfun, census16$weightbmorg1,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# fuel17 <- weighted.mean2(census17$nvspendfuel, census17$weightbfarrival,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food17 <- weighted.mean2(census17$nvspendfood, census17$weightbfarrival,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging17 <- weighted.mean2(census17$nvspendlodging, census17$weightbfarrival,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival17 <- weighted.mean2(census17$nvspendsurvival, census17$weightbfarrival,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun17 <- weighted.mean2(census17$nvspendfun, census17$weightbfarrival,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# fuel18 <- weighted.mean2(census18$nvspendfuel, census18$weightbfarrival,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food18 <- weighted.mean2(census18$nvspendfood, census18$weightbfarrival,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging18 <- weighted.mean2(census18$nvspendlodging, census18$weightbfarrival,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival18 <- weighted.mean2(census18$nvspendsurvival, census18$weightbfarrival,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun18 <- weighted.mean2(census18$nvspendfun, census18$weightbfarrival,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# fuel19 <- weighted.mean2(census19$nvspendfuel, census19$weightbfarrival,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food19 <- weighted.mean2(census19$nvspendfood, census19$weightbfarrival,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging19 <- weighted.mean2(census19$nvspendlodging, census19$weightbfarrival,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival19 <- weighted.mean2(census19$nvspendsurvival, census19$weightbfarrival,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun19 <- weighted.mean2(census19$nvspendfun, census19$weightbfarrival,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# fuel22 <- weighted.mean2(census22$spendNevada.fuel, census22$weights,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food22 <- weighted.mean2(census22$spendNevada.food, census22$weights,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging22 <- weighted.mean2(census22$spendNevada.lodging, census22$weights,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival22 <- weighted.mean2(census22$spendNevada.survival, census22$weights,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun22 <- weighted.mean2(census22$spendNevada.fun, census22$weights,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# fuel23 <- weighted.mean2(census23$spendNevada.fuel, census23$weights,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# food23 <- weighted.mean2(census23$spendNevada.food, census23$weights,
#                          trim = c(NA, 0.999), na.rm = TRUE)
# lodging23 <- weighted.mean2(census23$spendNevada.lodging, census23$weights,
#                             trim = c(NA, 0.999), na.rm = TRUE)
# survival23 <- weighted.mean2(census23$spendNevada.survival, census23$weights,
#                              trim = c(NA, 0.999), na.rm = TRUE)
# fun23 <- weighted.mean2(census23$spendNevada.fun, census23$weights,
#                         trim = c(NA, 0.999), na.rm = TRUE)
# 
# 
# nvspend <- data.frame(meanSpend = c(fuel15[1], food15[1], lodging15[1],
#                                     survival15[1], fun15[1], fuel16[1],
#                                     food16[1], lodging16[1], survival16[1],
#                                     fun16[1], fuel17[1], food17[1],
#                                     lodging17[1], survival17[1], fun17[1],
#                                     fuel18[1], food18[1], lodging18[1],
#                                     survival18[1], fun18[1], fuel19[1],
#                                     food19[1], lodging19[1], survival19[1],
#                                     fun19[1], fuel22[1], food22[1],
#                                     lodging22[1], survival22[1], fun22[1],
#                                     fuel23[1], food23[1],
#                                     lodging23[1], survival23[1], fun23[1]),
#                       category = rep(c("Fuel", "Food", "Lodging", "Survival",
#                                        "Fun"), times = 7),
#                       year = rep(c(2015:2019, 2022:2023), each = 5))
# nvspend$totalspend <- ifelse(nvspend$year == 2015, nvspend$meanSpend * 70000,
#                       ifelse(nvspend$year == 2016, nvspend$meanSpend * 70000,
#                       ifelse(nvspend$year == 2017, nvspend$meanSpend * 70000,
#                       ifelse(nvspend$year == 2018, nvspend$meanSpend * 70000,
#                       ifelse(nvspend$year == 2019, nvspend$meanSpend * 80000,
#                       ifelse(nvspend$year == 2022, nvspend$meanSpend * 87000,
#                       ifelse(nvspend$year == 2023, nvspend$meanSpend * 72000,
#                              NA)))))))
# ggplot(nvspend, aes(x = year, y = totalspend, fill = category,
#                     color = category)) +
#   geom_area(linewidth = 1.05, alpha = 0.7) +
#   theme_bw(13) +
#   scale_fill_manual(values = discreteColors[1:5]) +
#   scale_color_manual(values = discreteColors[1:5]) +
#   labs(x = "", y = "Dollars (USD) spent in Nevada",
#        fill = "Percentile",
#        title = "Total spending in Nevada of all participants") +
#   guides(color = "none") +
#   scale_y_continuous(labels = scales::dollar) +
#   scale_x_continuous(breaks = c(2015:2019, 2022:2023), 
#                      labels = c(2015:2019, 2022:2023))
# 
# 
# nvSpendTableDat <- cbind(list(fuel15, food15, lodging15, survival15, fun15),
#                        list(fuel16, food16, lodging16, survival16, fun16),
#                        list(fuel17, food17, lodging17, survival17, fun17),
#                        list(fuel18, food18, lodging18, survival18, fun18),
#                        list(fuel19, food19, lodging19, survival19, fun19),
#                        list(fuel22, food22, lodging22, survival22, fun22),
#                        list(fuel23, food23, lodging23, survival23, fun23))
# fdf <- paste0("%.", 1, "f")
# nvSpendTableDat <- apply(nvSpendTableDat, 2, function(x){
#   sapply(x, function(y){
#     paste0("$" ,sprintf(fdf, round(y[1],1)), " (",
#            sprintf(fdf, round(y[3], 1)), ", ",
#            sprintf(fdf, round(y[4], 1)), ")")
#   })
# })
# 
# rownames(nvSpendTableDat) <- c("Average fuel spending",
#                                "Average food spending",
#                                "Average lodging spending",
#                                "Average survival spending",
#                                "Average fun spending")
# 
# nvSpendTableDat |>
#   kbl(col.names = c(2015:2019, 2022:2023),
#       row.names = TRUE) |>
#   kable_paper("striped", full_width = F) |>
#   kable_styling() |>
#   column_spec(column = 1:8, width_min = "10.5em") |>
#   scroll_box(width = "100%")
```

<!-- Could get creative in how to summarize this, average, total -->
